### 2018-05-23 manuscript.tex
Autocommit (fgc)

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{adjustbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{longtable}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

\usepackage{longtable,booktabs}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\newcommand{\comment}[1]{\textbf{[[#1]]}}

\bibliographystyle{plain}

\date{}

\begin{document}

\subsection{Manuscript}\label{manuscript}

\subsubsection{Title}\label{title}

Attitudes and Social Norms (Attitudes) of Female Genital Cutting in Kenya, Mali, Nigeria and Sierra Leon

\subsubsection{Authors}\label{authors}

Chyun-Fung Shi (corresponding author), Department of Biology, McMaster
University. Michael Li, Department of Biology, McMaster University.
Jonathan Dushoff, Department of Biology, McMaster
University.

\subsection{Abstract}\label{abstract}

\subsubsection{Context}\label{context}

\subsubsection{Objective}\label{objective}

\subsubsection{Methods}\label{Methods}

\subsubsection{Main Outcome Measures}\label{main-outcome-measures}

\subsubsection{Results}\label{results}

\subsubsection{Conclusions}\label{conclusions}
Under the background that MC is not challenged in the West (e.g., against Jewish community), how  shall we frame FGC to be process by both communities from inside and outside?

\subsubsection{Funding}\label{funding}

\subsubsection{Keywords}\label{keywords}

female genital cutting/mutilation, multilevel model, social norms, gender, DHS

\subsection{Introduction}\label{introduction}

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16}, and the actual numbers might in fact higher \cite{GaluKama15} (more?).  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the progress is hindered due to the complicated history of the very practice.  The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, SchuLien13, WHO12} (more cites).  Interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites).

There are at least three main theoretical perspectives from outside the communities
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  conventional theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.

The modernization theory proposes that traditional social relationships and values would be impacted by the development of modernization and replaced with modern life styles (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).  There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman’s empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.  Although conventional theory was well studied and showed a larger effect on FGC practices than other theories of modernization and feminism (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), the aforementioned theories did not necessarily excluded each other, especially between modern theory and feminist theory \cite{Hayf05}.

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.  This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test the three theories aforementioned.

\subsection{Research Questions}\label{research-questions}
There are two main research questions in this study:  attitudes of FGC benefits (see the list of FGC benefits at table xx) in association with attitudes of FGC continuance; and attitudes of FGC benefits in association with intention (planned behavior) of cutting daughters and with attitudes of FGC continuance.  The first question is referred to a FGC future model (FGC attitude model?), and the second a FGC daughter model (FGC intention model?).

\_\_{[}CF: how about the third model xx basic daughter model?  A few sentence of the differences between FGC future model and FGC daughter model{]}

\_\_{[}CF: read \cite{Aske05, Brue05}{]}

\subsection{Methods}\label{methods}

\subsubsection{Data and Samples}\label{data-and-samples}

The were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires for this study.  We first chose nations with high FGC prevalence \cite{UNIC16}, then their DHS surveys with modules of FGC benefits, and index of gender awareness.  The following countries met the criteria:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not use a newer dataset from those countries due to the lack of FGC benefits information in the newer surveys (checked in 09/17).

\_\_{[}CF: none of the countries had GPS data.  Kenya 2014, Mali 2012-3 and Nigeria 2013 have no value set {]}.  Sierra Leone 2013 does.  Should we use Sierra Leone 2008 or 2013? 2008 data is closer to the other data in terms of time period. It seems more convincing to if the data is all in a similar time span.  On the other hand, it is a much recent data and provides a more updated view{]}.

We included all the women despite of their FGC status and with or without daughters in the future model because our main interest was to study women's attitudes towards FGC continuance in general and their opinions counted as community attitudes towards this practice.  In the daughters model, we included only women with uncircumcised daughters because we were interested in mother's intention of whether to cut their daughters; and that resulted in xxx, xxx, xxx and xxx in the future model, and xxx, xxx, xxx and xxx in the daughter model respectively.

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
The main constructs to test the three theories of FGC practices(e.g., conventions, modernization, and feminism) are inferred from the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm).  The planned behavior theory proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, we constructed women's fgc attitudes based on the xx questions of FGC benefits in DHS, women's gender attitudes based on xx questions of domestic violence; the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.

(CF: Can domestic violence index (gender power) be a proxy to perceived controlled behavior for daugther's FGC future?)

The main response variables were woman's opinion (or attitude?) on whether they think FGC should be continued in the FGC future model and woman's intention of cut their daughters in the daughter's FGC status model.  The main predictors in both of the models were beliefs of FGC benefits (see the list of FGC benefits at table-- in Appendix) and woman's FGC status.  We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.  It is noted that we chose woman's attitudes towards gender violence instead of personal violence experience from their spouse because the former better reflects gender awareness.  We believed that FGC benefits coded and the information of such collected by DHS represented the values of the communities where FGC practiced.

In reference to the studies mentioned above, we also included the followings as covariates:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs. rural).  The followings were treated as random variables:  cluster ID (villages), countries and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).  Further, media effect was also counted in the random effect (slope?) because we presumed that each country carried various media content from each other.

 \_\_{[}CF:Do we spline wealth and group age? How do we estimate FGC belief, attitudes towards violence against women and media use?{]}

%“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. “ \cite{Hayf05}

In order to address the significance of community impact on the practice of FGC, we tested education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level, which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).  Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?)

\_\_{[}CF: Did we calculate FGC prevalence by counting all the women in the DHS, or just those with daughters in the daughter model?{]}
\_\_{[}CF:cluster is not a random effect in FGC, is it?{]}
\_\_{[}CF:Shall we also test religion and ethnicity at a community level?{]}
\_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess. CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  Same reason as for clusterID{]}

\_\_{[}CF:reason why using PCA:  see \cite{Hayf05} p.. 129 for reference.{]}
\_\_{[}CF:The concept of heterogeneity and threshold is important.  How to address these 2 concepts, if necessary.{]}
\_\_{[}CF:Spatial Bayesian model \cite{KandNwak09} "Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788){]}

% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}

\subsubsection{Statistical Model}\label{statistical-model}

\_\_{[}CF: J and M, please confirm this.{]}

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to examine the models.  The CLMM framework allows us to model a binary or ordinal response variable (e.g., daughter's FGC, while treating clusters and country as random effects.

\_\_{[}CF: We have two main predictors:  mother's FGC status and FGC beliefs.  Mother's FGC status is binary categorical variable, and FGC belief is continuous.  The responses are daughter's FGC status and whether to continue FGC; both are categorical with 3 levels (yes, no, and dk/depends).{]}

\_\_{[}CF: reference: Methods and the first paragraph of Discussion\cite{Chia14}{]}
\_\_{[}CF: spatial patterns?{]}

\_\_{[}JD: What is the difference between clmm and clmm2?{]}

This line of code essentially assumes that the response is ordinal. But I don't think it is...it actually seems pretty complex. So the best thing to do would probably be to figure out the total number of categories your response variable has and use MCMCglmm. Not sure specifically how the MCMCglmm approach would work, but this blog post might help: http://hlplab.wordpress.com/2009/05/07/multinomial-random-effects-models-in-r/

More about response -- to clarify what model to use, it might help to ask yourself: what are the possible combinations of outcomes of the various response variables?  i.e. collapse all of the response variables into one single categorical response with many categories. \_\_{[}CF: I like this idea and actually have been thinking about this possibility.{]}

\_\_{[}jd: Probably we can start with binary responses, and with exploring patterns of type, before we worry to much about these details.{]}

\subsubsection{Scripts}\label{scripts}

\subsection{Results}\label{results-1}

Tables and figures including:
table of basic sociodemographic results
figure:  proportion of FGC daughters and FGC future
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% figure of significant variables on modernization and pile the findings of the 4 nations into one figure.
% a chart like figure 8-8D \cite{UNCI13}
% figure of FGC prevalence by age and country (see Hayf05)
% refer to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/figure/F1/  \cite{SipsChen12} for a figure on intention of cutting daughter, mom's fgc status and their thoughts on fgc continuity.

Kenya 21% vs. 3% (2004-15 aged 15-49 women vs. 2010-15 aged 0-14 girls)
Mali 89% vs. ?
Nigeria 25% vs. 17%
Sierra Leone 90% vs. 13%
(We want DHS fgc rate and the rate from our samples)

\_\_{[}CF: findings on convention theory vs. modernization theory vs. gender theory{]}

\subsubsection{Basic Sociodemographic background}\label{Basic-Sociodemographic-background}
% adding how many ethnic groups in each nation based on DHS data.

\subsubsection{The FGC Future}\label{The-FGC-Future}

\subsubsection{Daughters' FGC Status}\label{Daughters'-FGC-Status}

\subsubsection{full model}\label{full-model}

% Kenya and Nigeria both were under %30 vs. Mali and Sierra Leon over %80.  Are they different in terms of norm and beahvior?  To discuss this in the discussion.

\subsection{Discussion}\label{Discussion}

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).

--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}

-- Second interpretation --
--- socio demographic interpretation at both levels (link this to modernization?)
\cite{Hayf05, PashPonn16} (more)
% education:  \cite{IliyAbub12, KarmKand11}
% religion:  \cite{KarmKand11}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}

--- by nations
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]
---- Mali: "The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

---- Nigeria: "Modernization (education and high socioeconomic status) had minimal impact on the likelihood of FGM, but education plays an important role in the mother's decision not to circumcise her daughter. It follows from these findings that community factors have a large effect on FGM, with individual factors having little effect on the distribution of FGM" \cite{KandNwak09}

---- Sierra Leon: 
\cite{ShelHern06, ShelHern13}  (Are they on Senegal or Sierra Leone?)

===============================

% collective action problem referring to community level of impact
Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}. It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).

\comment{cf: how to cite \cite{AkhmWord13,EffeVogt15} and compare these two?}
% There are "discrepancies between attitudes and practices, especially significant under an analysis by sex as, despite manifesting less support, the percentage of female HCPs declaring to have performed medicalization is almost twice the males’ average. These findings suggest that female HCPs could be facing higher demand to medicalize the practice, and that, even when brought to the medical setting, FGM/C is regarded as a women’s issue to be performed by women to women." \cite{KaplSing16}

% "autonomy within culture" is socially situated and entails neither endorsement of FGC nor resignation to its persistence." \cite{Meye00}:  How can we apply this feminism perspective to our findings? (Since we did not categorize types of fgc in our study, we can't know if women of autonomy prefer to have a "nick" on their daughter to preserve cultural identity or abandon fgc completely.

% \cite{WahlJohn17} showed that change does occur in newly immigrants once they were relocated to a new society where FGC was defied; how does this compared to \cite{EffeVogt15}'s heterogeneous model?

% little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
% put religion into consideration of our findings (i.e., national distribution of religion, how many muslins in each country)
% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09}. (from the introduction.  try to compare our result with theirs).
% mother-daughter: \cite{PashPonn16}
% \cf{the structure:  cultural and legal background; comparison of our findings to previous studies; implications}
% Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status \cit{Hayf05}

% If convention theory is more than just about securing marriage market (e.g., peer convention), then it is a theory about norms in general, isn't it?  That is, types of norms explain better than just marriage market.

% Overall:

%Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics \cite{BrowBeec13}.

% contagious diffusion \cite{Mack96}

% “FGC facilitates the accumulation of social capital by younger women and of power and prestige by elder women. Based on this new evidence and reinterpretation of social convention theory, we suggest that interventions aimed at eliminating FGC should target women's social networks, which are intergenerational, and include both men and women. Our findings support Mackie's assertion that expectations regarding FGC are interdependent; change must therefore be coordinated among interconnected members of social networks." \cite{ShelWand11}

FGC is still in practice or a preference among women after migrated to a western environment from their original communities where FGC was a common practice, in the hope (wording?) of preserving their ethnic and gender identity despite its conflict against the  norms and laws of the newly settled society \cite{}; however, a baseline study in Sweden showed that a majority of female immigrants, including those newly arrived, opposed all forms of FGC with increased opposition over time after migration, and suggested that an attitude change had occurred \cite{WahlJohn17}; that suggested a likely influence of conventional theory.

(There are also studies proposing various factors impacting FGC practices, such as women's education \cite{KandNwak09,VanMeek15}, social economic status \cite{} etc, community levels of influences.) (What is conventional in convention theory can also be focal points to gender awareness and modern development.  Question:  What is the differences between conventional theory and community level of impact on FGC? the same or?)

% Others:

% To compare with findings in Burkina Faso \cite{KarmKand11}, and Tostan

% Spatial Bayesian model \cite{KandNwak09}
% idea of purity of women reflects on the status and honor of their families \cite{Ortn87}.  Female purity is oriented to an ideal and unattainable higher class. \cite{Ortn87}
% a possibility of a multicultural egalitarian society \cite{Wade11}
% success in community education program to abandon FGC \cite{DiopAske09}
%\cf{convention theory mainly work on norms or also on behaviour change?  There seems a gap between norm and behaviour in FGC, can diffusion theory brigade the gap?  As suggested, community-based education program has fallen shot tin changing FGC behaviours \cite{Shel08}}
% ”I do not deny that individuals have evolved the capability to learn and apply social norms even to situations that are completely new, but there is much evidence that we are conditional followers of norms. In fact, as the experiments reported in Bicchieri and Xiao (2009) and Bicchieri and Chavez (2010) show, manipulating information produces major changes in behavior, and the existence of a social norm is no guarantee that it will be followed. The real challenge we face is to explain how normative expectations emerge or, in other words, how the beliefs that support social norms take shape." \cite{Bicc10}.

\_\_{[}CF: empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}{[}

% get info on legal situation of FGC in those countries

% "granted, recognized, and implemented by the state must not de-emphasize or delegitimize approaches recognizing the cultural significance of FGC and the potentially multiple and cascading social effects of ending the practice." \cite{(Shel08}, p. 229)

% A society may discontinue FGC practice or maintain the practice in a different form (e.g., a less harmful type of FGC) (that is cultural change in Wade's concept \cite{Wade11})

%  "Residual spatial effects of FGM have enabled us to see the inherent spatial patterns of the prevalence of FGM because the variability or noise has been removed. A more precise spatial pattern of the prevalence of FGM emerged with the estimated residual state effects compared with the crude prevalence without the control of geographic location effects." \cite{KandNwak09, p. 791}

% From modifying the practice to discarding it through a process of conversations and understanding  \cite{Mutu02, Shel08}
% findings in \cite{BoylMcMo02}
%* "These finding are particularly informative because most modernization analyses only consider attitude change. The most plausible interpretation is that attitudes change before behavior, and that our analysis captured women in the midst of change." (p. 22)
%"The greater probability of favoring FGC in Egypt was statistically significant compared to all other countries;" (p.22) (This finding is against modern theory/development theory).
%"Our findings suggest that regional development influences attitudes and behavior, but national resistance to international norms can outweigh the influence of regional development." (p.23)
%* "We hypothesized that those carriers of the scripts of the international system – education, mass media and working in the paid economy – would affect women’s attitudes and behavior with respect to FGC. These hypotheses were confirmed" (p. 23) "Older women were less likely to favor the continuation of circumcision, although each year of age increased the probability that a woman had or planned to circumcise her daughters by 6 percent. Older women may have cut their daughters before there was international pressure opposing the practice. The reverse effect for attitudes is consistent with prior findings (see Williams and Sobieszczyk, 1997). It may be an artifact of the survey technique. Older women who oppose FGC may feel freer to say so than younger women because older women are accorded considerable independence in Muslim societies (see, for example, Geiger, 1997).20" (p.24)

% "This study suggests that the adoption of a ‘modern’ lifestyle is not an inevitable result of acquiring the tools that give a person mastery over nature. Rather, the transmission of particular ideologies through global institutionalized arrangements appears to be the critical factor in abandoning practices like FGC." \cite{(BoylMcMo02}, p. 26)  What does this mean???

% National and cultural boundaries are not coextensive, when religious and community-based norms are considered \cite{BoylCorl10} (similar cultural approach \cite{SchuLien13}

% The legitimacy of international laws banning the practice of FGC"rests on its ability to demonstrate that global and local cultures are highly interpenetrated—that global culture absorbs a full range of local values." \cite{(BoylCorl10}, p 209)

% Festinger's cognitive dissonance theory:  a condition of conflict results from inconsistence between one's attitudes and one's beliefs.

%\cf{a sentence on the national FGC policy of the 4 nations and gender law}
% "In 1997, the Ministry for the Promotion of Women in Mali created a National Committee Against Violence Towards Women that links all the international organizations active in preventing FGC in Mali" "In 2001, the Kenya legislature adopted a law banning FGC." "the founding father of the country (Kenyatta, 1962) explicitly linked FGC to nationalist pride."

%"This review demonstrates the strong social pressure to which women are subjected as regards the practice of female genital mutilation. However, many other factors can contribute to eroding beliefs and arguments in favour of this practice, such as the globalization, culture and social environment of countries in the West." \cite{ReigGonz14}

% \cite{BergDeni13}: application/public policy “A realist synthesis of controlled studies to determine the effectiveness of interventions to prevent genital cutting of girls.“

%Except for Mali, all the studied nations have enacted decrees or legislation related to FGC \cite{WHO13}

Gender/feminist perspective:  \cite{Meye00} Meyers questions the idea of social norm and autonomy "It seems to me that we would need far more consensus than we presently have (or are likely to get) about human nature and social justice before we could conclude that women who opt for compliance with female genital cutting norms never do so autonomously.  We would have to be persuaded, in other words, that all women's interests are such that this decision could not accord with any woman's authentic values and desires under any circumstances."

Egypt:  "Literate, better educated and employed women are more likely to oppose FGM" \cite{VanMeek15}
Sinegal: \cite{KandComb15}
West Africa:  \cite{SipsChen12} (law and current practices)
Theory:  
% gender symbol \cite{Youn04}
% gender autonomy \cite{Meye00}: 
%“Since autonomy-augmenting educational programs are typically developed by cultural initiates who rely on traditional modes of expression and appeal to traditional values, it is reasonable to surmise that autonomy is best extended by avoiding cultural alienation and by building on women’s existing autonomy skills." 
% “autonomy-augmenting programs regard women in cultures that practice female genital cutting as self-determining individuals. …they have some understanding of what matters to them and how best to proceed in light of their values and commitments before they participate in such programs. … women who are subject to female genital cutting are not without autonomy. But this understanding of autonomy entails neither endorsement of female genital cutting nor resignation to its persistence. Since cultures that practice female genital cutting may have selectively nurtured and stifled women’s autonomy skills, and since these cultures may shield the issue of female genital cutting from exercise of autonomy skills, developing and coordinating women’s autonomy skills and extending the range of application of these skills are key to augmenting their autonomy. “
% convention or modernization theory?“ campaigns against FGC using educational, health, legal, and human rights–based approaches are at times ineffective and counterproductive when they frame the practice as a “tradition” rooted in a “primitive” and unchanging culture. We suggest that development interventions that do not address local contexts of FGC, including the complex politics and history of interventions designed to eradicate it, can in fact reify and reinscribe the practice as central to Maasai cultural identity.” \cite{WintKoom09}

% \cite{Koom14}: “ practices of female excision are so diverse that they may defy generalizable remedies”  “Rather than relying on common campaign models, transferable advocacy tools, or ‘best practices,’ scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics.”

% "Tradition, cleanliness, and virginity were the most common motives empowering the continuation of FGM/C , followed by men's wish, esthetic factors, marriage, and religion factors.... A variety of socio-cultural myths, religious misbelievers, and hygienic and esthetic concerns were behind the FGM/C. Overall, a large proportion of the participants supported the continuation of FGM/C in spite of adverse effect and sexual dysfunction associated with FGM/C." \cite{MohaHass14}

%\{cf: a few words on each nation's FGC policy}
% read \cite{MohaHass14, MuteMill16, PashPonn16, VaroFras14}

A multicultural egalitarian approach respecting both cultural identity and basic legal human rights was addressed \cite{BoylCarb10, Wade11}.  Instead of straightforward campaigns against traditional culture, "culturalconstestaion" characterized by politicized negotiation and, at times, resistance, was proposed. \cite{Koom14}.

A synthesis of context studies of Africa showed that the main factors that supported FGC were tradition, religion, and reduction of women's sexual desire, and the main factors hindered FGM/C were medical complications and prevention of sexual satisfaction. \cite{BergDeni12a}.  For example, in Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.  In Kenya, woman's decision on whether to cut their daughters' genitals were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.

"support HCPs in the integration of FGM/C preventive interventions within the public health system, to address arguments favoring medicalization, and to use data to design appropriate strategies." \cite{KaplRiba16}

% norm/attitude vs. behaviour:  attitudes towards fgc did not have a positive correlation with their behaviour:  “within each country women from more developed regions, women who worked outside the home, and educated women were less likely to favor genital cutting and less likely to have their daughters cut. Living in an urban area decreased the likelihood of favoring genital cutting, but it had no effect on behavior. “ \cite{BoylMcMo02}

%\cf{Bicchieri’s norm theory—
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do
empirical expectation:  What the responder believes others do
normative expectation: What the responder believes others think she should do
\cite{Bicc06}
First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \_\_{[}CF:i.e., normative norm?{]}
and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.  Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cf{empirical norm?}?

% attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}
\cite{UNFPA14, UNIC16}
\subsection{suggestions and Limitations}\label{suggestions-and-Limitations}

% cultural sensitivity:  It suggests that "legislative efforts to protect women's health may remain ineffective with
out structured efforts between health systems, governments or legal institutions and the cultural society." \cite{Iyio12} and 
% through laws \cite{AloGbad11}

% “ the effectiveness of interventions was hampered by a general lack of information. However, through the realist synthesis we identified that all of the interventions were based on a theory that dissemination of information improves cognitions about FGM/C, but the interventions’ success was contingent upon a range of contextual factors. “ \cite{BergDeni12a}

% Education programs aimed to empower women through a broad range of educational and health-promoting activities by improvements in knowledge about and critical attitudes toward FGC had impact on behaviors and attitudes. \cite{DiopAske09}.  Legal measures must combine with social measures to effectively eradicate FGC and communities practising FGC must be involved in the planning and implementation of  intervention of FGC elimination \cite{AkoAwke09}

% \cite{BrowBeec13}:  their questions of the 4 current approaches (sexuality, human rights, etc) and their suggestions

% attitudes change may be followed by behaviour change, but more slowly \cite{BoylMcMo02}
% Limitations:  without incorporating national factor in this study.

% \cite{Meye00}:  rational model vs. hierarchical identification model; and plus oppression social context.  That is, knowing ≠ abling ≠ wanting ≠ doing.  How to apply this concept to theories of feminist/gender, modernization and convention.

%\cite{JohaDiop13}:  Some of the most common approaches (1) health risk approaches, (2) conversion of excisers, (3) training of health professionals as change agents, (4) alternative rituals, (5) community-led approaches, (6) public statements, and (7) legal measures.

% Based on our findings, are there any survey questions DHS should have included but did not?  Did our findings see something like group/community identity, womanhood \cite{Koom14}?
% \cite{Koom14}: “ an Aang Serian activist who had addressed a village meeting saying, ‘The world is changing and the Maasai must change with it or risk dying out.’ They argued that these appeals to cultural survival were much more persuasive and meaningful to them than the ‘foreign’ language of rights.”

Analyzing why MC is a much accepted behaviour might help us to re-think the meanings of FGC (see \cite{DarbSvob07}) and, if, to certain extent, to accept a form of FGC practice (e.g, a "nick" \cite{Wade11}).

% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cf{I don’t know if I want to cite \cite{EffeVogt15}.  It doesn’t cite some very important papers which had addressed the concerns/questions the paper suggested}).

% \cf{TOSTAN uses a strategy based on conventional theory’s critical mass to eradicate FGC (see (Wils13}}
 * Festinger (1950?):  Social pressure in informal groups

% Latikin 1995:  Norms o unsafe behaviours are not trivially changed trough information.
% Beliefs are susceptible social confirmation (Centola)
% Small world and "hubs" accelerate diseases but slow down behaviours change (Centola)
% a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see \cite{BoylCorl10}, table 1)

% suggestions: https://www.theguardian.com/global-development/2018/feb/06/battling-fgm-uganda-kenya-zero-tolerance-female-genital-mutilation "Thomas Lotongar, assistant chief in Konya Division in Kenya, says more rescue centres are needed, and schools must act as sanctuaries for girls to avoid FGM.  “We need to find more alternatives and livelihood projects like tailoring[or] salon work to empower our girls who run away from the practice to the rescue centres.”"

\subsection{Conclusion}\label{Conclusion}

%"targeting women and girls is a sound investment, but outcomes are dependent on integrated approaches and the protective umbrella of policy and legislative actions" to change gender norms among women and girls \cite{KeleFran}. 
Reasons of FGC is not universal and different from community to community and from society to society; campaigns of reducing and preventing FGC need to incorporate with local history and believes.
% call for eduction in communication of FGC:  \cite{Koom14, Meye00}}

Eradication of FGC is more controversial than expected.  FGC practice and its nature tended to be morally embraced, and deeply internalized \cite{SchuLien13}.  Decisions on undergoing FGC was often a result of a collective practice than an individual choice \cite{Dell04, Hayf06, FreyJoh07, KandMwek09, Mack96, Mack06, ShelHern06, ShelWand11, YirgKass12}. Public denouncements and anti-FGC laws could push FGC into private practices \cite{GaluKama15, VanCoen17}.  Given the regional FGC prevalence, variations among countries and the social context of FGC practices (e.g., see Burkina Faso \cite{KarmKand11} vs. Nigeria \cite{KandNwak09}), a “one size fits all” strategy for the abandonment of FGMC would not be effective \cite{JohaDiop13, YodeWang13}.

It is inevitable to compare male circumcision to female genital cutting and question how male circumcision gain its cultural recognition but not FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} may be an alternative without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative thought.)

--- questions worth addressing
1. Is there a tipping point?  Can our findings disclose some ideas on fgc intervention in terms of behavioural change in order to reach a tipping point?
\subsection{Funding}\label{Funding}

CF was funded by a grant from the James S. McDonnell foundation. JD holds a New Investigator award from the Canadian Institutes of Health Research.

\subsection{Conflicts of interest}\label{Conflicts-of-Interest}

The James S. McDonnell foundation and the Canadian Institutes of Health Research had no role in study design; collection, analysis, and interpretation of data; the writing of the manuscript; or in the decision to submit the manuscript for publication.  The views expressed herein do not necessarily represent the views of the founding bodies.

\subsection{Authors' contributions}\label{Authors'-contributions}

\subsubsection{Disclaimer}\label{disclaimer}

The findings and conclusions of this article are those of the authors
and do not necessarily represent the views of the funding agency.

\subsubsection{Acknowledgement}\label{Acknowledgement}
Ben Bolker,  Marta Wayne

\subsubsection{Appendix}\label{appendix-1}

\bibliography{refs}

\end{document}

### 2018-06-13 manuscript.tex
Autocommit (fgc)
Update manuscript.tex

@@
 There are at least three main theoretical perspectives from outside the communities
-shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  conventional theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
+shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
 When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
++ \cite{Shel-Wand11}
 
@@
 ===============================
+Concerns:
+
+We did not consider ages of women's daughters.
+For those whose daufhter is over 15(?), they were not likely to fgc them, but it doesnt' mean they are againt fgc.
+It might just mean the daughters were too old to be fgced.
+===============================
 
@@
 %Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics \cite{BrowBeec13}.
+ \cite{Shel-Wand11}:  supporting Mackie's convetion theory "expections regarding fgc are interdependent...."
 

### 2018-06-13 manuscript.tex
Update manuscript.tex

@@
 When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
-+ \cite{Shel-Wand11}
++ \cite{Shel-Wand11}:  Mackie's social convetional theory was supported in their findings; futher, they proposed that fgc practice is beyond the belief of marriage advanges; it goes beyond.
+FGC allows women to gain social capitals and access to networks.
+Their findings also suggested that the main deterent to marriges was not men's refusal of non-fgc women, but hostality and discrimination from fgc women to non fgc women.
 

### 2018-06-14 manuscript.tex
Update manuscript.tex

@@
 \subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
+---- benefirs of fgc is value (what fulfilment/benefits/positivity someone get by performing certain behaviors), not attitude,
+
 The main constructs to test the three theories of FGC practices(e.g., conventions, modernization, and feminism) are inferred from the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm).

### 2018-06-16 manuscript.tex
Update manuscript.tex

@@
 
+\cite{EffeVoge15}:  Each family may have its own threshold of fgc.
+I think fgc norm has shifted from marraige advantage of social capital of social networking as proposed by Shell-Duncon and her colleagues \cite{ShelWand11}.
+To elaborate the shifted values of fgc, what it imply and how to apply the change to policy.
+
 % suggestions: https://www.theguardian.com/global-development/2018/feb/06/battling-fgm-uganda-kenya-zero-tolerance-female-genital-mutilation "Thomas Lotongar, assistant chief in Konya Division in Kenya, says more rescue centres are needed, and schools must act as sanctuaries for girls to avoid FGM.

### 2018-07-11 manuscript.tex
Update manuscript.tex

@@
 \subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
----- benefirs of fgc is value (what fulfilment/benefits/positivity someone get by performing certain behaviors), not attitude,
 
@@
 \cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
+\cite{TerrHogg96}:  subjective norm on attitude and planned behavior
+\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.
+But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
 

### 2018-07-12 manuscript.tex
Update manuscript.tex

@@
 
-\subsubsection{Objective}\label{objective}
+\subsubsection{}\label{objective}
 
@@
 In this study, we constructed women's fgc attitudes based on the xx questions of FGC benefits in DHS, women's gender attitudes based on xx questions of domestic violence; the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.
+
+(see \cite{IloDarf18, PashPonn16} for measurements of the thoery of planned behaviors on fgc)
 
@@
 \cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
-\cite{TerrHogg96}:  subjective norm on attitude and planned behavior
+--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
+\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
 \cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.
@@
 % religion:  \cite{KarmKand11}
---- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
 

### 2018-07-16 manuscript.tex
Update manuscript.tex

@@
 
-It was estimated that more than 200 million women, of which 44 millions were girls under age 15, have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16}, and the actual numbers might in fact higher \cite{GaluKama15} (more?).
+It was estimated that more than 200 million women, of which 44 millions were girls under age 15, have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (to update), and the actual numbers might in fact higher \cite{GaluKama15} (more?).
 The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update).
@@
 \subsection{Research Questions}\label{research-questions}
-There are two main research questions in this study:  attitudes of FGC benefits (see the list of FGC benefits at table xx) in association with attitudes of FGC continuance; and attitudes of FGC benefits in association with intention (planned behavior) of cutting daughters and with attitudes of FGC continuance.
+There are two main research questions in this study:  attitudes of FGC benefits (see the list of FGC benefits at table xx) in association with attitudes of FGC continuance; and attitudes of FGC benefits and of FGC continuance in association with intention (planned behavior) of cutting daughters.
 The first question is referred to a FGC future model (FGC attitude model?), and the second a FGC daughter model (FGC intention model?).
 
-\_\_{[}CF: how about the third model xx basic daughter model?  A few sentence of the differences between FGC future model and FGC daughter model{]}
+\_\_{[}CF: how about the third model xx basic daughter model without counting attitudes of FGC continuance ?  A few sentence of the differences between FGC future model and FGC daughter model{]}
 
@@
 
-The main constructs to test the three theories of FGC practices(e.g., conventions, modernization, and feminism) are inferred from the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm).
-The planned behavior theory proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
+We conceptualized the main constrcuts in testing the three theories of FGC practice aformentioned based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92}.
+(to confirm and update) The heory of planned behavior proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
 Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.

### 2018-07-19 manuscript.tex
Update manuscript.tex

@@
 
-We conceptualized the main constrcuts in testing the three theories of FGC practice aformentioned based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92}.
-(to confirm and update) The heory of planned behavior proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
+The main constrcuts of analyzing FGC practice in this study were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92}.
+(to confirm and update) The heory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
 Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.
-In this study, we constructed women's fgc attitudes based on the xx questions of FGC benefits in DHS, women's gender attitudes based on xx questions of domestic violence; the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.
+In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, media use and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.
 
@@
 
-The main response variables were woman's opinion (or attitude?) on whether they think FGC should be continued in the FGC future model and woman's intention of cut their daughters in the daughter's FGC status model.
-The main predictors in both of the models were beliefs of FGC benefits (see the list of FGC benefits at table-- in Appendix) and woman's FGC status.
+The main response variables were woman's attitude on whether they think FGC should be continued in the FGC future model and woman's intention of cutting their daughters in the daughter's FGC status model.
+The main predictors in both of the models were attitudes of FGC benefits and woman's FGC status.
 We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.

### 2018-08-28 manuscript.tex
Update manuscript.tex

@@
 \subsection{Research Questions}\label{research-questions}
-There are two main research questions in this study:  attitudes of FGC benefits (see the list of FGC benefits at table xx) in association with attitudes of FGC continuance; and attitudes of FGC benefits and of FGC continuance in association with intention (planned behavior) of cutting daughters.
-The first question is referred to a FGC future model (FGC attitude model?), and the second a FGC daughter model (FGC intention model?).
-
-\_\_{[}CF: how about the third model xx basic daughter model without counting attitudes of FGC continuance ?  A few sentence of the differences between FGC future model and FGC daughter model{]}
+The main focus of this study is to analyze attitudes of FGC benefits (see the list of FGC benefits at table xx) and of FGC continuance in association with intention (planned behavior) to cut daughters.
+Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits and intention (planned behavior) of cutting daughters in the hope of???
 
@@
 
-The were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}.
-We used DHS data for this study because of certain questionnaires for this study.
-We first chose nations with high FGC prevalence \cite{UNIC16}, then their DHS surveys with modules of FGC benefits, and index of gender awareness.
-The following countries met the criteria:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-We did not use a newer dataset from those countries due to the lack of FGC benefits information in the newer surveys (checked in 09/17).
+There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}.
+We used DHS data for this study because of certain questionnaires only available in DHS.
+Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
+We were not able to use newer dataset from those countries due to the lack of FGC benefits modules (checked in 09/17).
 

### 2018-08-28 manuscript.tex
Update manuscript.tex

@@
 The main focus of this study is to analyze attitudes of FGC benefits (see the list of FGC benefits at table xx) and of FGC continuance in association with intention (planned behavior) to cut daughters.
-Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits and intention (planned behavior) of cutting daughters in the hope of???
+Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits and intention (planned behavior) of cutting daughters (structural models) in the hope of???
 

### 2018-08-28 hist.R
Meeting, random histogram example

@@ -1,0 +1,4 @@
+numComm <- 2222
+
+prev <- rbeta(numComm, 0.04, 0.08)
+hist(prev)

### 2018-08-28 catPCA.R
Sum quants AFTER PCA

@@ -11,8 +11,6 @@ quant <- na.omit(quant)
 
 print(summary(quant))
 
-quant$sum <- rowSums(quant)
-
 pc <- prcomp(quant, scale=TRUE, center=FALSE)
 print(pc$rotation)
 plot(pc)
@@ -21,6 +19,8 @@ scores <- as.data.frame(predict(pc))
 scores <- within(scores, {
 	PC1 <- PC1/mean(PC1)
 })
+
+quant$sum <- rowSums(quant)
 
 quant$score <- scores$PC1
 

### 2018-08-30 manuscript.tex
Update manuscript.tex

@@
 Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-We were not able to use newer dataset from those countries due to the lack of FGC benefits modules (checked in 09/17).
+We did not analyze the newest dataset due to the lack of FGC benefits modules (checked in 09/17).
 
-\_\_{[}CF: none of the countries had GPS data.
-Kenya 2014, Mali 2012-3 and Nigeria 2013 have no value set {]}.
-Sierra Leone 2013 does.
-Should we use Sierra Leone 2008 or 2013?
-2008 data is closer to the other data in terms of time period.
-It seems more convincing to if the data is all in a similar time span.
-On the other hand, it is a much recent data and provides a more updated view{]}.
-
-We included all the women despite of their FGC status and with or without daughters in the future model because our main interest was to study women's attitudes towards FGC continuance in general and their opinions counted as community attitudes towards this practice.
-In the daughters model, we included only women with uncircumcised daughters because we were interested in mother's intention of whether to cut their daughters; and that resulted in xxx, xxx, xxx and xxx in the future model, and xxx, xxx, xxx and xxx in the daughter model respectively.
+Only women with daughters to be considered for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
 
@@
 
-The main constrcuts of analyzing FGC practice in this study were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92}.
-(to confirm and update) The heory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
+The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm and update).
+The heory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
 Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.
@@
 % Kenya and Nigeria both were under %30 vs. Mali and Sierra Leon over %80.  Are they different in terms of norm and beahvior?  To discuss this in the discussion.
+
+In the results of association of cutting daughter and mother's fgc status, the individual model and the community model were consistent; the effect of fgc prevalence among mothers, attitudes of fgc benefits and education were clear at the community level but not wealth, gender awareness and media consumption were not clear at the community level (meaning media use, gender awareness and education were less homogeneous?)
+
+In the results of association of fgc future and mother's fgc status,
 

### 2018-08-31 daughterfgc.R
Autocommit (fgc)

@@ -41,6 +41,36 @@ scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
   return(tempdat)
 }
 
+
+beneframe <- scoring(Answers, "bene", rightfactor, Answers$id)
+attframe <- scoring(Answers, "att", yesnodk, Answers$id)
+mediaframe <- scoring(Answers, "media", rightfactor, Answers$id)
+
+
+covDat <- (Answers
+	%>% select(fgc, clusterId, age, id, edu, wealth, ethni
+		, religion , maritalStat, job, urRural
+		)
+	%>% left_join(., beneframe, by = "id")
+	%>% left_join(., attframe, by = "id")
+	%>% left_join(., mediaframe, by = "id")
+	%>% mutate(fgcstatusMom = fgc
+		, fgc = rightfactor(fgc)
+		, edu = rightfactor(edu)
+		, edu = edu / mean(edu, na.rm = TRUE)
+		)
+	%>% group_by(clusterId)
+	%>% mutate(group_bene = mean(bene, na.rm = TRUE)
+		, group_att = mean(att, na.rm = TRUE)
+		, group_media = mean(media, na.rm = TRUE)
+		, group_fgc = mean(fgc, na.rm = TRUE)
+		, group_edu = mean(edu, na.rm = TRUE)
+		, group_wealth = mean(wealth, na.rm = TRUE)
+		)
+  %>% select(-fgc)
+)
+
+
 responseDat <- (Answers 
   %>% select(c(daughterToFgc,id)) 
   %>% mutate(futurefgcDau = yesnodkFactor(daughterToFgc)
@@ -48,43 +78,11 @@ responseDat <- (Answers
   %>% select(-c(daughterToFgc))
 )
 
-covDat <- (Answers
-  %>% select(c(fgc,clusterId,age,id,edu,wealth,ethni
-    ,religion,maritalStat, job,urRural,CC,beneAcceptance,attArgue,mediaRadio 
-    ))
-  %>% mutate(fgcstatusMom = rightfactor(fgc))
-  %>% select(-fgc)
-)
-
-tempcombDat <- (left_join(responseDat,covDat,by="id") 
+combinedDat <- (left_join(responseDat,covDat,by="id") 
   %>% filter(complete.cases(.)) 
-  %>% select(-c(beneAcceptance,attArgue,mediaRadio))
 )
 
 
[…]

### 2018-08-31 futurefgc.R

@@ -5,6 +5,11 @@ yesnodk <- function(x){
   return(y)
 }
 
+yesnodkFactor <- function(x){
+  y <- factor(x,levels(x)[c(1,3,2)])
+  return(y)
+}
+
 contfgc <- function(x){
   y <- factor(x,levels(x)[c(2,3,1)])
   return(y)
@@ -14,78 +19,76 @@ rightfactor <- function(x){
   y <- as.numeric(x)-1
   return(y)
 }
-# aa <- names(table(Answers$clusterId)[table(Answers$clusterId)>1])
-# 
-# Answers <- Answers %>% filter(clusterId %in% aa)
 
 scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
-  if(is.null(colnam)) colnam = type
-  if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
-  if(is.null(idvec)) idvec <- 1:nrow(dat)
-  typeNames <- grepl(type, names(Answers))
-  cols <- sum(typeNames)
-  tempdat <- (dat[typeNames] 
-              %>% rowwise()
-              %>% summarise_each(funs(funct)) 
-              %>% mutate(id=idvec) 
-              %>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
-                            , id=id
-              ) 
-              %>% ungroup() 
-              %>% mutate(Score=total/mean(total,na.rm=TRUE)) 
-              %>% select(-total)
-  )
-  colnames(tempdat) <- c("id", colnam)
-  return(tempdat)
+	if(is.null(colnam)) colnam = type
+	if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
+	if(is.null(idvec)) idvec <- 1:nrow(dat)
+	typeNames <- grepl(type, names(Answers))
+	cols <- sum(typeNames)
+	tempdat <- (dat[typeNames] 
+		%>% rowwise()
+		%>% summarise_each(funs(funct)) 
+		%>% mutate(id=idvec) 
+		%>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
+			, id=id
+			) 
+		%>% ungroup() 
+		%>% mutate(Score=total/mean(total,na.rm=TRUE)) 
+		%>% select(-total)
+	)
+	colnames(tempdat) <- c("id", colnam)
+	return(tempdat)
 }
 
[…]

### 2018-08-31 futurefgcDau.R

@@ -5,7 +5,6 @@ yesnodk <- function(x){
   return(y)
 }
 
-
 yesnodkFactor <- function(x){
   y <- factor(x,levels(x)[c(1,3,2)])
   return(y)
@@ -20,78 +19,69 @@ rightfactor <- function(x){
   y <- as.numeric(x)-1
   return(y)
 }
-# aa <- names(table(Answers$clusterId)[table(Answers$clusterId)>1])
-# 
-# Answers <- Answers %>% filter(clusterId %in% aa)
-
 
 scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
-  if(is.null(colnam)) colnam = type
-  if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
-  if(is.null(idvec)) idvec <- 1:nrow(dat)
-  typeNames <- grepl(type, names(Answers))
-  cols <- sum(typeNames)
-  tempdat <- (dat[typeNames] 
-    %>% rowwise()
-    %>% summarise_each(funs(funct)) 
-    %>% mutate(id=idvec) 
-    %>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
-      , id=id
-    ) 
-    %>% ungroup() 
-    %>% mutate(Score=total/mean(total,na.rm=TRUE)) 
-    %>% select(-total)
-  )
-  colnames(tempdat) <- c("id", colnam)
-  return(tempdat)
+	if(is.null(colnam)) colnam = type
+	if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
+	if(is.null(idvec)) idvec <- 1:nrow(dat)
+	typeNames <- grepl(type, names(Answers))
+	cols <- sum(typeNames)
+	tempdat <- (dat[typeNames] 
+		%>% rowwise()
+		%>% summarise_each(funs(funct)) 
+		%>% mutate(id=idvec) 
+		%>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
+			, id=id
+		) 
+		%>% ungroup() 
+		%>% mutate(Score=total/mean(total,na.rm=TRUE)) 
+		%>% select(-total)
+		)
+	colnames(tempdat) <- c("id", colnam)
+	return(tempdat)
 }
 
-responseDat <- (Answers 
-  %>% select(c(daughterToFgc,id)) 
-  %>% mutate(futureDau = yesnodkFactor(daughterToFgc)
-    ) 
[…]

### 2018-08-31 iso.R

@@ -19,16 +19,16 @@ isoList <- lapply(predNames, function(n){
 print(
 grid.arrange(varPlot(isoList[[1]],P=varlvlsum$`Pr(>Chisq)`[1]),
              varPlot(isoList[[2]],P=varlvlsum$`Pr(>Chisq)`[2]),
-             varPlot(isoList[[3]],P=varlvlsum$`Pr(>Chisq)`[3]),
-             varPlot(isoList[[4]],P=varlvlsum$`Pr(>Chisq)`[4]),
-             varPlot(isoList[[5]],P=varlvlsum$`Pr(>Chisq)`[5]),
-             varPlot(isoList[[6]],P=varlvlsum$`Pr(>Chisq)`[6]),
-             varPlot(isoList[[7]],P=varlvlsum$`Pr(>Chisq)`[7]),
-             varPlot(isoList[[8]],P=varlvlsum$`Pr(>Chisq)`[8]),
-             varPlot(isoList[[9]],P=varlvlsum$`Pr(>Chisq)`[9]),
-             varPlot(isoList[[10]],P=varlvlsum$`Pr(>Chisq)`[10]),
-             varPlot(isoList[[11]],P=varlvlsum$`Pr(>Chisq)`[11]),
-             varPlot(isoList[[12]], P=varlvlsum$`Pr(>Chisq)`[[12]]),
+             varPlot(isoList[[3]],P=varlvlsum$`Pr(>Chisq)`[4]),
+             varPlot(isoList[[4]],P=varlvlsum$`Pr(>Chisq)`[5]),
+             varPlot(isoList[[5]],P=varlvlsum$`Pr(>Chisq)`[6]),
+             varPlot(isoList[[6]],P=varlvlsum$`Pr(>Chisq)`[7]),
+             varPlot(isoList[[7]],P=varlvlsum$`Pr(>Chisq)`[8]),
+             varPlot(isoList[[8]],P=varlvlsum$`Pr(>Chisq)`[9]),
+             varPlot(isoList[[9]],P=varlvlsum$`Pr(>Chisq)`[10]),
+             varPlot(isoList[[10]],P=varlvlsum$`Pr(>Chisq)`[11]),
+             varPlot(isoList[[11]],P=varlvlsum$`Pr(>Chisq)`[12]),
+             varPlot(isoList[[12]], P=varlvlsum$`Pr(>Chisq)`[[13]]),
              nrow=4,ncol=3)
 )
 
@@ -44,12 +44,12 @@ if(nrow(varlvlsum)==13){
[…]

### 2018-08-31 daughterfgc.R
the repo is a mess

@@ -46,6 +46,7 @@ beneframe <- scoring(Answers, "bene", rightfactor, Answers$id)
 attframe <- scoring(Answers, "att", yesnodk, Answers$id)
 mediaframe <- scoring(Answers, "media", rightfactor, Answers$id)
 
+print(summary(beneframe))
 
 covDat <- (Answers
 	%>% select(fgc, clusterId, age, id, edu, wealth, ethni

### 2018-08-31 df.R

@@ -6,4 +6,42 @@ Answers <- (Answers
   %>% mutate(id=1:nrow(.))
   )
 
+scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
+	if(is.null(colnam)) colnam = type
+	if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
+	if(is.null(idvec)) idvec <- 1:nrow(dat)
+	typeNames <- grepl(type, names(Answers))
+	cols <- sum(typeNames)
+	tempdat <- (dat[typeNames] 
+		%>% rowwise()
+		%>% summarise_each(funs(funct)) 
+		%>% mutate(id=idvec) 
+		%>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
+			, id=id
+			)
+		%>% ungroup() 
+		%>% mutate(Score=total/mean(total,na.rm=TRUE)) 
+		%>% select(-total)
+		)
+	colnames(tempdat) <- c("id", colnam)
+	return(tempdat)
+}
+																			 
+																			 
+beneframe <- scoring(Answers, "beneframe", rightfactor, Answers$id)
+attframe <- scoring(Answers, "attframe", yesnodk, Answers$id)
+mediaframe <- scoring(Answers, "mediaframe", rightfactor, Answers$id)
+
+Answers <- (Answers
+	%>% left_join(., beneframe)
+	%>% left_join(., attframe)
+	%>% left_join(., mediaframe)
+	%>% group_by(clusterId)
+	%>% mutate(group_benef = mean(beneframe, na.rm = TRUE)
+		, group_attf = mean(attframe, na.rm = TRUE)
+		, group_mediaf = mean(mediaframe, na.rm = TRUE)
+		)
+)
+
 # rdsave(Answers)
+saveRDS(Answers, rdsname)

### 2018-08-31 prevalance.R

@@ -1,0 +1,83 @@
+library(dplyr)
+library(ggplot2)
+
+for (r in grep("Rds$", input_files, value=TRUE)){
+  if (exists("dat"))
+    dat <- rbind(dat, readRDS(r))
+  else
+    dat <- readRDS(r)
+}
+
+yesnodk <- function(x){
+  y <- as.numeric(factor(x,levels(x)[c(1,3,2)]))-1
+  return(y)
+}
+
+yesnodkFactor <- function(x){
+  y <- factor(x,levels(x)[c(1,3,2)])
+  return(y)
+}
+
+contfgc <- function(x){
+  y <- factor(x,levels(x)[c(2,3,1)])
+  return(y)
+}
+
+rightfactor <- function(x){
+  y <- as.numeric(x)-1
+  return(y)
+}
+
+scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
+	if(is.null(colnam)) colnam = type
+	if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
+	if(is.null(idvec)) idvec <- 1:nrow(dat)
+	typeNames <- grepl(type, names(Answers))
+	cols <- sum(typeNames)
+	tempdat <- (dat[typeNames] 
+	%>% rowwise()
+	%>% summarise_each(funs(funct)) 
+	%>% mutate(id=idvec) 
+	%>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
+		, id=id
+		)		 
+	%>% ungroup() 
+	%>% mutate(Score=total/mean(total,na.rm=TRUE)) 
+	%>% select(-total)
+		)
+	colnames(tempdat) <- c("id", colnam)
+	return(tempdat)
+}
+
+print(summary(dat))
+
+groupdat <- (dat
+	%>% select(fgc, daughterToFgc, clusterId, age, id, edu, wealth, ethni
+		, religion, maritalStat, job, urRural
+		, beneframe, attframe, mediaframe 
+	)
+	%>% mutate(fgcstatusMom = fgc
+		, fgc = rightfactor(fgc)
+		, edu = rightfactor(edu)
+		, edu = edu / mean(edu, na.rm = TRUE)
+		, daughterToFgc = yesnodk(daughterToFgc)
+		)
+	%>% group_by(clusterId)
+	%>% summarise(group_fgc = mean(fgc, na.rm = TRUE)
+		, group_daughterToFgc = mean(daughterToFgc, na.rm = TRUE)
[…]

### 2018-08-31 prevalence.R
Autocommit (fgc)

@@ -75,7 +75,10 @@ groupdat <- (dat
 
 print(hist(groupdat$group_fgc))
 print(hist(groupdat$group_daughterToFgc))
-#print(hist(groupdat$group_bene))
+
+## Craziness!
+print(hist(groupdat$group_bene))
+
 #print(hist(groupdat$group_att))
 #print(hist(groupdat$group_media))
 #print(hist(groupdat$group_edu))

### 2018-09-02 community.R
Autocommit (fgc)

@@ -5,27 +5,6 @@ library(dplyr)
 Answers <- (Answers 
   %>% mutate(id=1:nrow(.))
   )
-
-scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
-	if(is.null(colnam)) colnam = type
-	if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
-	if(is.null(idvec)) idvec <- 1:nrow(dat)
-	typeNames <- grepl(type, names(Answers))
-	cols <- sum(typeNames)
-	tempdat <- (dat[typeNames] 
-		%>% rowwise()
-		%>% summarise_each(funs(funct)) 
-		%>% mutate(id=idvec) 
-		%>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
-			, id=id
-			)
-		%>% ungroup() 
-		%>% mutate(Score=total/mean(total,na.rm=TRUE)) 
-		%>% select(-total)
-		)
-	colnames(tempdat) <- c("id", colnam)
-	return(tempdat)
-}
 																			 
 																			 
 beneframe <- scoring(Answers, "beneframe", rightfactor, Answers$id)

### 2018-09-02 recode.R

@@ -55,4 +55,8 @@ Answers <- within(Answers, {
 	clusterId <- as.factor(clusterId)
 })
 
+
+
+
+
 # rdsave(Answers)

### 2018-09-02 recodeFuns.R

@@ -1,3 +1,5 @@
+## Helper functions to recode DHS answers
+
 
 tfun <- function(q, qmax, qmin=-1e7, dk=98, nalist=c(99)){
 	q[q==dk] <- qmax
@@ -59,5 +61,46 @@ tableRecode <- function(v, tableName,
 		if(length(levels(w))>maxCat)
 			stop("Too many levels", paste(levels(w), collapse=" : "))
 	return(w)
+}
+
+scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
+  if(is.null(colnam)) colnam = type
+  if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
+  if(is.null(idvec)) idvec <- 1:nrow(dat)
+  typeNames <- grepl(type, names(Answers))
+  cols <- sum(typeNames)
+  tempdat <- (dat[typeNames] 
+              %>% rowwise()
+              %>% summarise_each(funs(funct)) 
+              %>% mutate(id=idvec) 
+              %>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
+                            , id=id
+              )
+              %>% ungroup() 
+              %>% mutate(Score=total/mean(total,na.rm=TRUE)) 
+              %>% select(-total)
+  )
+  colnames(tempdat) <- c("id", colnam)
+  return(tempdat)
+}
+
+yesnodk <- function(x){
+  y <- as.numeric(factor(x,levels(x)[c(1,3,2)]))-1
+  return(y)
+}
+
+yesnodkFactor <- function(x){
+  y <- factor(x,levels(x)[c(1,3,2)])
+  return(y)
+}
+
+contfgc <- function(x){
+  y <- factor(x,levels(x)[c(2,3,1)])
+  return(y)
+}
+
+rightfactor <- function(x){
+  y <- as.numeric(x)-1
+  return(y)
 }
 

### 2018-09-05 recode.R
Autocommit (fgc)

@@ -18,24 +18,23 @@ Answers <- (Answers
 
 # Ideally, I like to have a variable as daughterFGC (daughter's FGC status) which involves a few variables:  numDaughterFgced (already cut; 95 and 0=none cut), and daughterToFgc.  Those variables provides answers of yes (already cut), no (none cut), plan to cut, plan not to be cut, and don't know the plan yet.  I like to make it a single outcome measurement with 6 levels: yes/to be cut, yes/not to be cut, no/to be cut, no/not to be cut, yes/don't know, no/don't know.
 
-Answers <- within(Answers, {
+Answers <- (Answers
+	%>% mutate(daughterFgced = ifelse(numDaughterFgced == 95, "No", "Yes")
+		, daughterFgced = ifelse(numDaughterFgced == 0, "Yes", daughterFgced)
+		, daughterFgced = factor(daughterFgced)
+		, continueFgc = ifelse(continueFgc == "Don't know", "Depends", as.character(continueFgc))
+		, continueFgc = factor(continueFgc)
+		, daughterNotFgced = ifelse(daughterNotFgced == "Don't know", NA, as.character(daughterNotFgced))
+		, daughterNotFgced = factor(daughterNotFgced)
+		, CC = substring(survey, 1, 2)
+		, CC = factor(CC)
+		, recode = substring(survey, 3, 3)
+		, recode = as.numeric(recode)
+		)
+)
 
-	# make numDaughterFgced as a binary:
-	daughterFgced <- ifelse(numDaughterFgced==95, "No", "Yes")
-	daughterFgced[numDaughterFgced==0] <- "Yes"
-	daughterFgced <- as.factor(daughterFgced)
 
-	if(sum(!is.na(continueFgc))>0){
-		levels(continueFgc)[levels(continueFgc)=="Don't know"] <- "Depends"
-	}
-
-	if(sum(!is.na(daughterNotFgced))>0){
-		levels(daughterNotFgced)[levels(daughterNotFgced)=="Don't know"] <- NA}
-})
-
-Answers <- within(Answers, {
-	CC <- substring(survey, 1, 2)
-	CC <- as.factor(CC)
+aa <- within(Answers, {
 	recode <- as.numeric(substring(survey, 3, 3))
 })
 

### 2018-09-05 recode.R
recoding complete

@@ -18,7 +18,7 @@ Answers <- (Answers
 
 # Ideally, I like to have a variable as daughterFGC (daughter's FGC status) which involves a few variables:  numDaughterFgced (already cut; 95 and 0=none cut), and daughterToFgc.  Those variables provides answers of yes (already cut), no (none cut), plan to cut, plan not to be cut, and don't know the plan yet.  I like to make it a single outcome measurement with 6 levels: yes/to be cut, yes/not to be cut, no/to be cut, no/not to be cut, yes/don't know, no/don't know.
 
-Answers <- (Answers
+aa <- (Answers
 	%>% mutate(daughterFgced = ifelse(numDaughterFgced == 95, "No", "Yes")
 		, daughterFgced = ifelse(numDaughterFgced == 0, "Yes", daughterFgced)
 		, daughterFgced = factor(daughterFgced)
@@ -30,32 +30,13 @@ Answers <- (Answers
 		, CC = factor(CC)
 		, recode = substring(survey, 3, 3)
 		, recode = as.numeric(recode)
+		, region = factor(paste(CC, region, sep="_"))
+		, clusterId = factor(paste(survey, clusterId, sep="_"))
+	  , ethni = factor(paste(CC, ethni, sep="_"))
+    , religion = tableRecode(religion, "religion", maxCat=4)
+    , maritalStat = tableRecode(maritalStat, "partnership", maxCat=4)
+    , wealth = wealth/100000
 		)
 )
-
-
-aa <- within(Answers, {
-	recode <- as.numeric(substring(survey, 3, 3))
-})
-
-Answers <- within(Answers, {
-	region <- as.factor(paste(CC, region, sep="_"))
-	clusterId <- as.factor(paste(survey, clusterId, sep="_"))
-
-	ethni <- as.factor(paste(CC, ethni, sep="_"))
-
-	religion <- tableRecode(religion, "religion", maxCat=4)
-
-	maritalStat <- tableRecode(maritalStat, "partnership", maxCat=4)
-
-	wealth <- wealth/100000
-
-	# Make cluster ID into a factor!
-	clusterId <- as.factor(clusterId)
-})
-
-
-
-
 
 # rdsave(Answers)

### 2018-09-06 community.R
Autocommit (fgc)

@@ -5,22 +5,29 @@ library(dplyr)
 Answers <- (Answers 
   %>% mutate(id=1:nrow(.))
   )
-																			 
-																			 
-beneframe <- scoring(Answers, "beneframe", rightfactor, Answers$id)
-attframe <- scoring(Answers, "attframe", yesnodk, Answers$id)
-mediaframe <- scoring(Answers, "mediaframe", rightfactor, Answers$id)
+
+# number of Yes/ total and then divided by the mean. 
+# mean score will be 1
+beneframe <- scoring(Answers, "bene", rightfactor, Answers$id)
+attframe <- scoring(Answers, "att", yesnodk, Answers$id)
+mediaframe <- scoring(Answers, "media", rightfactor, Answers$id)
 
 Answers <- (Answers
 	%>% left_join(., beneframe)
 	%>% left_join(., attframe)
 	%>% left_join(., mediaframe)
 	%>% group_by(clusterId)
-	%>% mutate(group_benef = mean(beneframe, na.rm = TRUE)
-		, group_attf = mean(attframe, na.rm = TRUE)
-		, group_mediaf = mean(mediaframe, na.rm = TRUE)
-		)
+	%>% mutate(group_fgc = mean(fgc, na.rm = TRUE)
+      , group_futurefgcDau = mean(futurefgcDau01, na.rm = TRUE)
+	    , group_bene = mean(bene, na.rm = TRUE)
+	    , group_att = mean(att, na.rm = TRUE)
+	    , group_media = mean(media, na.rm = TRUE)
+	    , group_edu = mean(edu, na.rm = TRUE)
+	    , group_wealth = mean(wealth, na.rm = TRUE)
 )
+)
+
+print(summary(Answers))
 
 # rdsave(Answers)
 saveRDS(Answers, rdsname)

### 2018-09-06 daughterfgc_full_clmm.R

@@ -1,27 +1,22 @@
 library(ordinal)
 library(splines)
 
-for (r in grep("Rds$", input_files, value=TRUE)){
-  if (exists("dat"))
-    dat <- rbind(dat, readRDS(r))
-  else
-    dat <- readRDS(r)
-}
 
 modAns <- model.frame(
-  futurefgcDau ~ fgcstatusMom + group_fgcstatusMom
+  futurefgcDau ~ fgcstatus + group_fgc
+  + CC
   + bene + group_bene
   + media + group_media 
   + att + group_att 
   + edu + group_edu
   + wealth + group_wealth
   + age + maritalStat + job + urRural + religion
-  + clusterId + ethni + CC
-  , data=dat, na.action=na.exclude, drop.unused.levels=TRUE
+  + clusterId + ethni 
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
 )
 
 system.time(mod<- clmm(
-  futurefgcDau ~ fgcstatusMom + group_fgcstatusMom
+  futurefgcDau ~ fgcstatus + group_fgc
   + CC
   + bene + group_bene
   + media + group_media 

### 2018-09-06 daughterfgc_full_varlvlsum.R

@@ -2,7 +2,6 @@ library(ordinal)
 library(splines)
 library(RVAideMemoire)
 
-load(".all.daughterfgc_full_clmm.RData")
 
 varlvlsum <- Anova.clmm(mod)
 

### 2018-09-06 daughterfgc_ind_clmm.R

@@ -1,27 +1,21 @@
 library(ordinal)
 library(splines)
 
-for (r in grep("Rds$", input_files, value=TRUE)){
-  if (exists("dat"))
-    dat <- rbind(dat, readRDS(r))
-  else
-    dat <- readRDS(r)
-}
 
 modAns <- model.frame(
-  futurefgcDau ~ fgcstatusMom + bene + media + att + edu 
-  + age + wealth + maritalStat + job + urRural + religion
-  + clusterId + ethni + CC
-  , data=dat, na.action=na.exclude, drop.unused.levels=TRUE
+  futurefgcDau ~ fgcstatus + CC 
+  + bene + media + att + edu 
+  + age + wealth 
+  + maritalStat + job + urRural + religion
+  + clusterId + ethni
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
 )
 
-system.time(mod <- clmm(futurefgcDau ~ fgcstatusMom
+system.time(mod <- clmm(futurefgcDau ~ fgcstatus
   + CC
   + bene + media + att + edu
   + ns(age,4) + ns(wealth,3)
-  + maritalStat 
-  + job
-  + urRural + religion
+  + maritalStat + job + urRural + religion
   + (1|clusterId) + (1|ethni)
   , data=modAns)
 )

### 2018-09-06 daughterfgc_ind_varlvlsum.R

@@ -2,8 +2,6 @@ library(ordinal)
 library(splines)
 library(RVAideMemoire)
 
-load(".all.daughterfgc_ind_clmm.RData")
-
 varlvlsum <- Anova.clmm(mod)
 
 print(varlvlsum)

### 2018-09-06 futurefgcDau_full_clmm.R

@@ -1,29 +1,29 @@
+library(dplyr)
 library(ordinal)
 library(splines)
 
-for (r in grep("Rds$", input_files, value=TRUE)){
-  if (exists("dat"))
-    dat <- rbind(dat, readRDS(r))
-  else
-    dat <- readRDS(r)
-}
+combined_dat <- (combined_dat
+	%>% group_by(clusterId)
+	%>% mutate(group_futurefgc = mean(futurefgc01, na.rm=TRUE))
+)
 
 modAns <- model.frame(
-  futureDau ~ futurefgc + group_futurefgc
-  + fgcstatusMom + group_fgcstatusMom
+  futurefgcDau ~ futurefgc + group_futurefgc
+  + fgcstatus + group_fgc
+  + CC
   + bene + group_bene
   + media + group_media 
   + att + group_att 
   + edu + group_edu
   + wealth + group_wealth
   + age + maritalStat + job + urRural + religion
-  + clusterId + ethni + CC
-  , data=dat, na.action=na.exclude, drop.unused.levels=TRUE
+  + clusterId + ethni
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
 )
 
 system.time(mod<- clmm(
-  futureDau ~ futurefgc + group_futurefgc
-  + fgcstatusMom + group_fgcstatusMom
+  futurefgcDau ~ futurefgc + group_futurefgc
+  + fgcstatus + group_fgc
   + CC
   + bene + group_bene
   + media + group_media 

### 2018-09-06 futurefgcDau_full_varlvlsum.R

@@ -2,8 +2,6 @@ library(ordinal)
 library(splines)
 library(RVAideMemoire)
 
-load(".all.futurefgcDau_full_clmm.RData")
-
 varlvlsum <- Anova.clmm(mod)
 
 print(varlvlsum)

### 2018-09-06 futurefgcDau_ind_clmm.R

@@ -1,28 +1,22 @@
 library(ordinal)
 library(splines)
 
-for (r in grep("Rds$", input_files, value=TRUE)){
-  if (exists("dat"))
-    dat <- rbind(dat, readRDS(r))
-  else
-    dat <- readRDS(r)
-}
 
 modAns <- model.frame(
-  futureDau ~ futurefgc + fgcstatusMom + bene + media + att + edu 
-  + age + wealth + maritalStat + job + urRural + religion
-  + clusterId + ethni + CC
-  , data=dat, na.action=na.exclude, drop.unused.levels=TRUE
+  futurefgcDau ~ futurefgc + fgcstatus + CC
+  + bene + media + att + edu 
+  + age + wealth 
+  + maritalStat + job + urRural + religion
+  + clusterId + ethni
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
 )
 
 
-system.time(mod <- clmm(futureDau ~ futurefgc + fgcstatusMom
+system.time(mod <- clmm(futurefgcDau ~ futurefgc + fgcstatus
   + CC
   + bene + media + att + edu
   + ns(age,4) + ns(wealth,3)
-  + maritalStat 
-  + job
-  + urRural + religion
+  + maritalStat + job + urRural + religion
   + (1|clusterId) + (1|ethni)
   , data=modAns)
 )

### 2018-09-06 futurefgcDau_ind_varlvlsum.R

@@ -2,8 +2,6 @@ library(ordinal)
 library(splines)
 library(RVAideMemoire)
 
-load(".all.futurefgcDau_ind_clmm.RData")
-
 varlvlsum <- Anova.clmm(mod)
 
 print(varlvlsum)

### 2018-09-06 futurefgc_full_clmm.R

@@ -1,27 +1,22 @@
 library(ordinal)
 library(splines)
 
-for (r in grep("Rds$", input_files, value=TRUE)){
-  if (exists("dat"))
-    dat <- rbind(dat, readRDS(r))
-  else
-    dat <- readRDS(r)
-}
 
 modAns <- model.frame(
-  futurefgc ~ fgcstatusMom + group_fgcstatusMom
+  futurefgc ~ fgcstatus + group_fgc
+  + CC
   + bene + group_bene
   + media + group_media 
   + att + group_att 
   + edu + group_edu
   + wealth + group_wealth
   + age + maritalStat + job + urRural + religion
-  + clusterId + ethni + CC
-  , data=dat, na.action=na.exclude, drop.unused.levels=TRUE
+  + clusterId + ethni
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
 )
 
 system.time(mod <- clmm(
-  futurefgc ~ fgcstatusMom + group_fgcstatusMom
+  futurefgc ~ fgcstatus + group_fgc
   + CC
   + bene + group_bene
   + media + group_media 

### 2018-09-06 futurefgc_full_varlvlsum.R

@@ -2,7 +2,6 @@ library(ordinal)
 library(splines)
 library(RVAideMemoire)
 
-load(".all.futurefgc_full_clmm.RData")
 
 varlvlsum <- Anova.clmm(mod)
 

### 2018-09-06 futurefgc_ind_clmm.R

@@ -1,29 +1,23 @@
 library(ordinal)
 library(splines)
 
-for (r in grep("Rds$", input_files, value=TRUE)){
-  if (exists("dat"))
-    dat <- rbind(dat, readRDS(r))
-  else
-    dat <- readRDS(r)
-}
 
 modAns <- model.frame(
-  futurefgc ~ fgcstatusMom + bene + media + att + edu 
-  + age + wealth + maritalStat + job + urRural + religion
-  + clusterId + ethni + CC
-  , data=dat, na.action=na.exclude, drop.unused.levels=TRUE
+  futurefgc ~ fgcstatus + CC
+  + bene + media + att + edu 
+  + age + wealth 
+  + maritalStat + job + urRural + religion
+  + clusterId + ethni
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
 )
 
 
 
-system.time(mod <- clmm(futurefgc ~ fgcstatusMom
+system.time(mod <- clmm(futurefgc ~ fgcstatus
   + CC
   + bene + media + att + edu
   + ns(age,4) + ns(wealth,3)
-  + maritalStat 
-  + job
-  + urRural + religion
+  + maritalStat + job + urRural + religion
   + (1|clusterId) + (1|ethni)
   , data=modAns)
 )

### 2018-09-06 futurefgc_ind_varlvlsum.R

@@ -2,8 +2,6 @@ library(ordinal)
 library(splines)
 library(RVAideMemoire)
 
-load(".all.futurefgc_ind_clmm.RData")
-
 varlvlsum <- Anova.clmm(mod)
 
 print(varlvlsum)

### 2018-09-06 iso.R

@@ -9,7 +9,7 @@ attr(modAns,"terms") <- NULL
 
 catNames <- c("religion","urRural","job","maritalStat")
 predNames <- colnames(modAns)[2:(ncol(modAns)-3)]
-predNames <- c(predNames,"CC")
+predNames <- c(predNames)
 
 isoList <- lapply(predNames, function(n){
   ordpred(mod, n, modAns)
@@ -19,16 +19,16 @@ isoList <- lapply(predNames, function(n){
 print(
 grid.arrange(varPlot(isoList[[1]],P=varlvlsum$`Pr(>Chisq)`[1]),
              varPlot(isoList[[2]],P=varlvlsum$`Pr(>Chisq)`[2]),
-             varPlot(isoList[[3]],P=varlvlsum$`Pr(>Chisq)`[4]),
-             varPlot(isoList[[4]],P=varlvlsum$`Pr(>Chisq)`[5]),
-             varPlot(isoList[[5]],P=varlvlsum$`Pr(>Chisq)`[6]),
-             varPlot(isoList[[6]],P=varlvlsum$`Pr(>Chisq)`[7]),
-             varPlot(isoList[[7]],P=varlvlsum$`Pr(>Chisq)`[8]),
-             varPlot(isoList[[8]],P=varlvlsum$`Pr(>Chisq)`[9]),
-             varPlot(isoList[[9]],P=varlvlsum$`Pr(>Chisq)`[10]),
-             varPlot(isoList[[10]],P=varlvlsum$`Pr(>Chisq)`[11]),
-             varPlot(isoList[[11]],P=varlvlsum$`Pr(>Chisq)`[12]),
-             varPlot(isoList[[12]], P=varlvlsum$`Pr(>Chisq)`[[13]]),
+             varPlot(isoList[[3]],P=varlvlsum$`Pr(>Chisq)`[3]),
+             varPlot(isoList[[4]],P=varlvlsum$`Pr(>Chisq)`[4]),
+             varPlot(isoList[[5]],P=varlvlsum$`Pr(>Chisq)`[5]),
+             varPlot(isoList[[6]],P=varlvlsum$`Pr(>Chisq)`[6]),
+             varPlot(isoList[[7]],P=varlvlsum$`Pr(>Chisq)`[7]),
+             varPlot(isoList[[8]],P=varlvlsum$`Pr(>Chisq)`[8]),
[…]

### 2018-09-06 prevalence.R

@@ -1,86 +1,32 @@
 library(dplyr)
 library(ggplot2)
 
-for (r in grep("Rds$", input_files, value=TRUE)){
-  if (exists("dat"))
-    dat <- rbind(dat, readRDS(r))
-  else
-    dat <- readRDS(r)
+combined_dat <- data.frame()
+for(r in input_files){
+  combined_dat <- bind_rows(combined_dat, readRDS(r))
 }
 
-yesnodk <- function(x){
-  y <- as.numeric(factor(x,levels(x)[c(1,3,2)]))-1
-  return(y)
-}
-
-yesnodkFactor <- function(x){
-  y <- factor(x,levels(x)[c(1,3,2)])
-  return(y)
-}
-
-contfgc <- function(x){
-  y <- factor(x,levels(x)[c(2,3,1)])
-  return(y)
-}
-
-rightfactor <- function(x){
-  y <- as.numeric(x)-1
-  return(y)
-}
-
-scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
-	if(is.null(colnam)) colnam = type
-	if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
-	if(is.null(idvec)) idvec <- 1:nrow(dat)
-	typeNames <- grepl(type, names(Answers))
-	cols <- sum(typeNames)
-	tempdat <- (dat[typeNames] 
-	%>% rowwise()
-	%>% summarise_each(funs(funct)) 
-	%>% mutate(id=idvec) 
-	%>% transmute(total = rowMeans(.[,1:cols],na.rm=TRUE)
-		, id=id
-		)		 
-	%>% ungroup() 
-	%>% mutate(Score=total/mean(total,na.rm=TRUE)) 
-	%>% select(-total)
-		)
-	colnames(tempdat) <- c("id", colnam)
-	return(tempdat)
-}
-
-print(summary(dat))
-
-groupdat <- (dat
-	%>% select(fgc, daughterToFgc, clusterId, age, id, edu, wealth, ethni
-		, religion, maritalStat, job, urRural
-		, beneframe, attframe, mediaframe 
-	)
-	%>% mutate(fgcstatusMom = fgc
-		, fgc = rightfactor(fgc)
-		, edu = rightfactor(edu)
-		, edu = edu / mean(edu, na.rm = TRUE)
-		, daughterToFgc = yesnodk(daughterToFgc)
-		)
[…]

### 2018-09-06 recode.R

@@ -18,7 +18,7 @@ Answers <- (Answers
 
 # Ideally, I like to have a variable as daughterFGC (daughter's FGC status) which involves a few variables:  numDaughterFgced (already cut; 95 and 0=none cut), and daughterToFgc.  Those variables provides answers of yes (already cut), no (none cut), plan to cut, plan not to be cut, and don't know the plan yet.  I like to make it a single outcome measurement with 6 levels: yes/to be cut, yes/not to be cut, no/to be cut, no/not to be cut, yes/don't know, no/don't know.
 
-aa <- (Answers
+Answers <- (Answers
 	%>% mutate(daughterFgced = ifelse(numDaughterFgced == 95, "No", "Yes")
 		, daughterFgced = ifelse(numDaughterFgced == 0, "Yes", daughterFgced)
 		, daughterFgced = factor(daughterFgced)
@@ -27,15 +27,23 @@ aa <- (Answers
 		, daughterNotFgced = ifelse(daughterNotFgced == "Don't know", NA, as.character(daughterNotFgced))
 		, daughterNotFgced = factor(daughterNotFgced)
 		, CC = substring(survey, 1, 2)
-		, CC = factor(CC)
+		, CC = as.factor(CC)
 		, recode = substring(survey, 3, 3)
 		, recode = as.numeric(recode)
-		, region = factor(paste(CC, region, sep="_"))
-		, clusterId = factor(paste(survey, clusterId, sep="_"))
-	  , ethni = factor(paste(CC, ethni, sep="_"))
+		, region = as.factor(paste(CC, region, sep="_"))
+		, clusterId = as.factor(paste(survey, clusterId, sep="_"))
+	  , ethni = as.factor(paste(CC, ethni, sep="_"))
     , religion = tableRecode(religion, "religion", maxCat=4)
     , maritalStat = tableRecode(maritalStat, "partnership", maxCat=4)
     , wealth = wealth/100000
+		, fgcstatus = fgc
+		, fgc = rightfactor(fgc)
+		, edu = rightfactor(edu)
+		, edu = edu / mean(edu, na.rm = TRUE)
+		, futurefgc = contfgc(continueFgc)
+		, futurefgc01 = contfgc01(continueFgc)
+		, futurefgcDau = yesnodkFactor(daughterToFgc)
+		, futurefgcDau01 = yesnodk01(daughterToFgc) 
 		)
 )
 

### 2018-09-06 recodeFuns.R

@@ -67,7 +67,7 @@ scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
   if(is.null(colnam)) colnam = type
   if(!is.null(idvec))(dat <- dat %>% filter(id %in% idvec))
   if(is.null(idvec)) idvec <- 1:nrow(dat)
-  typeNames <- grepl(type, names(Answers))
+  typeNames <- grepl(type, names(dat))
   cols <- sum(typeNames)
   tempdat <- (dat[typeNames] 
               %>% rowwise()
@@ -77,7 +77,7 @@ scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
                             , id=id
               )
               %>% ungroup() 
-              %>% mutate(Score=total/mean(total,na.rm=TRUE)) 
+              %>% mutate(Score=total/max(total,na.rm=TRUE)) 
               %>% select(-total)
   )
   colnames(tempdat) <- c("id", colnam)
@@ -85,18 +85,27 @@ scoring <- function(dat, type,funct,idvec=NULL,colnam=NULL){
 }
 
 yesnodk <- function(x){
-  y <- as.numeric(factor(x,levels(x)[c(1,3,2)]))-1
+  y <- as.numeric(yesnodkFactor(x))-1
   return(y)
 }
 
+yesnodk01 <- function(x){
+  yesnodk(x)/max(yesnodk(x),na.rm=TRUE)
+}
+
 yesnodkFactor <- function(x){
-  y <- factor(x,levels(x)[c(1,3,2)])
+  y <- factor(x,levels = c("No", "Don't know", "Yes"))
   return(y)
 }
 
 contfgc <- function(x){
-  y <- factor(x,levels(x)[c(2,3,1)])
+  y <- factor(x,levels=c("Discontinued","Depends","Continued"))
   return(y)
+}
+
+contfgc01 <- function(x){
+  y = as.numeric(contfgc(x)) -1
+  return(y/max(y, na.rm=TRUE))
 }
 
 rightfactor <- function(x){

### 2018-09-07 iso.R
waiting for last model

@@ -8,12 +8,13 @@ attr(modAns,"terms") <- NULL
 
 
 catNames <- c("religion","urRural","job","maritalStat")
-predNames <- colnames(modAns)[2:(ncol(modAns)-3)]
-predNames <- c(predNames)
+predNames <- colnames(modAns)[2:(ncol(modAns)-2)]
 
 isoList <- lapply(predNames, function(n){
   ordpred(mod, n, modAns)
 })
+
+print(length(isoList))
 
 ## futurefgc_ind, daughterfgc_ind
 print(
@@ -28,7 +29,7 @@ grid.arrange(varPlot(isoList[[1]],P=varlvlsum$`Pr(>Chisq)`[1]),
              varPlot(isoList[[9]],P=varlvlsum$`Pr(>Chisq)`[9]),
              varPlot(isoList[[10]],P=varlvlsum$`Pr(>Chisq)`[10]),
              varPlot(isoList[[11]],P=varlvlsum$`Pr(>Chisq)`[11]),
-             # varPlot(isoList[[12]], P=varlvlsum$`Pr(>Chisq)`[[12]]),
+             varPlot(isoList[[12]], P=varlvlsum$`Pr(>Chisq)`[[12]]),
              nrow=4,ncol=3)
 )
 
@@ -44,12 +45,12 @@ if(nrow(varlvlsum)==13){
 ## futurefgc_full, daughterfgc_full
 if(nrow(varlvlsum)==18){
   print(
-    grid.arrange(varPlot(isoList[[13]],P=varlvlsum$`Pr(>Chisq)`[14]),
-                 varPlot(isoList[[14]],P=varlvlsum$`Pr(>Chisq)`[15]),
-                 varPlot(isoList[[15]],P=varlvlsum$`Pr(>Chisq)`[16]),
-                 varPlot(isoList[[16]],P=varlvlsum$`Pr(>Chisq)`[17]),
-                 varPlot(isoList[[17]],P=varlvlsum$`Pr(>Chisq)`[18]),
-                 varPlot(isoList[[18]],P=varlvlsum$`Pr(>Chisq)`[3]),
+    grid.arrange(varPlot(isoList[[13]],P=varlvlsum$`Pr(>Chisq)`[13]),
+                 varPlot(isoList[[14]],P=varlvlsum$`Pr(>Chisq)`[14]),
+                 varPlot(isoList[[15]],P=varlvlsum$`Pr(>Chisq)`[15]),
[…]

### 2018-09-07 ordfuns.R

@@ -53,6 +53,9 @@ varpred <- function(mod, varname, frame, isolate=FALSE, isoValue=NULL, level=0.0
   # print(pat); print(fnames)
   fCol <- grep(pat, fnames)
   
+  ## in case grepping response variable
+  fCol <- fCol[which(fCol != 1)] 
+  
   print(paste("Selected variable", fnames[fCol]))
   if(length(fCol)<1) {
     stop(paste("No matches to", varname, "in the frame", collapse=" "))

### 2018-09-07 manuscript.tex
Update manuscript.tex

@@
 \subsection{Research Questions}\label{research-questions}
-The main focus of this study is to analyze attitudes of FGC benefits (see the list of FGC benefits at table xx) and of FGC continuance in association with intention (planned behavior) to cut daughters.
-Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits and intention (planned behavior) of cutting daughters (structural models) in the hope of???
+The main focus of this study is to analyze associations of attitudes of FGC benefits (see the list of FGC benefits at table xx) and intention (planned behavior) to cut daughters.
+Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why)
 
@@
 
-The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm and update).
-The heory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
+The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (need more work).
+The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
 Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.
-In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, media use and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.
+In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.
+\cf{need comments!!!}
 
@@
 
-The main response variables were woman's attitude on whether they think FGC should be continued in the FGC future model and woman's intention of cutting their daughters in the daughter's FGC status model.
-The main predictors in both of the models were attitudes of FGC benefits and woman's FGC status.
+The main response variables were woman's intention of cutting their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model .
+The main predictors were attitudes of FGC benefits and woman's FGC status.
 We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.
@@
 
-In reference to the studies mentioned above, we also included the followings as covariates:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs.
+The sociodemographic variables included age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs.
 rural).
@@
 
- \_\_{[}CF:Do we spline wealth and group age? How do we estimate FGC belief, attitudes towards violence against women and media use?{]}
+In order to address the significance of community impact on the practice, FGC prevalence was calculated on a cluster level \CF{right?} and applied in the models as part of the (wording...).
+Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?).
+We also tested education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level, which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).
+
+ \_\_{[}CF:Do we splne wealth and group age? How do we estimate FGC belief, attitudes towards violence against women and media use?{]}
 
@@
 
-In order to address the significance of community impact on the practice of FGC, we tested education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level, which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).
-Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?)
-
-\_\_{[}CF: Did we calculate FGC prevalence by counting all the women in the DHS, or just those with daughters in the daughter model?{]}
 \_\_{[}CF:cluster is not a random effect in FGC, is it?{]}
-\_\_{[}CF:Shall we also test religion and ethnicity at a community level?{]}
 \_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.
@@
 
-\_\_{[}CF:reason why using PCA:  see \cite{Hayf05} p.. 129 for reference.{]}
 \_\_{[}CF:The concept of heterogeneity and threshold is important.  How to address these 2 concepts, if necessary.{]}
@@
 
+-----stop reading -----
 % "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
@@
 
+To study types of FGC for the future to understand correlation/assocaition between types of fgc and fgc beneifts.
+
 --- questions worth addressing

### 2018-09-07 community.R
Show Chyun a histogram

@@ -17,13 +17,15 @@ Answers <- (Answers
 	%>% left_join(., attframe)
 	%>% left_join(., mediaframe)
 	%>% group_by(clusterId)
-	%>% mutate(group_fgc = mean(fgc, na.rm = TRUE)
+	%>% mutate(
+		group_fgc = mean(fgc, na.rm = TRUE)
       , group_futurefgcDau = mean(futurefgcDau01, na.rm = TRUE)
-	    , group_bene = mean(bene, na.rm = TRUE)
-	    , group_att = mean(att, na.rm = TRUE)
-	    , group_media = mean(media, na.rm = TRUE)
-	    , group_edu = mean(edu, na.rm = TRUE)
-	    , group_wealth = mean(wealth, na.rm = TRUE)
+      , group_futurefgc = mean(futurefgc01, na.rm = TRUE)
+	   , group_bene = mean(bene, na.rm = TRUE)
+	   , group_att = mean(att, na.rm = TRUE)
+	   , group_media = mean(media, na.rm = TRUE)
+	   , group_edu = mean(edu, na.rm = TRUE)
+	   , group_wealth = mean(wealth, na.rm = TRUE)
 )
 )
 

### 2018-09-07 prevalence.R

@@ -19,10 +19,11 @@ groupdat <- (combined_dat
 
 
 print(summary(groupdat))
+
 print(hist(groupdat$group_fgc))
 print(hist(groupdat$group_futurefgcDau))
+print(hist(groupdat$group_futurefgc))
 
-## Craziness!
 print(hist(groupdat$group_bene))
 print(hist(groupdat$group_att))
 print(hist(groupdat$group_media))

### 2018-09-07 community.R
Meeting with Mike and Chyun

@@ -26,10 +26,14 @@ Answers <- (Answers
 	   , group_media = mean(media, na.rm = TRUE)
 	   , group_edu = mean(edu, na.rm = TRUE)
 	   , group_wealth = mean(wealth, na.rm = TRUE)
+	)
 )
-)
+
+print(hist(Answers$group_fgc))
+print(hist(Answers$group_futurefgc))
+print(hist(Answers$group_futurefgcDau))
 
 print(summary(Answers))
-
-# rdsave(Answers)
 saveRDS(Answers, rdsname)
+
+# rdnosave

### 2018-09-07 prevalence.R

@@ -21,8 +21,8 @@ groupdat <- (combined_dat
 print(summary(groupdat))
 
 print(hist(groupdat$group_fgc))
-print(hist(groupdat$group_futurefgcDau))
 print(hist(groupdat$group_futurefgc))
+print(hist(groupdat$group_futurefgcDau))
 
 print(hist(groupdat$group_bene))
 print(hist(groupdat$group_att))

### 2018-09-07 manuscript.tex
Update manuscript.tex

@@
 
+Baseline socio-demographic and sample characteristics are shown in xxx.
+
 Tables and figures including:
@@
 But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
+\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))
 
@@
 
+\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
+
 \subsection{Conclusion}\label{Conclusion}

### 2018-09-10 manuscript.tex
Update manuscript.tex

@@
 
-There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}.
+There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}.
 We used DHS data for this study because of certain questionnaires only available in DHS.
 Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-We did not analyze the newest dataset due to the lack of FGC benefits modules (checked in 09/17).
+We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 09/17).
 
@@
 
-The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (need more work).
+The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?).
 The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
 Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.
-In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.
+Here, we refer the attitudes to women's attitudes of FGC benefits (see the list of FGC benefits at table-- in Appendix); perceived behavioral control to perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and to their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory).
 \cf{need comments!!!}
 
-(see \cite{IloDarf18, PashPonn16} for measurements of the thoery of planned behaviors on fgc)
-
-(CF: Can domestic violence index (gender power) be a proxy to perceived controlled behavior for daugther's FGC future?)
-
-The main response variables were woman's intention of cutting their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model .
+The main response variables in this study were woman's intention to cut their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model.
 The main predictors were attitudes of FGC benefits and woman's FGC status.
-We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.
-It is noted that we chose woman's attitudes towards gender violence instead of personal violence experience from their spouse because the former better reflects gender awareness.
-We believed that FGC benefits coded and the information of such collected by DHS represented the values of the communities where FGC practiced.
+In order to test other theories mentioned above, we also included woman's gender awareness and other socio demogramic variables (see below).
 
@@
 rural).
-The followings were treated as random variables:  cluster ID (villages), countries and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).
-Further, media effect was also counted in the random effect (slope?) because we presumed that each country carried various media content from each other.
+The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).
+(We did not treat media effect  in the random effect (slope?) because we presumed that each country carried media content different from each other.
+Why not?)
 
-In order to address the significance of community impact on the practice, FGC prevalence was calculated on a cluster level \CF{right?} and applied in the models as part of the (wording...).
+In order to address the significance of community impact on the practice were education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level (on a cluster leve, not national, right?), which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).
 Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?).
-We also tested education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level, which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).
-
- \_\_{[}CF:Do we splne wealth and group age? How do we estimate FGC belief, attitudes towards violence against women and media use?{]}
-
-%“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. “ \cite{Hayf05}
 
@@
 CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
-Same reason as for clusterID{]}
+Same reason as for clusterID{]} %“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior.
+“ \cite{Hayf05}
 
@@
 -----stop reading -----
-% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
 
@@
 % women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
-
+% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
 --- community levels of impact and intervention

### 2018-09-12 manuscript.tex
Update manuscript.tex

@@
 The sociodemographic variables included age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs.
-rural).
+rural) in addition to country.
 The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).
-(We did not treat media effect  in the random effect (slope?) because we presumed that each country carried media content different from each other.
-Why not?)
 
-In order to address the significance of community impact on the practice were education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level (on a cluster leve, not national, right?), which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).
-Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?).
+In order to address the significance of community impact on the practice of fgc, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cf{on a cluster leve, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).
 
-\_\_{[}CF:cluster is not a random effect in FGC, is it?{]}
+\_\_{[}CF: Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?{]}
 \_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.
 CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
-Same reason as for clusterID{]} %“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior.
+But as J said, it is too hard!
+{]} %“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior.
 “ \cite{Hayf05}
-
-\_\_{[}CF:The concept of heterogeneity and threshold is important.  How to address these 2 concepts, if necessary.{]}
 \_\_{[}CF:Spatial Bayesian model \cite{KandNwak09} "Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
@@
 
------stop reading -----
-
 \subsubsection{Statistical Model}\label{statistical-model}
 
-\_\_{[}CF: J and M, please confirm this.{]}
+We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.
+The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
 
-We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to examine the models.
-The CLMM framework allows us to model a binary or ordinal response variable (e.g., daughter's FGC, while treating clusters and country as random effects.
-
-\_\_{[}CF: We have two main predictors:  mother's FGC status and FGC beliefs.
-Mother's FGC status is binary categorical variable, and FGC belief is continuous.
-The responses are daughter's FGC status and whether to continue FGC; both are categorical with 3 levels (yes, no, and dk/depends).{]}
+\_\_{[}CF:  Our response ARE categorical not binary; AND still need to explain why ethinicity is a random effect.
+AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.{]}
 
 \_\_{[}CF: reference: Methods and the first paragraph of Discussion\cite{Chia14}{]}
-\_\_{[}CF: spatial patterns?{]}
-
-\_\_{[}JD: What is the difference between clmm and clmm2?{]}
-
-This line of code essentially assumes that the response is ordinal.
-But I don't think it is...it actually seems pretty complex.
-So the best thing to do would probably be to figure out the total number of categories your response variable has and use MCMCglmm.
-Not sure specifically how the MCMCglmm approach would work, but this blog post might help: http://hlplab.wordpress.com/2009/05/07/multinomial-random-effects-models-in-r/
-
-More about response -- to clarify what model to use, it might help to ask yourself: what are the possible combinations of outcomes of the various response variables?
-i.e.
-collapse all of the response variables into one single categorical response with many categories.
-\_\_{[}CF: I like this idea and actually have been thinking about this possibility.{]}
-
-\_\_{[}jd: Probably we can start with binary responses, and with exploring patterns of type, before we worry to much about these details.{]}
 
 \subsubsection{Scripts}\label{scripts}
+
+Codes are be available upon request.
+
+-----stop reading -----
 

### 2018-09-13 manuscript.tex
Working on MS

@@
 \newcommand{\comment}[1]{\textbf{[[#1]]}}
+\newcommand{\jd}[1]{\comment{JD: #1}}
+\newcommand{\cf}[1]{\comment{CF: #1}}
 
@@
 
+\jd{I don't understand the North-South framing. Isn't MC not challenged everywhere? Shouldn't the framing be gender?}
+
 \subsubsection{Funding}\label{funding}
@@
 
-It was estimated that more than 200 million women, of which 44 millions were girls under age 15, have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (to update), and the actual numbers might in fact higher \cite{GaluKama15} (more?).
-The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update).
-FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).
+It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low.
+I would expect a majority under 15, no?} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (to update), and the actual numbers might in fact higher \cite{GaluKama15} (more?).
+The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update) \jd{This claim is surprising, and the sources are not academic.}.
+FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it \jd{What: implies a degree of self-awareness and} is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).
 
@@
 Interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites).
+\jd{I think we have two choices.
+Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}
 
-There are at least three main theoretical perspectives from outside the communities
-shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
-When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
-+ \cite{Shel-Wand11}:  Mackie's social convetional theory was supported in their findings; futher, they proposed that fgc practice is beyond the belief of marriage advanges; it goes beyond.
+\jd{It's convention theory. Don't say ``conventional'' theory, that just means the accepted theory in a time and place.}
+There are at least three main theoretical perspectives \jd{WHAT: from outside the communities}
+shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Convention theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
+When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
++ \cite{Shel-Wand11}:  Mackie's social convention theory was supported in their findings \jd{Whose findings?
+I've lost track of this s.}; futher, they proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
 FGC allows women to gain social capitals and access to networks.
-Their findings also suggested that the main deterent to marriges was not men's refusal of non-fgc women, but hostality and discrimination from fgc women to non fgc women.
+Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women \jd{It continues to be unclear who is saying what.
+And what you're implying about their evidence.}.
 
-The modernization theory proposes that traditional social relationships and values would be impacted by the development of modernization and replaced with modern life styles (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
-There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman’s empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.
-Although conventional theory was well studied and showed a larger effect on FGC practices than other theories of modernization and feminism (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), the aforementioned theories did not necessarily excluded each other, especially between modern theory and feminist theory \cite{Hayf05}.
+Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
+There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.
+Although convention theory was well studied and showed a larger effect on FGC practices than other theories of modernization and feminism (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), the aforementioned theories did not necessarily excluded each other, especially between modern theory and feminist theory \cite{Hayf05}.
+
+\jd{Can you figure out how to not use ``smart" quotes? They mess up the latex.}
 
@@
 This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test the three theories aforementioned.
+\jd{This P.
+seems insufficient to tie the theoretical explanation to our research questions.
+We should study Efferson's approach.}
 
@@
 Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why)
+\jd{I can work on the structural part, but we need a clear explanation of what we are trying to learn from the main question.}
+\jd{I guess this is also a good place to discuss our community variables?}
 
-\_\_{[}CF: read \cite{Aske05, Brue05}{]}
+\cf{read \cite{Aske05, Brue05}}
 
@@
 
-There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}.
-We used DHS data for this study because of certain questionnaires only available in DHS.
+There are two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}.
+We used DHS data for this study because of certain questionnaires \jd{``Certain questions'' sounds weaselly.
+Also, it's not clear we need to talk about MICS; using DHS seems very reasonable.} only available in DHS.
 Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
@@
 
-Only women with daughters to be considered for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
+Only women \jd{What does this mean: with daughters to be considered} for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
+\jd{We need to know how DHS decided who to ask the question.}
 
@@
 
-The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?).
+\jd{Is this s.
+about us or not?
+Why is it in our Methods?} The main constructs analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?).
 The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
-Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.
-Here, we refer the attitudes to women's attitudes of FGC benefits (see the list of FGC benefits at table-- in Appendix); perceived behavioral control to perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and to their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory).
-\cf{need comments!!!}
+Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to perform the behavior (or not); and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.
+Here, we refer the attitudes to women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control to perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and to their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory).
+\cf{need comments!!!} \jd{Not sure what you're trying to do here.
+What do you mean by ``refer''?
+Seems loose.}
 
@@
 
-\_\_{[}CF: Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?{]}
-\_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.
-CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
+\jd{How did the comments get so messed up? Can it not happen again?}
+\cf{Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?}
+\jd{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cf{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
 But as J said, it is too hard!
-{]} %“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior.
-“ \cite{Hayf05}
-\_\_{[}CF:Spatial Bayesian model \cite{KandNwak09} "Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
+} %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior.
+`` \cite{Hayf05}
+\cf{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
 Consequently, the spatial analysis will be affected by some random fluctuations.
@@
 However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p.
-788){]}
+788)}
 
@@
 
-\_\_{[}CF:  Our response ARE categorical not binary; AND still need to explain why ethinicity is a random effect.
-AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.{]}
+\cf{Our response ARE categorical not binary; AND still need to explain why ethinicity is a random effect.
+AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}
 
-\_\_{[}CF: reference: Methods and the first paragraph of Discussion\cite{Chia14}{]}
+\cf{reference: Methods and the first paragraph of Discussion\cite{Chia14}}
 
@@
 
-\_\_{[}CF: findings on convention theory vs. modernization theory vs. gender theory{]}
+\cf{findings on convention theory vs. modernization theory vs. gender theory}
 
@@
 % women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
-% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
+% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
 --- community levels of impact and intervention
@@
 \cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
-\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.
+\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.
 But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
@@
 1. comparison: \cite{Chia14, Hayf05}, and [http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]
----- Mali: "The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali.
+---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali.
 The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others.
@@
 
----- Nigeria: "Modernization (education and high socioeconomic status) had minimal impact on the likelihood of FGM, but education plays an important role in the mother's decision not to circumcise her daughter.
+---- Nigeria: ``Modernization (education and high socioeconomic status) had minimal impact on the likelihood of FGM, but education plays an important role in the mother's decision not to circumcise her daughter.
 It follows from these findings that community factors have a large effect on FGM, with individual factors having little effect on the distribution of FGM" \cite{KandNwak09}
@@
 \comment{cf: how to cite \cite{AkhmWord13,EffeVogt15} and compare these two?}
-% There are "discrepancies between attitudes and practices, especially significant under an analysis by sex as, despite manifesting less support, the percentage of female HCPs declaring to have performed medicalization is almost twice the males’ average.
-These findings suggest that female HCPs could be facing higher demand to medicalize the practice, and that, even when brought to the medical setting, FGM/C is regarded as a women’s issue to be performed by women to women." \cite{KaplSing16}
+% There are "discrepancies between attitudes and practices, especially significant under an analysis by sex as, despite manifesting less support, the percentage of female HCPs declaring to have performed medicalization is almost twice the males' average.
+These findings suggest that female HCPs could be facing higher demand to medicalize the practice, and that, even when brought to the medical setting, FGM/C is regarded as a women's issue to be performed by women to women." \cite{KaplSing16}
 
@@
 %Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics \cite{BrowBeec13}.
- \cite{Shel-Wand11}:  supporting Mackie's convetion theory "expections regarding fgc are interdependent...."
+ \cite{Shel-Wand11}:  supporting Mackie's convetion theory ``expections regarding fgc are interdependent...."
 
@@
 
-% “FGC facilitates the accumulation of social capital by younger women and of power and prestige by elder women.
+% ``FGC facilitates the accumulation of social capital by younger women and of power and prestige by elder women.
 Based on this new evidence and reinterpretation of social convention theory, we suggest that interventions aimed at eliminating FGC should target women's social networks, which are intergenerational, and include both men and women.
@@
 
-FGC is still in practice or a preference among women after migrated to a western environment from their original communities where FGC was a common practice, in the hope (wording?) of preserving their ethnic and gender identity despite its conflict against the  norms and laws of the newly settled society \cite{}; however, a baseline study in Sweden showed that a majority of female immigrants, including those newly arrived, opposed all forms of FGC with increased opposition over time after migration, and suggested that an attitude change had occurred \cite{WahlJohn17}; that suggested a likely influence of conventional theory.
+FGC is still in practice or a preference among women after migrated to a western environment from their original communities where FGC was a common practice, in the hope (wording?) of preserving their ethnic and gender identity despite its conflict against the  norms and laws of the newly settled society \cite{}; however, a baseline study in Sweden showed that a majority of female immigrants, including those newly arrived, opposed all forms of FGC with increased opposition over time after migration, and suggested that an attitude change had occurred \cite{WahlJohn17}; that suggested a likely influence of convention theory.
 
 (There are also studies proposing various factors impacting FGC practices, such as women's education \cite{KandNwak09,VanMeek15}, social economic status \cite{} etc, community levels of influences.) (What is conventional in convention theory can also be focal points to gender awareness and modern development.
-Question:  What is the differences between conventional theory and community level of impact on FGC?
+Question:  What is the differences between convention theory and community level of impact on FGC?
 the same or?)
@@
 As suggested, community-based education program has fallen shot tin changing FGC behaviours \cite{Shel08}}
-% ”I do not deny that individuals have evolved the capability to learn and apply social norms even to situations that are completely new, but there is much evidence that we are conditional followers of norms.
+% "I do not deny that individuals have evolved the capability to learn and apply social norms even to situations that are completely new, but there is much evidence that we are conditional followers of norms.
 In fact, as the experiments reported in Bicchieri and Xiao (2009) and Bicchieri and Chavez (2010) show, manipulating information produces major changes in behavior, and the existence of a social norm is no guarantee that it will be followed.
@@
 
-\_\_{[}CF: empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}{[}
+\cf{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
 
@@
 %"Our findings suggest that regional development influences attitudes and behavior, but national resistance to international norms can outweigh the influence of regional development." (p.23)
-%* "We hypothesized that those carriers of the scripts of the international system – education, mass media and working in the paid economy – would affect women’s attitudes and behavior with respect to FGC.
+%* "We hypothesized that those carriers of the scripts of the international system – education, mass media and working in the paid economy – would affect women's attitudes and behavior with respect to FGC.
 These hypotheses were confirmed" (p.
@@
 
-% "This study suggests that the adoption of a ‘modern’ lifestyle is not an inevitable result of acquiring the tools that give a person mastery over nature.
+% "This study suggests that the adoption of a `modern' lifestyle is not an inevitable result of acquiring the tools that give a person mastery over nature.
 Rather, the transmission of particular ideologies through global institutionalized arrangements appears to be the critical factor in abandoning practices like FGC." \cite{(BoylMcMo02}, p.
@@
 
-% \cite{BergDeni13}: application/public policy “A realist synthesis of controlled studies to determine the effectiveness of interventions to prevent genital cutting of girls.“
+% \cite{BergDeni13}: application/public policy ``A realist synthesis of controlled studies to determine the effectiveness of interventions to prevent genital cutting of girls.``
 
@@
 % gender autonomy \cite{Meye00}: 
-%“Since autonomy-augmenting educational programs are typically developed by cultural initiates who rely on traditional modes of expression and appeal to traditional values, it is reasonable to surmise that autonomy is best extended by avoiding cultural alienation and by building on women’s existing autonomy skills."
-% “autonomy-augmenting programs regard women in cultures that practice female genital cutting as self-determining individuals.
+%``Since autonomy-augmenting educational programs are typically developed by cultural initiates who rely on traditional modes of expression and appeal to traditional values, it is reasonable to surmise that autonomy is best extended by avoiding cultural alienation and by building on women's existing autonomy skills."
+% ``autonomy-augmenting programs regard women in cultures that practice female genital cutting as self-determining individuals.
 …they have some understanding of what matters to them and how best to proceed in light of their values and commitments before they participate in such programs.
@@
 But this understanding of autonomy entails neither endorsement of female genital cutting nor resignation to its persistence.
-Since cultures that practice female genital cutting may have selectively nurtured and stifled women’s autonomy skills, and since these cultures may shield the issue of female genital cutting from exercise of autonomy skills, developing and coordinating women’s autonomy skills and extending the range of application of these skills are key to augmenting their autonomy.
-“
-% convention or modernization theory?“ campaigns against FGC using educational, health, legal, and human rights–based approaches are at times ineffective and counterproductive when they frame the practice as a “tradition” rooted in a “primitive” and unchanging culture.
-We suggest that development interventions that do not address local contexts of FGC, including the complex politics and history of interventions designed to eradicate it, can in fact reify and reinscribe the practice as central to Maasai cultural identity.” \cite{WintKoom09}
+Since cultures that practice female genital cutting may have selectively nurtured and stifled women's autonomy skills, and since these cultures may shield the issue of female genital cutting from exercise of autonomy skills, developing and coordinating women's autonomy skills and extending the range of application of these skills are key to augmenting their autonomy.
+``
+% convention or modernization theory?`` campaigns against FGC using educational, health, legal, and human rights–based approaches are at times ineffective and counterproductive when they frame the practice as a ``tradition" rooted in a ``primitive" and unchanging culture.
+We suggest that development interventions that do not address local contexts of FGC, including the complex politics and history of interventions designed to eradicate it, can in fact reify and reinscribe the practice as central to Maasai cultural identity." \cite{WintKoom09}
 
-% \cite{Koom14}: “ practices of female excision are so diverse that they may defy generalizable remedies”  “Rather than relying on common campaign models, transferable advocacy tools, or ‘best practices,’ scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics.”
+% \cite{Koom14}: `` practices of female excision are so diverse that they may defy generalizable remedies"  ``Rather than relying on common campaign models, transferable advocacy tools, or `best practices,' scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics."
 
@@
 % norm/attitude vs.
-behaviour:  attitudes towards fgc did not have a positive correlation with their behaviour:  “within each country women from more developed regions, women who worked outside the home, and educated women were less likely to favor genital cutting and less likely to have their daughters cut.
+behaviour:  attitudes towards fgc did not have a positive correlation with their behaviour:  ``within each country women from more developed regions, women who worked outside the home, and educated women were less likely to favor genital cutting and less likely to have their daughters cut.
 Living in an urban area decreased the likelihood of favoring genital cutting, but it had no effect on behavior.
-“ \cite{BoylMcMo02}
+`` \cite{BoylMcMo02}
 
-%\cf{Bicchieri’s norm theory—
+%\cf{Bicchieri's norm theory—
 behaviour:  What the responder do 
@@
 \cite{Bicc06}
-First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \_\_{[}CF:i.e., normative norm?{]}
+First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \cf{normative norm?}
 and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.
@@
 
-% “ the effectiveness of interventions was hampered by a general lack of information.
-However, through the realist synthesis we identified that all of the interventions were based on a theory that dissemination of information improves cognitions about FGM/C, but the interventions’ success was contingent upon a range of contextual factors.
-“ \cite{BergDeni12a}
+% `` the effectiveness of interventions was hampered by a general lack of information.
+However, through the realist synthesis we identified that all of the interventions were based on a theory that dissemination of information improves cognitions about FGM/C, but the interventions' success was contingent upon a range of contextual factors.
+`` \cite{BergDeni12a}
 
@@
 % Based on our findings, are there any survey questions DHS should have included but did not?  Did our findings see something like group/community identity, womanhood \cite{Koom14}?
-% \cite{Koom14}: “ an Aang Serian activist who had addressed a village meeting saying, ‘The world is changing and the Maasai must change with it or risk dying out.’ They argued that these appeals to cultural survival were much more persuasive and meaningful to them than the ‘foreign’ language of rights.”
+% \cite{Koom14}: `` an Aang Serian activist who had addressed a village meeting saying, `The world is changing and the Maasai must change with it or risk dying out.' They argued that these appeals to cultural survival were much more persuasive and meaningful to them than the `foreign' language of rights."
 
@@
 
-% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cf{I don’t know if I want to cite \cite{EffeVogt15}.
-It doesn’t cite some very important papers which had addressed the concerns/questions the paper suggested}).
+% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cf{I don't know if I want to cite \cite{EffeVogt15}.
+It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).
 
-% \cf{TOSTAN uses a strategy based on conventional theory’s critical mass to eradicate FGC (see (Wils13}}
+% \cf{TOSTAN uses a strategy based on convention theory's critical mass to eradicate FGC (see (Wils13}}
  * Festinger (1950?):  Social pressure in informal groups
@@
 % suggestions: https://www.theguardian.com/global-development/2018/feb/06/battling-fgm-uganda-kenya-zero-tolerance-female-genital-mutilation "Thomas Lotongar, assistant chief in Konya Division in Kenya, says more rescue centres are needed, and schools must act as sanctuaries for girls to avoid FGM.
-“We need to find more alternatives and livelihood projects like tailoring[or] salon work to empower our girls who run away from the practice to the rescue centres.”"
+``We need to find more alternatives and livelihood projects like tailoring[or] salon work to empower our girls who run away from the practice to the rescue centres.""
 
@@
 Given the regional FGC prevalence, variations among countries and the social context of FGC practices (e.g., see Burkina Faso \cite{KarmKand11} vs.
-Nigeria \cite{KandNwak09}), a “one size fits all” strategy for the abandonment of FGMC would not be effective \cite{JohaDiop13, YodeWang13}.
+Nigeria \cite{KandNwak09}), a ``one size fits all" strategy for the abandonment of FGMC would not be effective \cite{JohaDiop13, YodeWang13}.
 

### 2018-09-13 manuscript.tex
Update manuscript.tex

@@
 
-\jd{It's convention theory. Don't say ``conventional'' theory, that just means the accepted theory in a time and place.}
 There are at least three main theoretical perspectives \jd{WHAT: from outside the communities}
@@
 When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
-+ \cite{Shel-Wand11}:  Mackie's social convention theory was supported in their findings \jd{Whose findings?
+
+\cf{\cite{Shel-Wand11}:  Mackie's social convention theory was supported in their findings \jd{Whose findings?
 I've lost track of this s.}; futher, they proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
 FGC allows women to gain social capitals and access to networks.
-Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women \jd{It continues to be unclear who is saying what.
-And what you're implying about their evidence.}.
+Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
 
@@
 Although convention theory was well studied and showed a larger effect on FGC practices than other theories of modernization and feminism (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), the aforementioned theories did not necessarily excluded each other, especially between modern theory and feminist theory \cite{Hayf05}.
-
-\jd{Can you figure out how to not use ``smart" quotes? They mess up the latex.}
 

### 2018-09-13 manuscript.tex
Update manuscript.tex

@@
 \subsubsection{Conclusions}\label{conclusions}
-Under the background that MC is not challenged in the West (e.g., against Jewish community), how  shall we frame FGC to be process by both communities from inside and outside?
-
-\jd{I don't understand the North-South framing. Isn't MC not challenged everywhere? Shouldn't the framing be gender?}
 
@@
 It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low.
-I would expect a majority under 15, no?} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (to update), and the actual numbers might in fact higher \cite{GaluKama15} (more?).
-The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update) \jd{This claim is surprising, and the sources are not academic.}.
+I would expect a majority under 15, no?}\cf{Most of the surveys sampled women of 15-49, girls under 15  were reported by their mothers.
+The ration of girls under 15 is minority} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (updated Sep 18).
+The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jd{This claim is surprising, and the sources are not academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}.
 FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it \jd{What: implies a degree of self-awareness and} is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).
@@
 \jd{I think we have two choices.
-Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}
+Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}\cf{The main purpose of this study is not to discuss types or take a position.
+This paragraph is to briefly present fgc in context.}
 
-There are at least three main theoretical perspectives \jd{WHAT: from outside the communities}
-shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Convention theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
+There are at least three main theoretical perspectives from outside the FGC communities
+shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
 When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
-
-\cf{\cite{Shel-Wand11}:  Mackie's social convention theory was supported in their findings \jd{Whose findings?
-I've lost track of this s.}; futher, they proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
-FGC allows women to gain social capitals and access to networks.
-Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
 
@@
 There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.
-Although convention theory was well studied and showed a larger effect on FGC practices than other theories of modernization and feminism (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), the aforementioned theories did not necessarily excluded each other, especially between modern theory and feminist theory \cite{Hayf05}.
+Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.
 
@@
 \jd{We need to know how DHS decided who to ask the question.}
+\cf{Explain how we choose women}
 
@@
 % ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
+\cf{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{Shel-Wand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
+FGC allows women to gain social capitals and access to networks.
+Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
 --- community levels of impact and intervention

### 2018-09-14 manuscript.tex
Update manuscript.tex

@@
 Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.
-This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test the three theories aforementioned.
+This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards.
 \jd{This P.
 seems insufficient to tie the theoretical explanation to our research questions.
-We should study Efferson's approach.}
+We should study Efferson's approach.} \cf{good point.
+reframed and may still need more thoughts.}
 
@@
 
-There are two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}.
-We used DHS data for this study because of certain questionnaires \jd{``Certain questions'' sounds weaselly.
-Also, it's not clear we need to talk about MICS; using DHS seems very reasonable.} only available in DHS.
+We analyzed the Demographic and Health Surveys (DHS) by USAID.
 Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
@@
 
-Only women \jd{What does this mean: with daughters to be considered} for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
+Only women with daughters to be considered for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
 \jd{We need to know how DHS decided who to ask the question.}
@@
 The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
-Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to perform the behavior (or not); and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.
-Here, we refer the attitudes to women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control to perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and to their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory).
+Here, the attitudes is constructed as women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control as perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory).
 \cf{need comments!!!} \jd{Not sure what you're trying to do here.
@@
 788)}
+
+\cf{Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to perform the behavior (or not); and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.}
 

### 2018-09-14 manuscript.tex
Update manuscript.tex

@@
 We should study Efferson's approach.} \cf{good point.
-reframed and may still need more thoughts.}
+reframed and may still need more works.}
 
 \subsection{Research Questions}\label{research-questions}
-The main focus of this study is to analyze associations of attitudes of FGC benefits (see the list of FGC benefits at table xx) and intention (planned behavior) to cut daughters.
+The main focus of this study is to analyze associations of attitudes towards FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms associating behavioral intenation can be detected at both a population and a community level.
+If so, if social norms the most soundly
+
 Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why)
-\jd{I can work on the structural part, but we need a clear explanation of what we are trying to learn from the main question.}
+\jd{I can work on the structural part, but we need a clear explanation of what we are trying to learn from the main question.} \cf{reframed the main question.}
 \jd{I guess this is also a good place to discuss our community variables?}

### 2019-01-14 manuscript.tex
Update manuscript.tex

@@
 Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 09/17).
+We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 1/09/19).
 
@@
 \subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
-
+\cite{Rima08}*
 \jd{Is this s.
@@
 % religion:  \cite{KarmKand11}
+
+\cfcmt{feminism or women’s rights perspective:  which women?  Who are the women?  Women from the West or women from inside the fgc communities?}
 

### 2019-01-24 manuscript.tex
Update manuscript.tex

@@
 \newcommand{\comment}[1]{\textbf{[[#1]]}}
-\newcommand{\jd}[1]{\comment{JD: #1}}
-\newcommand{\cf}[1]{\comment{CF: #1}}
+\newcommand{\cfcmt}[1]{\comment{CFS: #1}}
+\newcommand{\cf}[1]{\comment{CFS only: #1}}
+\newcommand{\jdcmt}[1]{\comment{JD: #1}}
+\newcommand{\jdmlcmt}[1]{\comment{JDML: #1}}
+\newcommand{\mlcmt}[1]{\comment{MLi: #1}}
 
@@
 
-It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low.
-I would expect a majority under 15, no?}\cf{Most of the surveys sampled women of 15-49, girls under 15  were reported by their mothers.
+It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low. I would
+expect a majority under 15, no?}\cf{Most of the surveys sampled women of 15-49, girls under 15 were reported by their mothers.
 The ration of girls under 15 is minority} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (updated Sep 18).
-The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jd{This claim is surprising, and the sources are not academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}.
-FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it \jd{What: implies a degree of self-awareness and} is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).
+The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
+http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jd{This claim is surprising, and the sources are not
+academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}.
+Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.
+FGC is also known as female genital mutilation and female circumcision;
+we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
+Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).
 
-The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the progress is hindered due to the complicated history of the very practice.
-The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, SchuLien13, WHO12} (more cites).
-Interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites).
+The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the
+progress is hindered due to the complicated history of the very practice.
+The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, KhosBane17, SchuLien13, WHO12}.
+Interventions based on associating FGC with violations
+of human rights and health dangers also encountered challenges \cite{Obio97, MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, GaluKama15, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites).
 \jd{I think we have two choices.
@@
 
-There are at least three main theoretical perspectives from outside the FGC communities
-shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
-When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
+\cfcmt{Culture and tradtions are guarded as main reason for FGC practice \cite{PariSaru18}, more cites}There are at least three main theoretical perspectives from outside the FGC communities shedding lights on the complexities of FGC \cite{Hayf05, Youn02}: social
+convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09,
+DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm,
+and update), and feminist theory/human rights perspective
+\cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08,
+Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy
+\cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri
+Spivak) (confirm and update.) Convention theory posits FGC an
+important norm to control marriage fidelity and social prestige; this
+perspective views FGC as a social behaviour resulting from group
+practice, and it takes a ``critical mass" to initiate a change
+\cite{Mack00, MackLeJe09}. When norms within the communities are
+strong, individuals tend to self-enforce community norms
+\cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09,
+ThomMadd92}; hence, intervention of FGC should target women's social
+networks, which are intergenerational, interdependent and
+interconnected across generations and genders \cite{Mack00,
+DuncWand11}.
 
-Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
-There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.
-Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.
+Modernization
+theory proposes that traditional social relationships and values
+would be eroded by modernization (e.g., with the improvement of
+wealth and education and emphasis of individual rights)
+(see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?). There is a wide
+range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95})
+and woman's empowerment on making FGC decision are shared concerns:
+for example, from social position \cite{VanMeek15}, autonomy
+\cite{Meye00}, gender equality and human rights \cite{Drol11}, to
+gender identity \cite{Youn04, Koom14, WintKoom09}. Although
+convention theory was well studied and showed a larger effect on FGC
+practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10,
+FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06,
+ReigGonz14, YirgKass12}), these theories did not necessarily excluded
+each other, especially between modernization theory and feminist
+theory \cite{Hayf05}.
 
-Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.
-Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.
-This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards.
-\jd{This P.
-seems insufficient to tie the theoretical explanation to our research questions.
-We should study Efferson's approach.} \cf{good point.
+Multiple
+theoretical frameworks would have to be incorporated to grasp a full
+explanation of the persistence and decline of FGC due to the
+heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.
+Identifying benefits of FGC practice is crucial to promote
+sustainable change \cite{EffeVogt15}, and a community-based FGC
+perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,
+KandNwak09, OdukAfol17} (to confirm) should also be recognized. This
+study takes both the dynamics of attitudes and intention of FGC
+practices (beliefs of FGC benefits, and intention of cutting) into
+account at both a population and a community level to test whether
+FGC is a result of social interactions of social agents through
+interpreting norms in expectance of rewards. \jd{This P. seems
+insufficient to tie the theoretical explanation to our research
+questions. We should study Efferson's approach.} \cf{good point.
 reframed and may still need more works.}
@@
 
+pricking \cite{WahlJohn17a, WahlJohn17b}
+
 \subsection{Conclusion}\label{Conclusion}

### 2019-01-25 manuscript.tex
Update manuscript.tex

@@
 The ration of girls under 15 is minority} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (updated Sep 18).
+United Nation has declared zero tolerance for FGC as it violates human rights and promoted the abundance of the practice  \cite{}.
 The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
@@
 The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the
-progress is hindered due to the complicated history of the very practice.
-The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, KhosBane17, SchuLien13, WHO12}.
-Interventions based on associating FGC with violations
-of human rights and health dangers also encountered challenges \cite{Obio97, MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, GaluKama15, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites).
+progress is hindered due to the complicated history of the very practice \cite{cite}.
+The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+In addition, interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{Obio97, MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, GaluKama15, JohnEsse10, WahlEsse18}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites).
 \jd{I think we have two choices.
@@
 
-\cfcmt{Culture and tradtions are guarded as main reason for FGC practice \cite{PariSaru18}, more cites}There are at least three main theoretical perspectives from outside the FGC communities shedding lights on the complexities of FGC \cite{Hayf05, Youn02}: social
-convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09,
-DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm,
-and update), and feminist theory/human rights perspective
-\cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08,
-Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy
-\cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri
-Spivak) (confirm and update.) Convention theory posits FGC an
-important norm to control marriage fidelity and social prestige; this
-perspective views FGC as a social behaviour resulting from group
-practice, and it takes a ``critical mass" to initiate a change
-\cite{Mack00, MackLeJe09}. When norms within the communities are
-strong, individuals tend to self-enforce community norms
-\cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09,
-ThomMadd92}; hence, intervention of FGC should target women's social
-networks, which are intergenerational, interdependent and
-interconnected across generations and genders \cite{Mack00,
-DuncWand11}.
+\cfcmt{Culture and tradtions are guarded as main reason for FGC practice \cite{PariSaru18}, more cites}There are at least three main theoretical perspectives from outside the FGC communities shedding lights on the complexities of FGC \cite{Hayf05, Youn02}: social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.) Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
+When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
 
@@
 
-pricking \cite{WahlJohn17a, WahlJohn17b}
+Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShell18} vs. no-tolerance, fgc vs. mc \cite{WahlEsse18}?
 

### 2019-01-29 manuscript.tex
Update manuscript.tex

@@
 The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.
-In addition, interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{Obio97, MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, GaluKama15, JohnEsse10, WahlEsse18}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites).
-\jd{I think we have two choices.
-Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}\cf{The main purpose of this study is not to discuss types or take a position.
-This paragraph is to briefly present fgc in context.}
 
-\cfcmt{Culture and tradtions are guarded as main reason for FGC practice \cite{PariSaru18}, more cites}There are at least three main theoretical perspectives from outside the FGC communities shedding lights on the complexities of FGC \cite{Hayf05, Youn02}: social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.) Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
+Social norm is \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} a fundamental approach in understanding FGC practice while human rights and feminist theory entails \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of intervening and abolishing	the practices.
+Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
 When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
 
-Modernization
-theory proposes that traditional social relationships and values
-would be eroded by modernization (e.g., with the improvement of
-wealth and education and emphasis of individual rights)
-(see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?). There is a wide
-range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95})
-and woman's empowerment on making FGC decision are shared concerns:
-for example, from social position \cite{VanMeek15}, autonomy
-\cite{Meye00}, gender equality and human rights \cite{Drol11}, to
-gender identity \cite{Youn04, Koom14, WintKoom09}. Although
-convention theory was well studied and showed a larger effect on FGC
-practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10,
-FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06,
-ReigGonz14, YirgKass12}), these theories did not necessarily excluded
-each other, especially between modernization theory and feminist
-theory \cite{Hayf05}.
+There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.
+Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.
 
-Multiple
-theoretical frameworks would have to be incorporated to grasp a full
-explanation of the persistence and decline of FGC due to the
-heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.
+Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.
 Identifying benefits of FGC practice is crucial to promote
-sustainable change \cite{EffeVogt15}, and a community-based FGC
-perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,
-KandNwak09, OdukAfol17} (to confirm) should also be recognized. This
-study takes both the dynamics of attitudes and intention of FGC
-practices (beliefs of FGC benefits, and intention of cutting) into
-account at both a population and a community level to test whether
-FGC is a result of social interactions of social agents through
-interpreting norms in expectance of rewards. \jd{This P. seems
-insufficient to tie the theoretical explanation to our research
-questions. We should study Efferson's approach.} \cf{good point.
+sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,
+KandNwak09, OdukAfol17} (to confirm) should also be recognized. This study takes both the dynamics of attitudes and intention of FGC
+practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether
+FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems
+insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.} \cf{good point.
 reframed and may still need more works.}
 
+Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
+
 \subsection{Research Questions}\label{research-questions}
-The main focus of this study is to analyze associations of attitudes towards FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms associating behavioral intenation can be detected at both a population and a community level.
-If so, if social norms the most soundly
 
-Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why)
-\jd{I can work on the structural part, but we need a clear explanation of what we are trying to learn from the main question.} \cf{reframed the main question.}
+The main model is the “daughter” model, which analyzed associations of attitude (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms associating behavioral intention can be detected.
+Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s attitudes of FGC benefits and FGC continuance; and “future_daughter” model to examine the association of attitudes of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positionss change the main model.
+
 \jd{I guess this is also a good place to discuss our community variables?}
@@
 % figure of FGC prevalence by age and country (see Hayf05)
-% refer to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/figure/F1/  \cite{SipsChen12} for a figure on intention of cutting daughter, mom's fgc status and their thoughts on fgc continuity.
+% refer to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/figure/F1/  \cite{SipsChen12} for a figure on intention of cutting daughter, mom's fgc status and their thoughts on fgc continuance.
 
@@
 \cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
-\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.
+\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination,” for marital market.
+The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.
 But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
@@
 
+“we find that some older women express an openness to reassessing norms and practices as they seek solutions to maintaining the physical well-being, moral integrity and cultural identity of girls in their families.
+Moreover, given the authority of older women over younger women, they also have power to negotiate change.\cite{ShelMore18}
 % get info on legal situation of FGC in those countries
@@
 %Except for Mali, all the studied nations have enacted decrees or legislation related to FGC \cite{WHO13}
+
+systematic review of effectiveness of fgc factors associating the practice \cite{WaigDoos18}
 

### 2019-02-01 manuscript.tex
Update manuscript.tex

@@
 Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
-When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
+FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.
+When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC targeting women's social networks, which are intergenerational, interdependent and interconnected across generations and genders was proposed \cite{Mack00, DuncWand11, ShelWand11}.
 
@@
 % ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
-\cf{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{Shel-Wand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
+\cf{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
 FGC allows women to gain social capitals and access to networks.

### 2019-02-01 manuscript.tex
Update manuscript.tex

@@
 There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.
-Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.
+Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),
 
@@
 sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,
-KandNwak09, OdukAfol17} (to confirm) should also be recognized. This study takes both the dynamics of attitudes and intention of FGC
-practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether
+KandNwak09, OdukAfol17} (to confirm) should also be recognized.
+Both convention theory and gender_human rights approaches centre on values of emphasize values of how FGC associates with identity.
+This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether
 FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems
@@
 
+\cf{to add modernization measurement}
 The main response variables in this study were woman's intention to cut their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model.

### 2019-02-25 manuscript.tex
Update manuscript.tex

--- 2019-02-01 manuscript.tex
@@
 There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.
-Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.
-
+Both convention theory and gender approaches centre on values of how FGC associates with identity \cte{cites}.
+Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), gender perspective can shed lights on how women’s gender values intertwine with convention theory of FGC values \cite{cites}.
 Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.
-Identifying benefits of FGC practice is crucial to promote
-sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,
-KandNwak09, OdukAfol17} (to confirm) should also be recognized. This study takes both the dynamics of attitudes and intention of FGC
-practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether
-FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems
-insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.} \cf{good point.
-reframed and may still need more works.}
-
-Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
 
@@
 
-The main model is the “daughter” model, which analyzed associations of attitude (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms associating behavioral intention can be detected.
-Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s attitudes of FGC benefits and FGC continuance; and “future_daughter” model to examine the association of attitudes of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positionss change the main model.
-
-\jd{I guess this is also a good place to discuss our community variables?}
-
-\cf{read \cite{Aske05, Brue05}}
+Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.
+This study takes both the dynamics of beliefs of FGC benefits and of intention of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).
+We developed three models in this study.
+The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
+Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s beliefs of FGC benefits and FGC continuance; and “future_daughter” model to examine the association of beliefs of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positions change the main model.
 
@@
 
-Only women with daughters to be considered for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
-\jd{We need to know how DHS decided who to ask the question.}
-\cf{Explain how we choose women}
+Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
+\cf{FGC module at https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}
 
 \subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
-\cite{Rima08}*
-\jd{Is this s.
-about us or not?
-Why is it in our Methods?} The main constructs analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?).
-The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.
-Here, the attitudes is constructed as women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control as perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory).
-\cf{need comments!!!} \jd{Not sure what you're trying to do here.
-What do you mean by ``refer''?
-Seems loose.}
+\cf{\cite{Rima08}}*
 
-The main response variables in this study were woman's intention to cut their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model.
-The main predictors were attitudes of FGC benefits and woman's FGC status.
-In order to test other theories mentioned above, we also included woman's gender awareness and other socio demogramic variables (see below).
-
-The sociodemographic variables included age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs.
+The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.
+The main predictors were beliefs of FGC benefits, woman's FGC status and attitudes of gender equality.
+Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs.
 rural) in addition to country.
@@
 
-In order to address the significance of community impact on the practice of fgc, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cf{on a cluster leve, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).
+In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cf{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
+Cluster  was used to represent a community level of impact \cite{AligRen06, Hayf05}
 
-\jd{How did the comments get so messed up? Can it not happen again?}
-\cf{Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?}
-\jd{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cf{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
+\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
 But as J said, it is too hard!
@@
 788)}
-
-\cf{Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to perform the behavior (or not); and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.}
+\cfcmt{Regarding FGC benefits modules, there were 9 questions.
+Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).
+Should we drop STD since 3 out of 4 missed this variable?}
 
@@
 
-\cf{Our response ARE categorical not binary; AND still need to explain why ethinicity is a random effect.
+\cfcmt{Our response ARE categorical not binary; AND still need to explain why ethnicity is a random effect.
 AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}
@@
 
------stop reading -----
-
 \subsection{Results}\label{results-1}
 
-Baseline socio-demographic and sample characteristics are shown in xxx.
+Baseline socio-demographic and sample characteristics are shown in xxx.  The prevalence of FGC are \%, \%, \% and \% in Kenya, Mali, Nigeria and Sierra Leon accordingly.
 
-Tables and figures including:
-table of basic sociodemographic results
-figure:  proportion of FGC daughters and FGC future
+Tables and figures to be included:
+- table of basic sociodemographic results
+- 3 figures of the results of the 3 models
+- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/, Fig 1)
 % figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
 % figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
-% figure of significant variables on modernization and pile the findings of the 4 nations into one figure.
-% a chart like figure 8-8D \cite{UNCI13}
-% figure of FGC prevalence by age and country (see Hayf05)
-% refer to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/figure/F1/  \cite{SipsChen12} for a figure on intention of cutting daughter, mom's fgc status and their thoughts on fgc continuance.
-
-Kenya 21% vs. 3% (2004-15 aged 15-49 women vs. 2010-15 aged 0-14 girls)
-Mali 89% vs. ?
-Nigeria 25% vs. 17%
-Sierra Leone 90% vs. 13%
-(We want DHS fgc rate and the rate from our samples)
-
-\cf{findings on convention theory vs. modernization theory vs. gender theory}
-
-\subsubsection{Basic Sociodemographic background}\label{Basic-Sociodemographic-background}
-% adding how many ethnic groups in each nation based on DHS data.
-
-\subsubsection{The FGC Future}\label{The-FGC-Future}
-
-\subsubsection{Daughters' FGC Status}\label{Daughters'-FGC-Status}
-
-\subsubsection{full model}\label{full-model}
-
-% Kenya and Nigeria both were under %30 vs. Mali and Sierra Leon over %80.  Are they different in terms of norm and beahvior?  To discuss this in the discussion.
-
-In the results of association of cutting daughter and mother's fgc status, the individual model and the community model were consistent; the effect of fgc prevalence among mothers, attitudes of fgc benefits and education were clear at the community level but not wealth, gender awareness and media consumption were not clear at the community level (meaning media use, gender awareness and education were less homogeneous?)
-
-In the results of association of fgc future and mother's fgc status,
+% a chart like figure 8-8D \cite{UNIC13}
 
@@
 
+% “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})
 --- by nations
@@
 
+% Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
+
 % `` the effectiveness of interventions was hampered by a general lack of information.

### 2019-02-26 manuscript.tex
Update manuscript.tex

@@
 The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.
-The main predictors were beliefs of FGC benefits, woman's FGC status and attitudes of gender equality.
+The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.
 Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs.
@@
 
-Baseline socio-demographic and sample characteristics are shown in xxx.  The prevalence of FGC are \%, \%, \% and \% in Kenya, Mali, Nigeria and Sierra Leon accordingly.
+Baseline socio-demographic and sample characteristics are shown in xxx.
+The prevalence of FGC are \%, \%, \% and \% in Kenya, Mali, Nigeria and Sierra Leon accordingly, and \%, \%, \% and \%  of the samples thought FGC should continue as well.
+
+The results of the three models are at ____.
+The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and community level of women’s fgc status; so as the following factors:  country, media, education, age and religion and the community levels of media, education.
+We did not find clear association of the community level of beliefs of fgc benefits and the three responses.
+
+\cfcmt{main predictors:  beliefs of FGC benefits, woman's FGC status and attitudes of gender equality}
 

### 2019-03-01 manuscript.tex
Update manuscript.tex

@@
 
-Attitudes and Social Norms (Attitudes) of Female Genital Cutting in Kenya, Mali, Nigeria and Sierra Leon
+Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
+\cfcmb{This title is a rebuttal to Efferson’s title}
 
@@
 The results of the three models are at ____.
-The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and community level of women’s fgc status; so as the following factors:  country, media, education, age and religion and the community levels of media, education.
+The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and FGC prevalence in a community; so as the following factors:  country, media, education, age and religion and the community levels of media, education.
 We did not find clear association of the community level of beliefs of fgc benefits and the three responses.
@@
 --Main interpretation --
+
+Our findings showed that women’s decision on cutting their daughters was clearly associated with their own FGC status and beliefs in FGC benefits at a population (?) level and FGC prevalent at a community level; the results also applied to their views of FGC continuity .
+However, the women’s beliefs of FGC benefits in cutting women at a community level did not play as a clear factor in all the three FGC preferences.
+Our findings implies that the practice of FGC is a social norm in terms of how a community as a whole carried out the practice.
+
+Regarding the daughter model,
+
 --- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs.
@@
 Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
+
 --- community levels of impact and intervention
@@
 \cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
+
 --- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
@@
 % “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})
+
 --- by nations
@@
 
-===============================
-Concerns:
-
-We did not consider ages of women's daughters.
-For those whose daufhter is over 15(?), they were not likely to fgc them, but it doesnt' mean they are againt fgc.
-It might just mean the daughters were too old to be fgced.
-===============================
+==========
 
@@
 
-Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShell18} vs. no-tolerance, fgc vs. mc \cite{WahlEsse18}?
+Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShell18} vs.
+no-tolerance, fgc vs.
+mc \cite{WahlEsse18}?
+We suggest to position ourselves in a context where male circumcision (MC) is practices and accepted; to consider the differences of a prick of FGC and MC; to comprehend the outcomes of abolishing FGC vs.
+changing FGC practices.
 

### 2019-03-18 manuscript.tex
Edit in github
Push with Chyun

@@
 \newcommand{\jdcmt}[1]{\comment{JD: #1}}
-\newcommand{\jdmlcmt}[1]{\comment{JDML: #1}}
 \newcommand{\mlcmt}[1]{\comment{MLi: #1}}
@@
 Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
-\cfcmb{This title is a rebuttal to Efferson’s title}
+\cfcmt{This title is a response to Efferson’s title}
 
@@
 
-It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low. I would
-expect a majority under 15, no?}\cf{Most of the surveys sampled women of 15-49, girls under 15 were reported by their mothers.
-The ration of girls under 15 is minority} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (updated Sep 18).
-United Nation has declared zero tolerance for FGC as it violates human rights and promoted the abundance of the practice  \cite{}.
-The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
-http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jd{This claim is surprising, and the sources are not
+It is estimated that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East \cite{UNFPA14, UNIC16} \cf{updated Sep 18}.
+The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{}.
+Current progress of in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
+http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jdcmt{This claim is surprising, and the sources are not
 academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}.
-Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.
+\jdcmt{Not all UN sources are the same.
+The factsheet does not even seem to say that.} Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.
 FGC is also known as female genital mutilation and female circumcision;

### 2019-03-18 manuscript.tex
Working with chyun

@@
 \newcommand{\cfcmt}[1]{\comment{CFS: #1}}
-\newcommand{\cf}[1]{\comment{CFS only: #1}}
+\newcommand{\cfonly}[1]{\comment{CFS only: #1}}
 \newcommand{\jdcmt}[1]{\comment{JD: #1}}
@@
 
-It is estimated that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East \cite{UNFPA14, UNIC16} \cf{updated Sep 18}.
+It is estimated that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East \cite{UNFPA14, UNIC16} \cfonly{updated Sep 18}.
 The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{}.
@@
 http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jdcmt{This claim is surprising, and the sources are not
-academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}.
+academic.}\cfcmt{UN is supposed to be reliable and often quoted by academic papers}.
 \jdcmt{Not all UN sources are the same.
@@
 we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
-Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).
+Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)) \jd{How do you see the Tostan fitting in? Or is that a cfonly thing?.
 
@@
 Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
-\cf{FGC module at https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}
+\cfcmt{FGC module at https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}
 
 \subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
-\cf{\cite{Rima08}}*
+\cfonly{\cite{Rima08}}*
 
@@
 
-In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cf{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
+In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
 Cluster  was used to represent a community level of impact \cite{AligRen06, Hayf05}
@@
 `` \cite{Hayf05}
-\cf{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
+\cfcmt{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
 Consequently, the spatial analysis will be affected by some random fluctuations.
@@
 
-\cf{reference: Methods and the first paragraph of Discussion\cite{Chia14}}
+\cfcmt{reference: Methods and the first paragraph of Discussion\cite{Chia14}}
 
@@
 % ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
-\cf{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
+\cfcmt{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
 FGC allows women to gain social capitals and access to networks.
@@
 % mother-daughter: \cite{PashPonn16}
-% \cf{the structure:  cultural and legal background; comparison of our findings to previous studies; implications}
+% \cfcmt{the structure:  cultural and legal background; comparison of our findings to previous studies; implications}
 % Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status \cit{Hayf05}
@@
 % success in community education program to abandon FGC \cite{DiopAske09}
-%\cf{convention theory mainly work on norms or also on behaviour change?
+%\cfcmt{convention theory mainly work on norms or also on behaviour change?
 There seems a gap between norm and behaviour in FGC, can diffusion theory brigade the gap?
@@
 
-\cf{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
+\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
 
@@
 
-%\cf{a sentence on the national FGC policy of the 4 nations and gender law}
+%\cfcmt{a sentence on the national FGC policy of the 4 nations and gender law}
 % "In 1997, the Ministry for the Promotion of Women in Mali created a National Committee Against Violence Towards Women that links all the international organizations active in preventing FGC in Mali" "In 2001, the Kenya legislature adopted a law banning FGC." "the founding father of the country (Kenyatta, 1962) explicitly linked FGC to nationalist pride."
@@
 
-%\cf{Bicchieri's norm theory—
+%\cfcmt{Bicchieri's norm theory—
 behaviour:  What the responder do 
@@
 \cite{Bicc06}
-First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \cf{normative norm?}
+First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \cfcmt{normative norm?}
 and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.
-Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cf{empirical norm?}?
+Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cfcmt{empirical norm?}?
 
@@
 
-% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cf{I don't know if I want to cite \cite{EffeVogt15}.
+% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{I don't know if I want to cite \cite{EffeVogt15}.
 It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).
 
-% \cf{TOSTAN uses a strategy based on convention theory's critical mass to eradicate FGC (see (Wils13}}
+% \cfcmt{TOSTAN uses a strategy based on convention theory's critical mass to eradicate FGC (see (Wils13}}
  * Festinger (1950?):  Social pressure in informal groups

### 2019-03-25 manuscript.tex
Update manuscript.tex

@@
 
-It is estimated that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East \cite{UNFPA14, UNIC16} \cfonly{updated Sep 18}.
-The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{}.
-Current progress of in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
-http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jdcmt{This claim is surprising, and the sources are not
-academic.}\cfcmt{UN is supposed to be reliable and often quoted by academic papers}.
-\jdcmt{Not all UN sources are the same.
-The factsheet does not even seem to say that.} Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.
-FGC is also known as female genital mutilation and female circumcision;
-we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
-Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)) \jd{How do you see the Tostan fitting in? Or is that a cfonly thing?.
+It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.
+The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08}.
+Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see
+http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18).
+Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.
+FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.
+The types of FGC vary from just a knick to a sever sewing of the genital area.
+Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.
+FGC(cirumcision) may be the best for current situation globally.)
 
-The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the
+The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}; but the
 progress is hindered due to the complicated history of the very practice \cite{cite}.
@@
 % Overall:
+
+% To question the difference between MC and FGC if FGC can be minimized to the form of “just a knick” or type I or minor.
 
@@
 changing FGC practices.
+\cite{WahlEsse18}:  from sameness to differences, a global multicultural approach especially during the international migration across the globe.
 
@@
 1. Is there a tipping point?  Can our findings disclose some ideas on fgc intervention in terms of behavioural change in order to reach a tipping point?
+
+_ Following up project:
+ Threshold on FGC:  based on our finding, mother’s FGC status and community FGC prevalence is a good predictor of daughter’s future FGC status.
+We can use newer DHS of multiple nations to predict the future of FGC practice.
+
 \subsection{Funding}\label{Funding}

### 2019-03-25 manuscript.tex
Update manuscript.tex
Cleaning up tex problems

@@
 \documentclass[12pt,]{article}
+\usepackage[utf8]{inputenc}
 \usepackage{lmodern}
@@
 \usepackage{longtable}
-\usepackage{hyperref}
+\usepackage{url,hyperref}
 \hypersetup{unicode=true,
@@
 Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see
-http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18).
+\url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).
 Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.
@@
 The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
-Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s beliefs of FGC benefits and FGC continuance; and “future_daughter” model to examine the association of beliefs of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positions change the main model.
+Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s beliefs of FGC benefits and FGC continuance; and “futureDaughter” model to examine the association of beliefs of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positions change the main model.
 
@@
 Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
-\cfcmt{FGC module at https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}
+\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
 
@@
 - 3 figures of the results of the 3 models
-- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/, Fig 1)
+- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)
 % figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
@@
 ---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
-1. comparison: \cite{Chia14, Hayf05}, and [http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]
+1. comparison: \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
 ---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali.
@@
 We can use newer DHS of multiple nations to predict the future of FGC practice.
+We can use data without fgc benefit module, and that will give us more data than the current 4 nations.
 
@@
 
-\bibliography{refs}
+\bibliography{manual}
 

### 2019-03-28 manuscript.tex
Update manuscript.tex

@@
 
-Social norm is \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} a fundamental approach in understanding FGC practice while human rights and feminist theory entails \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of intervening and abolishing	the practices.
+Social norm is \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} a fundamental approach in understanding FGC practice while human rights and feminist theory entails \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} and modernization theory \cite{BoylMcMo02, (see BellNova15 and Hayf05 for reference)}entails reasons of intervening and abolishing the practices.
 Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
@@
 Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), gender perspective can shed lights on how women’s gender values intertwine with convention theory of FGC values \cite{cites}.
+Modernization theory proposed that, for example, education and \cite{BoylMcMo02, Youn02} can contribute to the reduction of FGC practice.
 Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.
@@
 The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.
+The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.
 The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.
@@
 
+% Comparison of individual vs. village contribution to the variation of women’s fgc status to fgc future (see Fig 2 https://www.sciencedirect.com/science/article/pii/S0304387815000620#bb0230)
+
 -- Second interpretation --
@@
 
+% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors.
+This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.” \cite{BellNova15}
+
 \comment{cf: how to cite \cite{AkhmWord13,EffeVogt15} and compare these two?}
@@
  \cite{Shel-Wand11}:  supporting Mackie's convetion theory ``expections regarding fgc are interdependent...."
+
+% suggestions:  to invite elder woman to participate in reducing FGC \cite{ShelMore18}
 
@@
 It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).
+Can heterogeneity explain the differences of beliefs in FGC benefits at individual level vs.
+at a community level?
 

### 2019-03-29 daughterfgc_full_clmm.R
Need to add individual-level benefits back in

@@ -5,7 +5,7 @@ library(splines)
 modAns <- model.frame(
   futurefgcDau ~ fgcstatus + group_fgc
   + CC
-  #+ bene 
+  + bene 
   + group_bene
   + media + group_media 
   + gender + group_gender
@@ -19,7 +19,7 @@ modAns <- model.frame(
 fit_time <- system.time(mod<- clmm(
   futurefgcDau ~ fgcstatus + group_fgc
   + CC
-  #+ bene 
+  + bene 
   + group_bene
   + media + group_media 
   + gender + group_gender 

### 2019-03-29 futurefgcDau_full_clmm.R

@@ -11,7 +11,7 @@ modAns <- model.frame(
   futurefgcDau ~ futurefgc + group_futurefgc
   + fgcstatus + group_fgc
   + CC
-#  + bene 
+  + bene 
   + group_bene
   + media + group_media 
   + gender + group_gender 
@@ -26,7 +26,7 @@ system.time(mod<- clmm(
   futurefgcDau ~ futurefgc + group_futurefgc
   + fgcstatus + group_fgc
   + CC
-#  + bene 
+  + bene 
   + group_bene
   + media + group_media 
   + gender + group_gender 

### 2019-03-29 futurefgc_full_clmm.R

@@ -5,7 +5,7 @@ library(splines)
 modAns <- model.frame(
   futurefgc ~ fgcstatus + group_fgc
   + CC
-#  + bene 
+  + bene 
   + group_bene
   + media + group_media 
   + gender + group_gender
@@ -19,7 +19,7 @@ modAns <- model.frame(
 system.time(mod <- clmm(
   futurefgc ~ fgcstatus + group_fgc
   + CC
-#  + bene
+  + bene
   + group_bene
   + media + group_media 
   + gender + group_gender

### 2019-04-01 manuscript.tex
Update manuscript.tex

@@
 It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.
-The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08}.
-Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see
-\url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).
-Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.
+Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).
 FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.
@@
 
-The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}; but the
-progress is hindered due to the complicated history of the very practice \cite{cite}.
+The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.
+The progress is hindered due to the complicated history of the very practice \cite{Cami16}.
 The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.
 
-Social norm is \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} a fundamental approach in understanding FGC practice while human rights and feminist theory entails \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} and modernization theory \cite{BoylMcMo02, (see BellNova15 and Hayf05 for reference)}entails reasons of intervening and abolishing the practices.
+Social norm is a fundamental approach in comprehending and intervening FGC practice \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.
 Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
 FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.
-When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC targeting women's social networks, which are intergenerational, interdependent and interconnected across generations and genders was proposed \cite{Mack00, DuncWand11, ShelWand11}.
+When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}.
+\cfonly{add \cite{Bicc15}}
 
-There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.
-Both convention theory and gender approaches centre on values of how FGC associates with identity \cte{cites}.
-Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), gender perspective can shed lights on how women’s gender values intertwine with convention theory of FGC values \cite{cites}.
-Modernization theory proposed that, for example, education and \cite{BoylMcMo02, Youn02} can contribute to the reduction of FGC practice.
-Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.
+\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, more} and other norm studies of why mother cut daughters etc}
+
+Although convention theory was well deliberated and applied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges \cite{EffeVogt15} and multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13}.
 
@@
 Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.
-This study takes both the dynamics of beliefs of FGC benefits and of intention of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).
+This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).
 We developed three models in this study.
 The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
-Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s beliefs of FGC benefits and FGC continuance; and “futureDaughter” model to examine the association of beliefs of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positions change the main model.
+Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of cutting daughters to understand how such positions change the main model.
 
@@
 
+% FGC laws in those nations
 % collective action problem referring to community level of impact
@@
 % The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors.
-This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.” \cite{BellNova15}
+This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.
 
@@
 
+%There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}…..Modernization theory proposed that, for example, education and \cite{BoylMcMo02, Youn02} can contribute to the reduction of FGC practice.
+
 \subsection{Conclusion}\label{Conclusion}

### 2019-04-01 ordfuns.R
Fixed the scales on the plots

@@ -1,14 +1,14 @@
-ordTrans <- function(v, a){
+ordTrans <- function(v, a, s){
   sapply(v, function(n){
-    return(sum(plogis(n-a)))
+    return(sum(plogis(n-a))*(1/s))
   })
 }
 
 ordpred <- function(mod, n, modAns){
   v <- varpred(mod, n, modAns, isolate=TRUE)
-  v$fit <- ordTrans(v$fit, mod$alpha)
-  v$lwr <- ordTrans(v$lwr, mod$alpha)
-  v$upr <- ordTrans(v$upr, mod$alpha)
+  v$fit <- ordTrans(v$fit, mod$alpha, length(mod$alpha))
+  v$lwr <- ordTrans(v$lwr, mod$alpha, length(mod$alpha))
+  v$upr <- ordTrans(v$upr, mod$alpha, length(mod$alpha))
   return(v)
 }
 

### 2019-04-01 manuscript.tex
figures are done and in place

@@
 \usepackage{url,hyperref}
+\usepackage{graphicx}
+\usepackage{grffile}
+
 \hypersetup{unicode=true,
@@
 % a chart like figure 8-8D \cite{UNIC13}
+
+\includegraphics[scale= 0.7, page=1]{./git_push/futurefgc_full.isoplots.Rout.pdf}
+\includegraphics[scale=0.7,page=2]{./git_push/futurefgc_full.isoplots.Rout.pdf}
+\includegraphics[scale=0.7,page=1]{./git_push/daughterfgc_full.isoplots.Rout.pdf}
+\includegraphics[scale=0.7,page=2]{./git_push/daughterfgc_full.isoplots.Rout.pdf}
+\includegraphics[scale=0.7,page=1]{./git_push/futurefgcDau_full.isoplots.Rout.pdf}
+\includegraphics[scale=0.7,page=2]{./git_push/futurefgcDau_full.isoplots.Rout.pdf}
 

### 2019-04-01 iso.R

@@ -16,47 +16,39 @@ isoList <- lapply(predNames, function(n){
 
 print(length(isoList))
 
-for(i in 1:length(isoList)){
-	print(varPlot(isoList[[i]]))
-}
+#for(i in 1:length(isoList)){
+#	print(varPlot(isoList[[i]]))
+#}
 
-quit()
 
 ## futurefgc_ind, daughterfgc_ind
 print(
-grid.arrange(varPlot(isoList[[1]]),#P=varlvlsum$`Pr(>Chisq)`[1]),
-             varPlot(isoList[[2]]),#P=varlvlsum$`Pr(>Chisq)`[2]),
-             varPlot(isoList[[3]]),#P=varlvlsum$`Pr(>Chisq)`[3]),
-             varPlot(isoList[[4]]),#P=varlvlsum$`Pr(>Chisq)`[4]),
-             varPlot(isoList[[5]]),#P=varlvlsum$`Pr(>Chisq)`[5]),
-             varPlot(isoList[[6]]),#P=varlvlsum$`Pr(>Chisq)`[6]),
-             varPlot(isoList[[7]]),#P=varlvlsum$`Pr(>Chisq)`[7]),
-             varPlot(isoList[[8]]),#P=varlvlsum$`Pr(>Chisq)`[8]),
-             varPlot(isoList[[9]]),#P=varlvlsum$`Pr(>Chisq)`[9]),
-             varPlot(isoList[[10]]),#P=varlvlsum$`Pr(>Chisq)`[10]),
-             varPlot(isoList[[11]]),#P=varlvlsum$`Pr(>Chisq)`[11]),
-             varPlot(isoList[[12]]),#P=varlvlsum$`Pr(>Chisq)`[[12]]),
+grid.arrange(varPlot(isoList[[1]] ,P=varlvlsum$`Pr(>Chisq)`[1]),
+             varPlot(isoList[[2]] ,P=varlvlsum$`Pr(>Chisq)`[2]),
+             varPlot(isoList[[3]] ,P=varlvlsum$`Pr(>Chisq)`[3]),
+             varPlot(isoList[[4]] ,P=varlvlsum$`Pr(>Chisq)`[4]),
+             varPlot(isoList[[5]] ,P=varlvlsum$`Pr(>Chisq)`[5]),
+             varPlot(isoList[[6]] ,P=varlvlsum$`Pr(>Chisq)`[6]),
+             varPlot(isoList[[7]] ,P=varlvlsum$`Pr(>Chisq)`[7]),
[…]

### 2019-04-02 effects_plot.R
effect plots complete

@@ -1,0 +1,15 @@
+library(ggplot2)
+
+gg <- (ggplot(betadf
+		, aes(x=reorder(variable,beta), y=beta, ymin=lower, ymax=upper, colour=inCI))
+	+ geom_pointrange()
+	+ scale_colour_manual(values=c("black","gray"))
+	+ geom_hline(yintercept=0)
+	+ coord_flip()
+	+ theme_bw()
+	+ ggtitle(rtargetname)
+	+ xlab("predictors")
+)
+
+print(gg)
+

### 2019-04-02 single_var_effect.R

@@ -1,0 +1,42 @@
+library(ordinal)
+library(dplyr)
+library(tidyr)
+
+beta_est <- coef(mod)
+beta_ci <- confint(mod)
+
+beta_dat <- cbind(beta_est,beta_ci)
+dd <- data.frame(beta_dat, variable=rownames(beta_dat))
+colnames(dd) <- c("beta", "lower", "upper", "variable")
+
+mm <- as.data.frame(modAns)
+
+## changing all categorical variables to numeric
+mm2 <- (mm
+  %>% rowwise()
+  %>% dplyr:::summarise_all(funs(as.numeric(.)))
+)
+x_keep <- (mm
+  # %>% 
+  %>% dplyr:::summarise_all(funs(as.numeric(!is.numeric(.))*length(unique(.))))
+  %>% gather(variable,levels)
+  %>% filter(levels<=2)
+)
+
+betadf <- (mm2
+   %>% dplyr:::summarise_all(funs(sd))
+   %>% gather(variable,sd)
+   %>% left_join(.,x_keep) ## creating keep 
+   %>% mutate(variable = ifelse(variable == "fgcstatus","fgcstatusYes",variable)
+        , variable = ifelse(variable == "job","jobYes",variable))
+   %>% left_join(.,dd) ## joining beta df
+   %>% filter(complete.cases(.))
+   %>% rowwise()
+   %>% mutate(beta = beta*sd
+              , lower = lower*sd
+              , upper = upper*sd
+              , inCI = between(0,lower,upper)
+   )
+)
+
+

### 2019-04-02 manuscript.tex
Update manuscript.tex

--- 2019-04-01 manuscript.tex
@@
 The progress is hindered due to the complicated history of the very practice \cite{Cami16}.
-The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.
 
@@
 
-\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, more} and other norm studies of why mother cut daughters etc}
+\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, ShelWand11, more} and other norm studies of why mother cut daughters etc}
 
@@
 
-Our findings showed that women’s decision on cutting their daughters was clearly associated with their own FGC status and beliefs in FGC benefits at a population (?) level and FGC prevalent at a community level; the results also applied to their views of FGC continuity .
-However, the women’s beliefs of FGC benefits in cutting women at a community level did not play as a clear factor in all the three FGC preferences.
-Our findings implies that the practice of FGC is a social norm in terms of how a community as a whole carried out the practice.
+Our findings showed that women’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.
+The similar results also applied to women’s view of whether FGC should be continued \cf{link}.
+\cfjd{How to use the future-mother producing daughter model?}.
+Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .
 
-Regarding the daughter model,
+— Norm —
 
---- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs.
-modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs.
-gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).
-% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
-% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
-\cfcmt{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
+- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. 
+- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
+- \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
 FGC allows women to gain social capitals and access to networks.
 Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
+\cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}
 
---- community levels of impact and intervention
+- community level of effects -
+
+- tipping point/threshold -
+
+— secondary analysis/socio demograhpic —
+
+- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} .
+
+— Suggestions —
+- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
+- MC vs.
+FGC.
+Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice.
+(I'm not sure if I'm comfortable with this position, but it is an alternative.)
+
+\subsection{Conclusion}\label{Conclusion}
+
+==================================
 \cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
@@
 
--- Second interpretation --
+OVERALL:
+% “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})
+% Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}.
+It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).
+
+— Second interpretation —
 --- socio demographic interpretation at both levels (link this to modernization?)
@@
 
-\cfcmt{feminism or women’s rights perspective:  which women?  Who are the women?  Women from the West or women from inside the fgc communities?}
-
-% “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})
-
---- by nations
+— by nations —
 ---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
@@
 
-==========
+% FGC laws in those nations
 
-% FGC laws in those nations
-% collective action problem referring to community level of impact
-Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}.
-It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).
-
+=================
 % The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors.
@@
 
-% If convention theory is more than just about securing marriage market (e.g., peer convention), then it is a theory about norms in general, isn't it?
-That is, types of norms explain better than just marriage market.
-
 % Overall:
@@
 the same or?)
-
-% Others:
 
@@
 
-% \cite{BergDeni13}: application/public policy ``A realist synthesis of controlled studies to determine the effectiveness of interventions to prevent genital cutting of girls.``
-
 %Except for Mali, all the studied nations have enacted decrees or legislation related to FGC \cite{WHO13}
@@
 
-A synthesis of context studies of Africa showed that the main factors that supported FGC were tradition, religion, and reduction of women's sexual desire, and the main factors hindered FGM/C were medical complications and prevention of sexual satisfaction.
-\cite{BergDeni12a}.
-For example, in Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.
+In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.
 In Kenya, woman's decision on whether to cut their daughters' genitals were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.
@@
 % Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
-
-% `` the effectiveness of interventions was hampered by a general lack of information.
-However, through the realist synthesis we identified that all of the interventions were based on a theory that dissemination of information improves cognitions about FGM/C, but the interventions' success was contingent upon a range of contextual factors.
-`` \cite{BergDeni12a}
 
@@
 
-It is inevitable to compare male circumcision to female genital cutting and question how male circumcision gain its cultural recognition but not FGC.
-Considering the acceptance of Alternative rights of passage \cite{GaluKama15} may be an alternative without criminalize the practice.
-(I'm not sure if I'm comfortable with this position, but it is an alternative thought.)
-
-To study types of FGC for the future to understand correlation/assocaition between types of fgc and fgc beneifts.
-
---- questions worth addressing
-1. Is there a tipping point?  Can our findings disclose some ideas on fgc intervention in terms of behavioural change in order to reach a tipping point?
-
-_ Following up project:
- Threshold on FGC:  based on our finding, mother’s FGC status and community FGC prevalence is a good predictor of daughter’s future FGC status.
-We can use newer DHS of multiple nations to predict the future of FGC practice.
-We can use data without fgc benefit module, and that will give us more data than the current 4 nations.
-
+====================================
 \subsection{Funding}\label{Funding}

### 2019-04-07 community.R
Autocommit (fgc)

@@ -1,4 +1,10 @@
-##df for mcmcglmm fit
+## norm
+## we want to calculate the community avg but not including the individual
+## the logic to do it is:
+## create the denominator (d1) by taking the sum
+## create the numerator (n1) by taking the mean of the group * d1
+## new denominator (d2) = d1-1
+## new numerator n1 - my response 
 
 library(dplyr)
 
@@ -21,21 +27,34 @@ Answers <- (Answers
 	%>% left_join(., attframe)
 	%>% left_join(., mediaframe)
 	%>% group_by(clusterId)
-	%>% mutate(
-		group_fgc = mean(fgc, na.rm = TRUE)
-      , group_futurefgcDau = mean(futurefgcDau01, na.rm = TRUE)
-      , group_futurefgc = mean(futurefgc01, na.rm = TRUE)
-	   , group_bene = mean(bene, na.rm = TRUE)
-	   , group_gender = mean(gender, na.rm = TRUE)
-	   , group_media = mean(media, na.rm = TRUE)
-	   , group_edu = mean(edu, na.rm = TRUE)
-	   , group_wealth = mean(wealth, na.rm = TRUE)
+	%>% mutate(fgc_d = sum(!is.na(fgc))
+		, fgc_n = mean(fgc,na.rm=TRUE)*fgc_d - fgc
+		, group_fgc = fgc_n/(fgc_d-1)
+		, futurefgcDau_d = sum(!is.na(futurefgcDau))
+		, futurefgcDau_n = mean(futurefgcDau01, na.rm=TRUE)*futurefgcDau_d - futurefgcDau01
+      , group_futurefgcDau = futurefgcDau_n/(futurefgcDau_d-1)
+		, futurefgc_d = sum(!is.na(futurefgc))
+		, futurefgc_n = mean(futurefgc01, na.rm=TRUE)*futurefgc_d - futurefgc01
+      , group_futurefgc = futurefgc_n/(futurefgc_d - 1)
+	   , bene_d = sum(!is.na(bene))
+		, bene_n = mean(bene, na.rm=TRUE)*bene_d - bene
+		, group_bene = bene_n/(bene_d - 1)
+		, gender_d = sum(!is.na(gender))
+	   , gender_n = mean(gender, na.rm = TRUE)
+		, group_gender = gender_n/(gender_d - 1)
+		, media_d = sum(!is.na(media))
[…]

### 2019-04-07 daughterfgc_full_clmm.R

@@ -3,7 +3,8 @@ library(splines)
 
 
 modAns <- model.frame(
-  futurefgcDau ~ fgcstatus + group_fgc
+  futurefgcDau ~ group_futurefgcDau
+  + fgcstatus + group_fgc
   + CC
   + bene 
   + group_bene
@@ -17,7 +18,8 @@ modAns <- model.frame(
 )
 
 fit_time <- system.time(mod<- clmm(
-  futurefgcDau ~ fgcstatus + group_fgc
+  futurefgcDau ~ group_futurefgcDau
+  + fgcstatus + group_fgc
   + CC
   + bene 
   + group_bene

### 2019-04-07 futurefgcDau_full_clmm.R

@@ -8,7 +8,8 @@ combined_dat <- (combined_dat
 )
 
 modAns <- model.frame(
-  futurefgcDau ~ futurefgc + group_futurefgc
+  futurefgcDau ~ group_futurefgcDau
+  + futurefgc + group_futurefgc
   + fgcstatus + group_fgc
   + CC
   + bene 
@@ -23,7 +24,8 @@ modAns <- model.frame(
 )
 
 system.time(mod<- clmm(
-  futurefgcDau ~ futurefgc + group_futurefgc
+  futurefgcDau ~ group_futurefgcDau
+  + futurefgc + group_futurefgc
   + fgcstatus + group_fgc
   + CC
   + bene 

### 2019-04-07 futurefgc_full_clmm.R

@@ -3,7 +3,8 @@ library(splines)
 
 
 modAns <- model.frame(
-  futurefgc ~ fgcstatus + group_fgc
+  futurefgc ~ group_futurefgc
+  + fgcstatus + group_fgc
   + CC
   + bene 
   + group_bene
@@ -17,7 +18,8 @@ modAns <- model.frame(
 )
 
 system.time(mod <- clmm(
-  futurefgc ~ fgcstatus + group_fgc
+  futurefgc ~ group_futurefgc
+  + fgcstatus + group_fgc
   + CC
   + bene
   + group_bene

### 2019-04-07 community.R
Autocommit (fgc)

@@ -1,10 +1,10 @@
 ## norm
 ## we want to calculate the community avg but not including the individual
 ## the logic to do it is:
-## create the denominator (d1) by taking the sum
-## create the numerator (n1) by taking the mean of the group * d1
-## new denominator (d2) = d1-1
-## new numerator n1 - my response 
+## create the denominator (d1) by taking the number of people in the community
+## create the new_numerator (n1) by taking the sum of all responses minus the individual of interest
+## new_denominator (d2) = d1-1
+## new group mean = new_numerator/new_denominator
 
 library(dplyr)
 
@@ -28,28 +28,28 @@ Answers <- (Answers
 	%>% left_join(., mediaframe)
 	%>% group_by(clusterId)
 	%>% mutate(fgc_d = sum(!is.na(fgc))
-		, fgc_n = mean(fgc,na.rm=TRUE)*fgc_d - fgc
+		, fgc_n = sum(fgc,na.rm=TRUE) - fgc
 		, group_fgc = fgc_n/(fgc_d-1)
 		, futurefgcDau_d = sum(!is.na(futurefgcDau))
-		, futurefgcDau_n = mean(futurefgcDau01, na.rm=TRUE)*futurefgcDau_d - futurefgcDau01
+		, futurefgcDau_n = sum(futurefgcDau01, na.rm=TRUE) - futurefgcDau01
       , group_futurefgcDau = futurefgcDau_n/(futurefgcDau_d-1)
 		, futurefgc_d = sum(!is.na(futurefgc))
-		, futurefgc_n = mean(futurefgc01, na.rm=TRUE)*futurefgc_d - futurefgc01
+		, futurefgc_n = sum(futurefgc01, na.rm=TRUE) - futurefgc01
       , group_futurefgc = futurefgc_n/(futurefgc_d - 1)
 	   , bene_d = sum(!is.na(bene))
-		, bene_n = mean(bene, na.rm=TRUE)*bene_d - bene
+		, bene_n = sum(bene, na.rm=TRUE) - bene
 		, group_bene = bene_n/(bene_d - 1)
 		, gender_d = sum(!is.na(gender))
-	   , gender_n = mean(gender, na.rm = TRUE)
+	   , gender_n = sum(gender, na.rm = TRUE) - gender
 		, group_gender = gender_n/(gender_d - 1)
 		, media_d = sum(!is.na(media))
[…]

### 2019-04-08 effects_plot.R
Done?

@@ -1,10 +1,10 @@
 library(ggplot2)
 
 gg <- (ggplot(betadf
-		, aes(x=reorder(variable,beta), y=beta, ymin=lower, ymax=upper, colour=inCI))
+		, aes(x=reorder(variable,beta), y=beta, ymin=lower, ymax=upper))
 	+ geom_pointrange()
-	+ scale_colour_manual(values=c("black","gray"))
-	+ geom_hline(yintercept=0)
+#	+ scale_colour_manual(values=c("black","gray"))
+	+ geom_hline(yintercept=0,lty=2)
 	+ coord_flip()
 	+ theme_bw()
 	+ ggtitle(rtargetname)

### 2019-04-08 iso.R

@@ -9,16 +9,34 @@ attr(modAns,"terms") <- NULL
 
 catNames <- c("religion","urRural","job","maritalStat")
 predNames <- colnames(modAns)[2:(ncol(modAns)-2)]
+predNames <- c("CC","religion","maritalStat","age","wealth","group_wealth")
+predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)","ns(group_wealth, 3)")
+
 
 isoList <- lapply(predNames, function(n){
   ordpred(mod, n, modAns)
 })
 
-print(length(isoList))
-
 #for(i in 1:length(isoList)){
 #	print(varPlot(isoList[[i]]))
 #}
+
+varlvlsum <- varlvlsum[predsummary,]
+print(
+  grid.arrange(varPlot(isoList[[1]] ,P=varlvlsum$`Pr(>Chisq)`[1]),
+               varPlot(isoList[[2]] ,P=varlvlsum$`Pr(>Chisq)`[2]),
+               varPlot(isoList[[3]] ,P=varlvlsum$`Pr(>Chisq)`[3]),
+               varPlot(isoList[[4]] ,P=varlvlsum$`Pr(>Chisq)`[4]),
+               varPlot(isoList[[5]] ,P=varlvlsum$`Pr(>Chisq)`[5]),
+               varPlot(isoList[[6]] ,P=varlvlsum$`Pr(>Chisq)`[6]),
+					nrow=2
+					
+					)
+)
+
+quit()
+
+## All iso plots
 
 
 ## futurefgc_ind, daughterfgc_ind
@@ -41,7 +59,7 @@ grid.arrange(varPlot(isoList[[1]] ,P=varlvlsum$`Pr(>Chisq)`[1]),
 
 
 ## futurefgc_full, daughterfgc_full
-if(nrow(varlvlsum)==18){
+if(nrow(varlvlsum)==19){
   print(
     grid.arrange(varPlot(isoList[[13]],P=varlvlsum$`Pr(>Chisq)`[13]),
                  varPlot(isoList[[14]],P=varlvlsum$`Pr(>Chisq)`[14]),
@@ -49,13 +67,14 @@ if(nrow(varlvlsum)==18){
                  varPlot(isoList[[16]],P=varlvlsum$`Pr(>Chisq)`[16]),
                  varPlot(isoList[[17]],P=varlvlsum$`Pr(>Chisq)`[17]),
[…]

### 2019-04-08 single_var_effect.R

@@ -28,7 +28,9 @@ betadf <- (mm2
    %>% gather(variable,sd)
    %>% left_join(.,x_keep) ## creating keep 
    %>% mutate(variable = ifelse(variable == "fgcstatus","fgcstatusYes",variable)
-        , variable = ifelse(variable == "job","jobYes",variable))
+        , variable = ifelse(variable == "job","jobYes",variable)
+		  , variable = ifelse(variable == "urRural","urRuralRural",variable)
+		  )
    %>% left_join(.,dd) ## joining beta df
    %>% filter(complete.cases(.))
    %>% rowwise()
@@ -39,4 +41,4 @@ betadf <- (mm2
    )
 )
 
-
+print(betadf)

### 2019-04-08 manuscript.tex
Update manuscript.tex

@@
 
-\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, ShelWand11, more} and other norm studies of why mother cut daughters etc}
+\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, Rima08, ShelWand11, more} and other norm studies of why mother cut daughters etc}
 
@@
 
-- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. 
-- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
-- \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
+- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
+- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}.
+“alternative convention/peer convention\cite{ShelWand11}
+ \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
 FGC allows women to gain social capitals and access to networks.
@@
 \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}
+\cite{PashPonn16}: Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms
 
 - community level of effects -
-
+\cite{ChegAske04}(community -based approach), \cite{BrowBeec13, Hayf05, KandShel19, PatrSing15, ShelWand11}
+\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
 - tipping point/threshold -
@@
 
-- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} .
+- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02}. 
+ \cit{Hayf05}  Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status
+\cite{KandNwak09,VanMeek15} proposing various factors impacting FGC practices, such as women's education
+
+\cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
+\cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
+\cite{Hayf05, PashPonn16} (more)
+% education:  \cite{IliyAbub12, KarmKand11}
+% religion:  \cite{KarmKand11}
 
@@
 Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice.
-(I'm not sure if I'm comfortable with this position, but it is an alternative.)
+(I'm not sure if I'm comfortable with this position, but it is an alternative.) vs.
+focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
 
@@
 \cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),
-\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
 
---- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
-\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
-\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination,” for marital market.
-The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.
-But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
+--- attitudes vs. norm (beliefs) vs. (behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
+\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intention:  attitude, norm and perceived behavioroal control.
+
 \cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))
 
-% Comparison of individual vs. village contribution to the variation of women’s fgc status to fgc future (see Fig 2 https://www.sciencedirect.com/science/article/pii/S0304387815000620#bb0230)
+OVERALL:
+\cite{UNIC13}:  “Many girls who are cut are daughters of women who oppose the practice”
 
-OVERALL:
-% “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})
-% Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}.
-It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).
-
-— Second interpretation —
---- socio demographic interpretation at both levels (link this to modernization?)
-\cite{Hayf05, PashPonn16} (more)
-% education:  \cite{IliyAbub12, KarmKand11}
-% religion:  \cite{KarmKand11}
-
-— by nations —
+— by nations and laws in those nations—
 ---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
-1. comparison: \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
+ vs. \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
 ---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali.
@@
 
----- Sierra Leon: 
-\cite{ShelHern06, ShelHern13}  (Are they on Senegal or Sierra Leone?)
-
-% FGC laws in those nations
+---- Sierra Leone: 
+\cite{Sagn14}
 
@@
 % little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
-% put religion into consideration of our findings (i.e., national distribution of religion, how many muslins in each country)
 % when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09}.
@@
 % mother-daughter: \cite{PashPonn16}
-% \cfcmt{the structure:  cultural and legal background; comparison of our findings to previous studies; implications}
-% Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status \cit{Hayf05}
 
 % Overall:
-
-% To question the difference between MC and FGC if FGC can be minimized to the form of “just a knick” or type I or minor.
 
@@
 FGC is still in practice or a preference among women after migrated to a western environment from their original communities where FGC was a common practice, in the hope (wording?) of preserving their ethnic and gender identity despite its conflict against the  norms and laws of the newly settled society \cite{}; however, a baseline study in Sweden showed that a majority of female immigrants, including those newly arrived, opposed all forms of FGC with increased opposition over time after migration, and suggested that an attitude change had occurred \cite{WahlJohn17}; that suggested a likely influence of convention theory.
-
-(There are also studies proposing various factors impacting FGC practices, such as women's education \cite{KandNwak09,VanMeek15}, social economic status \cite{} etc, community levels of influences.) (What is conventional in convention theory can also be focal points to gender awareness and modern development.
-Question:  What is the differences between convention theory and community level of impact on FGC?
-the same or?)
-
-% To compare with findings in Burkina Faso \cite{KarmKand11}, and Tostan
 
@@
 % Latikin 1995:  Norms o unsafe behaviours are not trivially changed trough information.
-% Beliefs are susceptible social confirmation (Centola)
-% Small world and "hubs" accelerate diseases but slow down behaviours change (Centola)
+% Beliefs are susceptible social confirmation (Damon Centola)
 % a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see \cite{BoylCorl10}, table 1)
@@
 To elaborate the shifted values of fgc, what it imply and how to apply the change to policy.
+\cite{CentBeck18}:  social convention and tipping point
 
@@
 ``We need to find more alternatives and livelihood projects like tailoring[or] salon work to empower our girls who run away from the practice to the rescue centres.""
-
-\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
 

### 2019-04-08 manuscript.tex
Update manuscript.tex

@@
 
-% \cite{Koom14}: `` practices of female excision are so diverse that they may defy generalizable remedies"  ``Rather than relying on common campaign models, transferable advocacy tools, or `best practices,' scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics."
+% \cite{Koom14}: `` practices of female excision are so diverse that they may defy generalizable remedies"  ``Rather than relying on common campaign models, transferable advocacy tools, or `best practices,' scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics."  Instead of straightforward campaigns against traditional culture, "culturalconstestaion" characterized by politicized negotiation and, at times, resistance, was proposed.
+\cite{Koom14}.
+
+A multicultural egalitarian approach respecting both cultural identity and basic legal human rights was addressed \cite{BoylCarb10, Wade11}.
 
@@
 
-%\{cf: a few words on each nation's FGC policy}
 % read \cite{MohaHass14, MuteMill16, PashPonn16, VaroFras14}
-
-A multicultural egalitarian approach respecting both cultural identity and basic legal human rights was addressed \cite{BoylCarb10, Wade11}.
-Instead of straightforward campaigns against traditional culture, "culturalconstestaion" characterized by politicized negotiation and, at times, resistance, was proposed.
-\cite{Koom14}.
 
@@
 
-%\cfcmt{Bicchieri's norm theory—
+%\cfcmt{Bicchieri's norm theory \cite{Bicc06}:
 behaviour:  What the responder do 
@@
 normative expectation: What the responder believes others think she should do
-\cite{Bicc06}
-First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \cfcmt{normative norm?}
-and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.
-Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cfcmt{empirical norm?}?
 
@@
 \cite{UNFPA14, UNIC16}
-\subsection{suggestions and Limitations}\label{suggestions-and-Limitations}
 
@@
 % through laws \cite{AloGbad11}
-
-% Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
 
@@
 % Limitations:  without incorporating national factor in this study.
-
-% \cite{Meye00}:  rational model vs.
-hierarchical identification model; and plus oppression social context.
-That is, knowing ≠ abling ≠ wanting ≠ doing.
-How to apply this concept to theories of feminist/gender, modernization and convention.
 

### 2019-04-09 manuscript.tex
Update manuscript.tex

@@
 University.
+
+\subsection{journals}\label{journals}
+possible consideration:  The Lancet Global Health, Science, BMJ, Bulletin of WHO
 
@@
 - tipping point/threshold -
-
+\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
 — secondary analysis/socio demograhpic —
@@
 
+— by nations and laws in those nations—
+
+%Except for Mali, all the studied nations have enacted decrees or legislation related to FGC \cite{WHO13}
+
+In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.
+In Kenya, woman's decision on whether to cut their daughters' genitals were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.
+
+---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
+ vs. \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
+---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali.
+The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others.
+FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone.
+We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}
+
+---- Nigeria: ``Modernization (education and high socioeconomic status) had minimal impact on the likelihood of FGM, but education plays an important role in the mother's decision not to circumcise her daughter.
+It follows from these findings that community factors have a large effect on FGM, with individual factors having little effect on the distribution of FGM" \cite{KandNwak09}
+
+---- Sierra Leone: 
+\cite{Sagn14}
+
 — Suggestions —
@@
 focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
+- modelling by plotting empirical data to study threshold/tipping point.
+- redesign questions of fgc benefits in DHS
+- inviting faced women migrated to western society to participate in fgc intervention campaign.
+For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}
+
+— Limitation —
+- No FGC types relating to our response varialbes
 
@@
 
-— by nations and laws in those nations—
----- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
- vs. \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
----- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali.
-The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others.
-FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone.
-We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}
-
----- Nigeria: ``Modernization (education and high socioeconomic status) had minimal impact on the likelihood of FGM, but education plays an important role in the mother's decision not to circumcise her daughter.
-It follows from these findings that community factors have a large effect on FGM, with individual factors having little effect on the distribution of FGM" \cite{KandNwak09}
-
----- Sierra Leone: 
-\cite{Sagn14}
-
-=================
 % The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors.
@@
 
-\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
-
 “we find that some older women express an openness to reassessing norms and practices as they seek solutions to maintaining the physical well-being, moral integrity and cultural identity of girls in their families.
 Moreover, given the authority of older women over younger women, they also have power to negotiate change.\cite{ShelMore18}
-% get info on legal situation of FGC in those countries
 
@@
 
-%\cfcmt{a sentence on the national FGC policy of the 4 nations and gender law}
 % "In 1997, the Ministry for the Promotion of Women in Mali created a National Committee Against Violence Towards Women that links all the international organizations active in preventing FGC in Mali" "In 2001, the Kenya legislature adopted a law banning FGC." "the founding father of the country (Kenyatta, 1962) explicitly linked FGC to nationalist pride."
@@
 However, many other factors can contribute to eroding beliefs and arguments in favour of this practice, such as the globalization, culture and social environment of countries in the West." \cite{ReigGonz14}
-
-%Except for Mali, all the studied nations have enacted decrees or legislation related to FGC \cite{WHO13}
 
@@
 Theory:
-% gender symbol \cite{Youn04}
-% gender autonomy \cite{Meye00}: 
-%``Since autonomy-augmenting educational programs are typically developed by cultural initiates who rely on traditional modes of expression and appeal to traditional values, it is reasonable to surmise that autonomy is best extended by avoiding cultural alienation and by building on women's existing autonomy skills."
-% ``autonomy-augmenting programs regard women in cultures that practice female genital cutting as self-determining individuals.
-…they have some understanding of what matters to them and how best to proceed in light of their values and commitments before they participate in such programs.
-… women who are subject to female genital cutting are not without autonomy.
-But this understanding of autonomy entails neither endorsement of female genital cutting nor resignation to its persistence.
-Since cultures that practice female genital cutting may have selectively nurtured and stifled women's autonomy skills, and since these cultures may shield the issue of female genital cutting from exercise of autonomy skills, developing and coordinating women's autonomy skills and extending the range of application of these skills are key to augmenting their autonomy.
-``
+
 % convention or modernization theory?`` campaigns against FGC using educational, health, legal, and human rights–based approaches are at times ineffective and counterproductive when they frame the practice as a ``tradition" rooted in a ``primitive" and unchanging culture.
@@
 
-In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.
-In Kenya, woman's decision on whether to cut their daughters' genitals were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.
-
 "support HCPs in the integration of FGM/C preventive interventions within the public health system, to address arguments favoring medicalization, and to use data to design appropriate strategies." \cite{KaplRiba16}
@@
 
-% attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}
 \cite{UNFPA14, UNIC16}
@@
 % attitudes change may be followed by behaviour change, but more slowly \cite{BoylMcMo02}
-% Limitations:  without incorporating national factor in this study.
 
@@
 
-% Based on our findings, are there any survey questions DHS should have included but did not?  Did our findings see something like group/community identity, womanhood \cite{Koom14}?
+% Did our findings see something like group/community identity, womanhood \cite{Koom14}?
 % \cite{Koom14}: `` an Aang Serian activist who had addressed a village meeting saying, `The world is changing and the Maasai must change with it or risk dying out.' They argued that these appeals to cultural survival were much more persuasive and meaningful to them than the `foreign' language of rights."
@@
 
-% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{I don't know if I want to cite \cite{EffeVogt15}.
-It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).
-Can heterogeneity explain the differences of beliefs in FGC benefits at individual level vs.
-at a community level?
+% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{Can heterogeneity explain the differences of beliefs in FGC benefits at individual level vs.
+at a community level?}
 
@@
 
-% Latikin 1995:  Norms o unsafe behaviours are not trivially changed trough information.
-% Beliefs are susceptible social confirmation (Damon Centola)
 % a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see \cite{BoylCorl10}, table 1)
@@
 \cite{WahlEsse18}:  from sameness to differences, a global multicultural approach especially during the international migration across the globe.
-
-%There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}…..Modernization theory proposed that, for example, education and \cite{BoylMcMo02, Youn02} can contribute to the reduction of FGC practice.
 

### 2019-04-13 community.R
rerunning all the models

@@ -19,7 +19,7 @@ attframe <- scoring(Answers, "att", yesnodk, Answers$id)
 mediaframe <- scoring(Answers, "media", rightfactor, Answers$id)
 
 attframe <- (attframe
-	%>% mutate(gender = 1-att)
+	%>% mutate(genderAware = 1-att)
 )
 
 Answers <- (Answers
@@ -30,27 +30,24 @@ Answers <- (Answers
 	%>% mutate(fgc_d = sum(!is.na(fgc))
 		, fgc_n = sum(fgc,na.rm=TRUE) - fgc
 		, group_fgc = fgc_n/(fgc_d-1)
-		, futurefgcDau_d = sum(!is.na(futurefgcDau))
-		, futurefgcDau_n = sum(futurefgcDau01, na.rm=TRUE) - futurefgcDau01
-      , group_futurefgcDau = futurefgcDau_n/(futurefgcDau_d-1)
-		, futurefgc_d = sum(!is.na(futurefgc))
-		, futurefgc_n = sum(futurefgc01, na.rm=TRUE) - futurefgc01
-      , group_futurefgc = futurefgc_n/(futurefgc_d - 1)
+		, daughterPlan_d = sum(!is.na(daughterPlan))
+		, daughterPlan_n = sum(daughterPlan01, na.rm=TRUE) - daughterPlan01
+      , group_daughterPlan = daughterPlan_n/(daughterPlan_d-1)
+		, Persist_d = sum(!is.na(Persist))
+		, Persist_n = sum(Persist01, na.rm=TRUE) - Persist01
+      , group_Persist = Persist_n/(Persist_d - 1)
 	   , bene_d = sum(!is.na(bene))
 		, bene_n = sum(bene, na.rm=TRUE) - bene
 		, group_bene = bene_n/(bene_d - 1)
-		, gender_d = sum(!is.na(gender))
-	   , gender_n = sum(gender, na.rm = TRUE) - gender
-		, group_gender = gender_n/(gender_d - 1)
+		, genderAware_d = sum(!is.na(genderAware))
+	   , genderAware_n = sum(genderAware, na.rm = TRUE) - genderAware
+		, group_genderAware = genderAware_n/(genderAware_d - 1)
 		, media_d = sum(!is.na(media))
 		, media_n = sum(media, na.rm=TRUE) - media
 	   , group_media = media_n/(media_d - 1)
[…]

### 2019-04-13 daughterPlan_clmm.R

@@ -1,0 +1,41 @@
+library(ordinal)
+library(splines)
+
+
+modAns <- model.frame(
+  daughterPlan ~ group_daughterPlan
+  + fgcstatus + group_fgc
+  + CC
+  + bene 
+  + group_bene
+  + media + group_media 
+  + genderAware + group_genderAware
+  + edu + group_edu
+  + wealth
+  + age + maritalStat + job + urRural + religion
+  + clusterId + ethni 
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
+)
+
+fit_time <- system.time(mod<- clmm(
+  daughterPlan ~ group_daughterPlan
+  + fgcstatus + group_fgc
+  + CC
+  + bene 
+  + group_bene
+  + media + group_media 
+  + genderAware + group_genderAware 
+  + edu + group_edu
+  + ns(wealth,3)
+  + ns(age,4) 
+  + maritalStat 
+  + job
+  + urRural + religion
+  + (1|clusterId) + (1|ethni)
+  , data=modAns)
+)
+
+
+print(summary(mod))
+
+# rdsave(mod, modAns, fit_time)

### 2019-04-13 fgcPersist_clmm.R

@@ -1,0 +1,40 @@
+library(ordinal)
+library(splines)
+
+
+modAns <- model.frame(
+  Persist ~ group_Persist
+  + fgcstatus + group_fgc
+  + CC
+  + bene 
+  + group_bene
+  + media + group_media 
+  + genderAware + group_genderAware
+  + edu + group_edu
+  + wealth
+  + age + maritalStat + job + urRural + religion
+  + clusterId + ethni
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
+)
+
+system.time(mod <- clmm(
+  Persist ~ group_Persist
+  + fgcstatus + group_fgc
+  + CC
+  + bene
+  + group_bene
+  + media + group_media 
+  + genderAware + group_genderAware
+  + edu + group_edu
+  + ns(wealth,3)
+  + ns(age,4) 
+  + maritalStat 
+  + job
+  + urRural + religion
+  + (1|clusterId) + (1|ethni)
+  , data=modAns)
+)
+
+print(summary(mod))
+
+# rdsave(mod, modAns)

### 2019-04-13 hybrid_clmm.R

@@ -1,0 +1,47 @@
+library(dplyr)
+library(ordinal)
+library(splines)
+
+combined_dat <- (combined_dat
+	%>% group_by(clusterId)
+	%>% mutate(group_Persist = mean(Persist01, na.rm=TRUE))
+)
+
+modAns <- model.frame(
+  daughterPlan ~ group_daughterPlan
+  + Persist + group_Persist
+  + fgcstatus + group_fgc
+  + CC
+  + bene 
+  + group_bene
+  + media + group_media 
+  + genderAware + group_genderAware 
+  + edu + group_edu
+  + wealth
+  + age + maritalStat + job + urRural + religion
+  + clusterId + ethni
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
+)
+
+system.time(mod<- clmm(
+  daughterPlan ~ group_daughterPlan
+  + Persist + group_Persist
+  + fgcstatus + group_fgc
+  + CC
+  + bene 
+  + group_bene
+  + media + group_media 
+  + genderAware + group_genderAware 
+  + edu + group_edu
+  + ns(wealth,3)
+  + ns(age,4) 
+  + maritalStat 
+  + job
+  + urRural + religion
+  + (1|clusterId) + (1|ethni)
+  , data=modAns)
+)
+
+print(summary(mod))
+
+# rdsave(mod, modAns)

### 2019-04-13 iso.R

@@ -9,8 +9,8 @@ attr(modAns,"terms") <- NULL
 
 catNames <- c("religion","urRural","job","maritalStat")
 predNames <- colnames(modAns)[2:(ncol(modAns)-2)]
-predNames <- c("CC","religion","maritalStat","age","wealth","group_wealth")
-predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)","ns(group_wealth, 3)")
+predNames <- c("CC","religion","maritalStat","age","wealth","group_wealth","futurefgc")
+predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)","ns(group_wealth, 3)","futurefgc")
 
 
 isoList <- lapply(predNames, function(n){

### 2019-04-13 recode.R

@@ -40,10 +40,10 @@ Answers <- (Answers
 		, fgc = rightfactor(fgc)
 		, edu = rightfactor(edu)
 		, edu = edu / mean(edu, na.rm = TRUE)
-		, futurefgc = contfgc(continueFgc)
-		, futurefgc01 = contfgc01(continueFgc)
-		, futurefgcDau = yesnodkFactor(daughterToFgc)
-		, futurefgcDau01 = yesnodk01(daughterToFgc) 
+		, Persist = contfgc(continueFgc)
+		, Persist01 = contfgc01(continueFgc)
+		, daughterPlan = yesnodkFactor(daughterToFgc)
+		, daughterPlan01 = yesnodk01(daughterToFgc) 
 		)
 )
 

### 2019-04-13 varlvlsum.R

@@ -1,0 +1,10 @@
+library(ordinal)
+library(splines)
+library(RVAideMemoire)
+
+
+varlvlsum <- Anova.clmm(mod)
+
+print(varlvlsum)
+
+# rdsave(mod,modAns,varlvlsum)

### 2019-04-14 community.R
Adding group_wealth back in and histograms!

@@ -48,6 +48,9 @@ Answers <- (Answers
 		, edu_d = sum(!is.na(edu))
 		, edu_n = sum(edu, na.rm=TRUE) - edu
 		, group_edu = edu_n/(edu_d - 1) 
+		, wealth_d = sum(!is.na(wealth))
+	   , wealth_n = sum(wealth, na.rm = TRUE) - wealth
+		, group_wealth = wealth_n/ (wealth_d - 1)
 	)
 )
 

### 2019-04-14 daughterPlan_clmm.R

@@ -11,7 +11,7 @@ modAns <- model.frame(
   + media + group_media 
   + genderAware + group_genderAware
   + edu + group_edu
-  + wealth
+  + wealth + group_wealth
   + age + maritalStat + job + urRural + religion
   + clusterId + ethni 
   , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
@@ -26,7 +26,7 @@ fit_time <- system.time(mod<- clmm(
   + media + group_media 
   + genderAware + group_genderAware 
   + edu + group_edu
-  + ns(wealth,3)
+  + ns(wealth,3) + ns(group_wealth,3)
   + ns(age,4) 
   + maritalStat 
   + job

### 2019-04-14 fgcPersist_clmm.R

@@ -11,7 +11,7 @@ modAns <- model.frame(
   + media + group_media 
   + genderAware + group_genderAware
   + edu + group_edu
-  + wealth
+  + wealth + group_wealth
   + age + maritalStat + job + urRural + religion
   + clusterId + ethni
   , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
@@ -26,7 +26,7 @@ system.time(mod <- clmm(
   + media + group_media 
   + genderAware + group_genderAware
   + edu + group_edu
-  + ns(wealth,3)
+  + ns(wealth,3) + ns(group_wealth)
   + ns(age,4) 
   + maritalStat 
   + job

### 2019-04-14 hybrid_clmm.R

@@ -17,7 +17,7 @@ modAns <- model.frame(
   + media + group_media 
   + genderAware + group_genderAware 
   + edu + group_edu
-  + wealth
+  + wealth + group_wealth
   + age + maritalStat + job + urRural + religion
   + clusterId + ethni
   , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
@@ -33,7 +33,7 @@ system.time(mod<- clmm(
   + media + group_media 
   + genderAware + group_genderAware 
   + edu + group_edu
-  + ns(wealth,3)
+  + ns(wealth,3) + ns(group_wealth,3)
   + ns(age,4) 
   + maritalStat 
   + job

### 2019-04-14 iso.R

@@ -9,8 +9,9 @@ attr(modAns,"terms") <- NULL
 
 catNames <- c("religion","urRural","job","maritalStat")
 predNames <- colnames(modAns)[2:(ncol(modAns)-2)]
-predNames <- c("CC","religion","maritalStat","age","wealth","group_wealth","futurefgc")
-predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)","ns(group_wealth, 3)","futurefgc")
+
+predNames <- c("CC","religion","maritalStat","age","wealth")
+predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)")
 
 
 isoList <- lapply(predNames, function(n){
@@ -28,7 +29,6 @@ print(
                varPlot(isoList[[3]] ,P=varlvlsum$`Pr(>Chisq)`[3]),
                varPlot(isoList[[4]] ,P=varlvlsum$`Pr(>Chisq)`[4]),
                varPlot(isoList[[5]] ,P=varlvlsum$`Pr(>Chisq)`[5]),
-               varPlot(isoList[[6]] ,P=varlvlsum$`Pr(>Chisq)`[6]),
 					nrow=2
 					
 					)

### 2019-04-14 wealth.R

@@ -1,0 +1,2 @@
+
+print(hist(combined_dat$wealth))

### 2019-04-15 manuscript.tex
Update manuscript.tex

@@
 Social norm is a fundamental approach in comprehending and intervening FGC practice \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.
-Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.
+Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
 FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.
-When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}.
+When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}.
 \cfonly{add \cite{Bicc15}}
@@
 
+% prevalence of FGC in those 4 nations.
+
 \subsection{Research Questions}\label{research-questions}
@@
 Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.
-This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).
+This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).
 We developed three models in this study.
@@
 
-The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.
+Our main interest in this project is to study how norms associate with behavioural intention.
+We focus on how women will likely cut their daughters or not based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g.
+women’s own FGC status).
+Therefore, our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.
 The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.
 The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.
+Beliefs of FGC benefits was estimated based on a list of questionnaires (see supp) and quantified using PCA in order to identify which benefit was mostly recognized in connection norm.
 Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs.
@@
 In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
-Cluster  was used to represent a community level of impact \cite{AligRen06, Hayf05}
+Cluster  was used as a proxy to represent a community level of impact \cite{AligRen06, Hayf05, Krav02}
 
@@
 The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
+We subtracted respondent (-1) from the cluster when testing the community effect \cfjd{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
 
@@
 
-Our findings showed that women’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.
+Our findings suggest that a daughter’s likely future of being cut or not is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others.
+Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.
 The similar results also applied to women’s view of whether FGC should be continued \cf{link}.
@@
 \cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
+
+- Beliefs of FGC benefits -
+Our PCA results show that women’s beliefs of what benefits FGC brings is not clearly identified (see figure pca) and marriageability was not a clear one (to compare with \cite{Mack?,}.
+On interpretation is that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, MackLeJe08, ShelWand11, networking, part of social groups Duncan-Shell?}
+
 — secondary analysis/socio demograhpic —
@@
 % education:  \cite{IliyAbub12, KarmKand11}
-% religion:  \cite{KarmKand11}
+% religion:  \cite{HayfTrin11, KarmKand11}
 
@@
 % little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
-% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09}.
+% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08}.
 (from the introduction.

### 2019-04-15 manuscript.tex
Autocommit (fgc)

--- 2019-04-09 manuscript.tex
@@
 \usepackage{longtable,booktabs}
+\usepackage{graphicx}
+\usepackage{grffile}
 \IfFileExists{parskip.sty}{%
@@
 
+\FloatBarrier
+
+\section{Figures}
+
+\subsection{Daughter Plan}
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/daughterPlan_effects_plot.Rout.pdf}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/daughterPlan_isoplots.Rout.pdf}
+\end{figure}
+\end{center}
+
+\newpage
+
+\subsection{FGC Persistence}
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/fgcPersist_effects_plot.Rout.pdf}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/fgcPersist_isoplots.Rout.pdf}
+\end{figure}
+\end{center}
+
+\newpage
+
+\subsection{Hybrid Model}
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/hybrid_effects_plot.Rout.pdf}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/hybrid_isoplots.Rout.pdf}
+\end{figure}
+\end{center}
+
+\FloatBarrier
+
 \bibliography{manual}

### 2019-04-15 effects_plot.R

@@ -1,7 +1,7 @@
 library(ggplot2)
 
 gg <- (ggplot(betadf
-		, aes(x=reorder(variable,beta), y=beta, ymin=lower, ymax=upper))
+		, aes(x=reorder(plotnames,beta), y=beta, ymin=lower, ymax=upper))
 	+ geom_pointrange()
 #	+ scale_colour_manual(values=c("black","gray"))
 	+ geom_hline(yintercept=0,lty=2)

### 2019-04-15 fgcPersist_clmm.R

@@ -26,7 +26,7 @@ system.time(mod <- clmm(
   + media + group_media 
   + genderAware + group_genderAware
   + edu + group_edu
-  + ns(wealth,3) + ns(group_wealth)
+  + ns(wealth,3) + ns(group_wealth, 3)
   + ns(age,4) 
   + maritalStat 
   + job

### 2019-04-15 iso.R

@@ -10,8 +10,14 @@ attr(modAns,"terms") <- NULL
 catNames <- c("religion","urRural","job","maritalStat")
 predNames <- colnames(modAns)[2:(ncol(modAns)-2)]
 
-predNames <- c("CC","religion","maritalStat","age","wealth")
-predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)")
+predNames <- c("CC","religion","maritalStat","age","wealth", "group_wealth")
+predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)","ns(group_wealth)")
+
+if(rtargetname == "hybrid_isoplots"){
+	predNames <- c(predNames, "Persist")
+	predsummary <- c(predsummary, "Persist")
+	predSummary <- NA
+}
 
 
 isoList <- lapply(predNames, function(n){
@@ -22,17 +28,21 @@ isoList <- lapply(predNames, function(n){
 #	print(varPlot(isoList[[i]]))
 #}
 
-varlvlsum <- varlvlsum[predsummary,]
+# varlvlsum <- varlvlsum[predsummary,]
 print(
-  grid.arrange(varPlot(isoList[[1]] ,P=varlvlsum$`Pr(>Chisq)`[1]),
-               varPlot(isoList[[2]] ,P=varlvlsum$`Pr(>Chisq)`[2]),
-               varPlot(isoList[[3]] ,P=varlvlsum$`Pr(>Chisq)`[3]),
-               varPlot(isoList[[4]] ,P=varlvlsum$`Pr(>Chisq)`[4]),
-               varPlot(isoList[[5]] ,P=varlvlsum$`Pr(>Chisq)`[5]),
+  grid.arrange(varPlot(isoList[[1]] ),#P=varlvlsum$`Pr(>Chisq)`[1]),
+               varPlot(isoList[[2]] ),#P=varlvlsum$`Pr(>Chisq)`[2]),
+               varPlot(isoList[[3]] ),#P=varlvlsum$`Pr(>Chisq)`[3]),
+               varPlot(isoList[[4]] ),#P=varlvlsum$`Pr(>Chisq)`[4]),
+               varPlot(isoList[[5]] ),#P=varlvlsum$`Pr(>Chisq)`[5]),
+					varPlot(isoList[[6]] ),#P=varlvlsum$`Pr(>Chisq)`[6]),
 					nrow=2
[…]

### 2019-04-15 rename_dat.R

@@ -1,0 +1,33 @@
+varnames <- c("group_Persist"
+, "fgcstatusYes"
+, "group_fgc"
+, "bene" 
+, "group_bene"
+, "media"
+, "group_media"
+, "genderAware"
+, "group_genderAware"
+, "edu"
+, "group_edu"
+, "jobYes"
+, "urRuralRural"
+, "group_daughterPlan"
+) 
+
+plotnames <- c("Persistence Norm"
+, "FGCed"
+, "FGC Norm"
+, "Benefit"
+, "Benefit Norm"
+, "Media"
+, "Media Norm"
+, "Gender Awareness"
+, "Gender Awareness Norm"
+, "Education"
+, "Education Norm"
+, "Job"
+, "Rural Residence"
+, "Daughter Plan Norm"
+)  
+
+rename_dat <- data.frame(variable=varnames, plotnames)

### 2019-04-15 single_var_effect.R

@@ -39,6 +39,7 @@ betadf <- (mm2
               , upper = upper*sd
               , inCI = between(0,lower,upper)
    )
+	%>% left_join(.,rename_dat)
 )
 
 print(betadf)

### 2019-04-15 manuscript.tex
Autocommit (fgc)
Update manuscript.tex

--- 2019-04-15 manuscript.tex
@@
 
-Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
+Only women with daughters to be considered for FGC were included in 
+ main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
@@
 Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
-\cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}
+\cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}.
+In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.
+
 \cite{PashPonn16}: Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms
@@
 \cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
+
+What does it mean that group level of daughter future as the biggest predictor compared to individual benefit and group fgc (prevalence)?
+Does it mean that fgc norm works implicitly and it might not be something behaviour women really agree with?
+Is it a social norm supported by social sanction (i.e., cutting daughter) for what reason?
+(see \cite{MackLeJe08} (p.28 which mentioned Bicchieri06)
 

### 2019-04-15 manuscript.tex
Update manuscript.tex

@@
 \usepackage{adjustbox}
+\usepackage{graphicx}
+\usepackage{grffile}
 \usepackage{amssymb,amsmath}
@@
 
+\FloatBarrier
+
+\section{Figures}
+
+\subsection{Daughter Plan}
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/daughterPlan_effects_plot.Rout.pdf}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/daughterPlan_isoplots.Rout.pdf}
+\end{figure}
+\end{center}
+
+\newpage
+
+\subsection{FGC Persistence}
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/fgcPersist_effects_plot.Rout.pdf}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/fgcPersist_isoplots.Rout.pdf}
+\end{figure}
+\end{center}
+
+\newpage
+
+\subsection{Hybrid Model}
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/hybrid_effects_plot.Rout.pdf}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7]{./git_push/hybrid_isoplots.Rout.pdf}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h!]
+\includegraphics[scale=0.7,page=2]{./git_push/hybrid_isoplots.Rout.pdf}
+\end{figure}
+\end{center}
+
+\FloatBarrier
+
 \bibliography{manual}

### 2019-04-17 iso.R
Autocommit (fgc)

@@ -11,12 +11,21 @@ catNames <- c("religion","urRural","job","maritalStat")
 predNames <- colnames(modAns)[2:(ncol(modAns)-2)]
 
 predNames <- c("CC","religion","maritalStat","age","wealth", "group_wealth")
-predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)","ns(group_wealth)")
+predsummary <- c("CC","religion","maritalStat","ns(age, 4)","ns(wealth, 3)","ns(group_wealth, 3)")
 
 if(rtargetname == "hybrid_isoplots"){
 	predNames <- c(predNames, "Persist")
 	predsummary <- c(predsummary, "Persist")
-	predSummary <- NA
+	respLab <- "Hybrid Score"
+}
+if(rtargetname == "fgcPersist_isoplots"){
+	varlvlnames <- varlvlnames[-which(varlvlnames == "group_daughterPlan")]
+	respLab <- "FGC Persistence Score"
+}
+
+if(rtargetname == "daughterPlan_isoplots"){
+	varlvlnames <- varlvlnames[-which(varlvlnames == "group_Persist")]
+	respLab <- "Daughter Plan Score"
 }
 
 
@@ -24,83 +33,55 @@ isoList <- lapply(predNames, function(n){
   ordpred(mod, n, modAns)
 })
 
-#for(i in 1:length(isoList)){
-#	print(varPlot(isoList[[i]]))
-#}
 
-# varlvlsum <- varlvlsum[predsummary,]
+varlvlsum1 <- varlvlsum[predsummary,]
 print(
-  grid.arrange(varPlot(isoList[[1]] ),#P=varlvlsum$`Pr(>Chisq)`[1]),
-               varPlot(isoList[[2]] ),#P=varlvlsum$`Pr(>Chisq)`[2]),
-               varPlot(isoList[[3]] ),#P=varlvlsum$`Pr(>Chisq)`[3]),
-               varPlot(isoList[[4]] ),#P=varlvlsum$`Pr(>Chisq)`[4]),
-               varPlot(isoList[[5]] ),#P=varlvlsum$`Pr(>Chisq)`[5]),
-					varPlot(isoList[[6]] ),#P=varlvlsum$`Pr(>Chisq)`[6]),
-					nrow=2
[…]

### 2019-04-17 rename_dat.R

@@ -1,5 +1,4 @@
-varnames <- c("group_Persist"
-, "fgcstatusYes"
+varnames <- c("fgcstatusYes"
 , "group_fgc"
 , "bene" 
 , "group_bene"
@@ -12,22 +11,40 @@ varnames <- c("group_Persist"
 , "jobYes"
 , "urRuralRural"
 , "group_daughterPlan"
+, "group_Persist"
 ) 
 
-plotnames <- c("Persistence Norm"
-, "FGCed"
-, "FGC Norm"
+varlvlnames <- c("fgcstatus" 
+, "group_fgc"
+, "bene"
+, "group_bene"
+, "media"
+, "group_media"
+, "genderAware"
+, "group_genderAware"
+, "edu"
+, "group_edu"
+, "job"
+, "urRural"
+, "group_daughterPlan"
+, "group_Persist"
+) 
+
+
+plotnames <- c("FGCed"
+, "Group FGC"
 , "Benefit"
-, "Benefit Norm"
+, "Group Benefit"
 , "Media"
-, "Media Norm"
+, "Group Media"
 , "Gender Awareness"
-, "Gender Awareness Norm"
+, "Group Gender Awareness"
 , "Education"
-, "Education Norm"
+, "Group Education"
 , "Job"
 , "Rural Residence"
-, "Daughter Plan Norm"
+, "Group Daughter Plan"
+, "Group Persistence"
 )  
 
 rename_dat <- data.frame(variable=varnames, plotnames)

### 2019-04-29 manuscript.tex
Update manuscript.tex

--- 2019-04-15 manuscript.tex
@@
 Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
+(or:  Cutting or Not:  Depending on what others will undergo the practice than what they think about the practice)
 \cfcmt{This title is a response to Efferson’s title}
@@
 
-It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.
+It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{AdnrLesc16, UNIC16}.
 Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).
-FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.
-The types of FGC vary from just a knick to a sever sewing of the genital area.
-Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.
-FGC(cirumcision) may be the best for current situation globally.)
+FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}.
 
@@
 When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}.
-\cfonly{add \cite{Bicc15}}
-
-\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, Rima08, ShelWand11, more} and other norm studies of why mother cut daughters etc}
+\cfonly{add \cite{Bicc15}}.
+Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}
 
@@
 
-We analyzed the Demographic and Health Surveys (DHS) by USAID.
+We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS).
 Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
@@
 Therefore, our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.
+In other words, only women with daughter for a consideration of fgc were included in the main and mix models, and all women were included in the persistence model.
 The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.
-The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.
-Beliefs of FGC benefits was estimated based on a list of questionnaires (see supp) and quantified using PCA in order to identify which benefit was mostly recognized in connection norm.
-Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs.
+The main predictors were woman's FGC status and beliefs of FGC benefits.
+Beliefs of FGC benefits was estimated based on a list of questionnaires (see supp) and quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice.
+Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use, gender awareness (see — for questions of gender awareness proxy) and residence (urban vs.
 rural) in addition to country.
+Media use and gender awareness were scored.
 The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).
@@
 
+\cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing? }
 \cfcmt{reference: Methods and the first paragraph of Discussion\cite{Chia14}}
@@
 
-The results of the three models are at ____.
+The results of the three models are at figure?.
 The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and FGC prevalence in a community; so as the following factors:  country, media, education, age and religion and the community levels of media, education.
@@
 
-Our findings suggest that a daughter’s likely future of being cut or not is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others.
+Our findings suggest that a daughter’s likely future of being cut or not is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others:  the norm of FGC is synergistic, based on what women think about the other women in the community will like undergo the practice than what they think about this practice.
 Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.
@@
 \cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
+-community level of fgc benefit:  can the no effect result partially due to heterogeneity?
 
@@
 \cite{Hayf05, PashPonn16} (more)
-% education:  \cite{IliyAbub12, KarmKand11}
+% education:  \cite{IliyAbub12, KarmKand11}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.
 % religion:  \cite{HayfTrin11, KarmKand11}
@@
 - inviting faced women migrated to western society to participate in fgc intervention campaign.
-For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}
+For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \ciet{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs.
+trickle-down strategy)
+- \cite{MackLeJe08}”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html).
+Both human rights deliberation and coordinated community abandonment are necessary for change.
+National programmes in Egypt and Sudan are promoting positive human rights messages and discussions at national, regional, and local levels, and are experimenting with a variety of coordinated abandonment through community dialogue efforts at the local level.
+“ (use \cite{Dagn09, MackLeJe08} for this idea)
 
@@
 - No FGC types relating to our response varialbes
+- Not controlling for daughter’s age
 
-\subsection{Conclusion}\label{Conclusion}
+\subsection{Funding}\label{Funding}
 
-==================================
+CF was funded by a grant from the James S. McDonnell foundation. JD holds a New Investigator award from the Canadian Institutes of Health Research.
+
+\subsection{Conflicts of interest}\label{Conflicts-of-Interest}
+
+The James S.
+McDonnell foundation and the Canadian Institutes of Health Research had no role in study design; collection, analysis, and interpretation of data; the writing of the manuscript; or in the decision to submit the manuscript for publication.
+The views expressed herein do not necessarily represent the views of the founding bodies.
+
+\subsection{Authors' contributions}\label{Authors'-contributions}
+
+\subsubsection{Disclaimer}\label{disclaimer}
+
+The findings and conclusions of this article are those of the authors
+and do not necessarily represent the views of the funding agency.
+
+\subsubsection{Acknowledgement}\label{Acknowledgement}
+Ben Bolker,  Marta Wayne
+
+\subsubsection{Appendix}\label{appendix-1}
+
+\bibliography{manual}
+
+\end{document}
+
+=======================================================================
+
 \cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),
@@
 % through laws \cite{AloGbad11}
+%\cite{MackLeJe08}: “transformative human rights”  it seems to assume that western human rights will work accompanied with social and moral norm in abandoning fgc (p.
+2).
+But will it?
+Norm is like fixed, nor universal….
 
@@
 
-\cite{EffeVoge15}:  Each family may have its own threshold of fgc.
-I think fgc norm has shifted from marraige advantage of social capital of social networking as proposed by Shell-Duncon and her colleagues \cite{ShelWand11}.
-To elaborate the shifted values of fgc, what it imply and how to apply the change to policy.
 \cite{CentBeck18}:  social convention and tipping point
@@
 
-\subsection{Conclusion}\label{Conclusion}
+% A Bourdieun approach:  how symbolic capital (fgc status) encounter social capital (wealth) and other forms of capital to gain community acceptance (what form of capital is this?)
 
-%"targeting women and girls is a sound investment, but outcomes are dependent on integrated approaches and the protective umbrella of policy and legislative actions" to change gender norms among women and girls \cite{KeleFran}.
-Reasons of FGC is not universal and different from community to community and from society to society; campaigns of reducing and preventing FGC need to incorporate with local history and believes.
-% call for eduction in communication of FGC:  \cite{Koom14, Meye00}}
-
-Eradication of FGC is more controversial than expected.
-FGC practice and its nature tended to be morally embraced, and deeply internalized \cite{SchuLien13}.
-Decisions on undergoing FGC was often a result of a collective practice than an individual choice \cite{Dell04, Hayf06, FreyJoh07, KandMwek09, Mack96, Mack06, ShelHern06, ShelWand11, YirgKass12}.
-Public denouncements and anti-FGC laws could push FGC into private practices \cite{GaluKama15, VanCoen17}.
-Given the regional FGC prevalence, variations among countries and the social context of FGC practices (e.g., see Burkina Faso \cite{KarmKand11} vs.
-Nigeria \cite{KandNwak09}), a ``one size fits all" strategy for the abandonment of FGMC would not be effective \cite{JohaDiop13, YodeWang13}.
+% \cite{Hayf06}:”Practical arrangements for a daughter’s circumcision are usually made by mothers (Caldwell et al.
+2000; Shell-Duncan, Obiero, and Muruli 2000; Thomas 2003).
+However, husbands and other family members, especially mothers-in-law, can exert pressure on women to make these arrangements (Shell- Duncan et al.
+2000; Yount 2002).
+If fathers, mothers, and grandparents have different opin- ions on the genital cutting, family power struc- tures will influence the relationship between individual attitudes toward circumcision and the practice of cutting.
+Thus, family dynamics are relevant to the process of gathering the critical mass of support that, according to convention theory, is necessary to end female genital cutting”
 
 ====================================
-\subsection{Funding}\label{Funding}
-
-CF was funded by a grant from the James S. McDonnell foundation. JD holds a New Investigator award from the Canadian Institutes of Health Research.
-
-\subsection{Conflicts of interest}\label{Conflicts-of-Interest}
-
-The James S.
-McDonnell foundation and the Canadian Institutes of Health Research had no role in study design; collection, analysis, and interpretation of data; the writing of the manuscript; or in the decision to submit the manuscript for publication.
-The views expressed herein do not necessarily represent the views of the founding bodies.
-
-\subsection{Authors' contributions}\label{Authors'-contributions}
-
-\subsubsection{Disclaimer}\label{disclaimer}
-
-The findings and conclusions of this article are those of the authors
-and do not necessarily represent the views of the funding agency.
-
-\subsubsection{Acknowledgement}\label{Acknowledgement}
-Ben Bolker,  Marta Wayne
-
-\subsubsection{Appendix}\label{appendix-1}
-
-\bibliography{manual}
-
-\end{document}

### 2019-04-29 manuscript.tex
Working with C; intermediate merge

--- 2019-04-15 manuscript.tex
@@
 FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.
-The types of FGC vary from just a knick to a sever sewing of the genital area.
+The types of FGC vary from just a nick to a sever sewing of the genital area.
 Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.
-FGC(cirumcision) may be the best for current situation globally.)
+FGC(cirumcision) may be the best for current situation globally.}
 
@@
 
-The results of the three models are at ____.
+The results of the three models are at ???.
 The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and FGC prevalence in a community; so as the following factors:  country, media, education, age and religion and the community levels of media, education.
@@
 \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}.
-In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.
+In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.}
 
@@
 Our PCA results show that women’s beliefs of what benefits FGC brings is not clearly identified (see figure pca) and marriageability was not a clear one (to compare with \cite{Mack?,}.
-On interpretation is that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, MackLeJe08, ShelWand11, networking, part of social groups Duncan-Shell?}
+On interpretation is that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cfonly{Cite: EffeVogt15, MackLeJe08, ShelWand11, networking, part of social groups Duncan-Shell?}
 
@@
 — Suggestions —
-- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
+- empowering community, engaging community leaders and other strategies \cite{BergDeni13b}
 - MC vs.

### 2019-04-29 manuscript.tex

--- 2019-04-29 manuscript.tex
@@
 
-\bibliography{manual}
+\bibliography{refs}
 
@@
 
-Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShell18} vs.
+Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShel18} vs.
 no-tolerance, fgc vs.

### 2019-05-06 recode.R
renaming for table

@@ -38,12 +38,15 @@ Answers <- (Answers
     , wealth = wealth/100000
 		, fgcstatus = fgc
 		, fgc = rightfactor(fgc)
+		, Education = edu
 		, edu = rightfactor(edu)
 		, edu = edu / mean(edu, na.rm = TRUE)
 		, Persist = contfgc(continueFgc)
 		, Persist01 = contfgc01(continueFgc)
 		, daughterPlan = yesnodkFactor(daughterToFgc)
-		, daughterPlan01 = yesnodk01(daughterToFgc) 
+		, daughterPlan01 = yesnodk01(daughterToFgc)
+		, Religion = religion
+		, MaritalStatus = maritalStat
 		)
 )
 

### 2019-05-06 table_funs.R

@@ -1,0 +1,49 @@
+library(dplyr)
+dfill <- function(dat,x){
+  return(dat
+         %>% filter(Category==x)
+         %>% filter(Category2!="Total")
+         %>% select(-c(Total,Category))
+  )
+}
+
+latex <- function(x,spaces=FALSE){
+  n <- nrow(x)
+  string <- knitr:::kable(x,format="latex",digits=3,align="l",col.names = NULL,booktabs=FALSE)
+  tab <- unlist(strsplit(string[1],"\n"))
+  if(spaces){
+    return(paste("\\hspace{0.2in}",tab[c(2+2*1:n)]))
+  }
+  return(tab[c(2+2*1:n,2+2*n+1)])
+}
+
+header <- c("
+  \\documentclass{article}
+  \\usepackage[top=0.01in,left=1in]{geometry}
+  \\usepackage[T1]{fontenc}
+            
+  \\begin{document}
+  \\begin{table}{}
+  \\scriptsize{
+  \\begin{tabular}{|l|rrrrrrrrrr|r|}
+  \\hline
+  \\bf{Country} & KE & LS & MW & MZ & NM & RW & TZ & UG & ZM & ZW & Total \\\\
+  \\hline
+")
+
+footer <- c("
+  \\hline
+  \\end{tabular}
+  }
+  \\end{table}
+  \\end{document}
+")
+
+space <- c("
+  \\hspace{0.2in}
+")
+hline <- c("
+  \\hline
+")  
+
+spaces <- c("&&&&&&&&&&&\\\\")

### 2019-05-06 tables.R

@@ -1,0 +1,99 @@
+library(ordinal)
+library(splines)
+library(dplyr)
+
+# Answers <- subset(Answers, CC != "LS")
+# Answers (Answers
+#   %>% select(-c(Age,baseAge,interviewYear, oldMC, MCcat,))
+# )
+# Answers <- Answers[complete.cases(Answers),]
+Ans <- model.frame(
+  daughterPlan ~ Persist + fgcstatus + CC 
+  + age + Residence + Religion + MaritalStatus + Job 
+  + mediaNpmg + mediaRadio + mediaTv
+  + attNoTell + attNegKids + attArgue + attRefuseSex + attBurnFood
+  + heardFGC + heardGF 
+  + beneHygiene + beneAcceptance + beneMarriage + benePreventPreSex
+  + benePleasureM beneReligion + beneRedPromis + beneRedSTD + beneOther
+  + daughterPlan  + daughterFgced 
+  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
+)
+
+CCtable <- function(x){
+  return(table(Ans[,x],Ans[,"CC"]))
+}
+
+predictors <- c("age","Residence","Religion","Education","Job","MaritalStatus","maxLastcondom"
+                   ,"ExtraPartnerYear", "MC", "maxLastPartner", "MCprovider2","knowledgeCondomsProtect"
+                   ,"knowledgeLessPartnerProtect", "knowledgeHealthyGetAids","mediaNpMg"
+                   ,"mediaRadio","mediaTv")
+
+
+tablist <- lapply(predictors,CCtable)
+
+print(head(tablist[[1]]))
+
+quit()
+
+combdf <- function(pred,lldf){
+  tempdf <- as.data.frame.matrix(lldf)
+  df <- data.frame(Category=pred,Sub_Category=rownames(tempdf),tempdf)
+  return(df)
+}
+
+ddtab <- data.frame()
+for(i in seq_along(predictors)){
+  ddtab <- rbind(ddtab,combdf(predictors[i],tablist[[i]]))
+}
+
+row.names(ddtab) <- NULL
+
+ddtab2 <- (ddtab 
+  %>% mutate(Total = KE+LS+MW+MZ+NM+RW+TZ+UG+ZM+ZW)
+)
+
+
+ddtabpercent <- (ddtab2
[…]

### 2019-05-06 tabletex.R

@@ -1,0 +1,52 @@
+library(dplyr)
+
+
+Country <- (ddtab4 
+  %>% filter(Category2=="Total") 
+  %>% filter(row_number()==1)
+  %>% select(-c(Category,Category2,totalper))
+)
+
+cat("\\bf{Survey Year} & 2014 & 2014 & 2015-16 & 2011 & 2013 & 2014-15 & 2009-10 & 2011 & 2013-14 & 2015 & \\\\"
+  , "\\bf{Sample Size} &" , latex(Country) ## sample size 
+  , "\\bf{Category (in percentage)}", spaces
+  , hline
+  , "\\bf{Age Group}" , spaces
+  , latex(dfill(ddtab4,"ageGroup"))
+  , "\\bf{Residence}" , spaces
+  , latex(dfill(ddtab4,"Residence"))
+  , "\\bf{Education}" , spaces
+  , latex(dfill(ddtab4,"Education"))
+  , "\\bf{Religion}" , spaces 
+  , latex(dfill(ddtab4,"Religion"))
+  , "\\bf{Marital Status}" , spaces
+  , latex(dfill(ddtab4,"MaritalStatus"))
+  , "\\bf{Job}" , spaces
+  , latex(dfill(ddtab4,"Job"))
+  , "\\bf{Condom Usage}" , spaces
+  , latex(dfill(ddtab4,"maxLastcondom"))
+  , "\\bf{Non-cohabiting Partners}" , spaces
+  , latex(dfill(ddtab4,"ExtraPartnerYear"))
+  , "\\bf{Circumcised}" , spaces
+  , latex(dfill(ddtab4,"MC"))
+  , "\\bf{MC Provider}" , spaces
+  , latex(dfill(ddtab4,"MCprovider2"))
+  , "\\bf{The Riskiest Sexual Partner}" , spaces
+  , latex(dfill(ddtab4,"maxLastPartner"))
+  , "\\bf{HIV Knowledge}" , spaces
+  , space , "\\bf{Condoms Protect}" , spaces
+  , latex(dfill(ddtab4,"knowledgeCondomsProtect"),space=TRUE)
+  , space , "\\bf{Less Partner Protect}" , spaces
+  , latex(dfill(ddtab4,"knowledgeLessPartnerProtect"),space=TRUE)
+  , space , "\\bf{Healthy People Get Aids}" , spaces
[…]

### 2019-05-06 recode.R
Autocommit (fgc)

@@ -47,6 +47,8 @@ Answers <- (Answers
 		, daughterPlan01 = yesnodk01(daughterToFgc)
 		, Religion = religion
 		, MaritalStatus = maritalStat
+		, Residence = urRural
+		, Job = job
 		)
 )
 

### 2019-05-06 tables.R

@@ -7,39 +7,49 @@ library(dplyr)
 #   %>% select(-c(Age,baseAge,interviewYear, oldMC, MCcat,))
 # )
 # Answers <- Answers[complete.cases(Answers),]
-Ans <- model.frame(
-  daughterPlan ~ Persist + fgcstatus + CC 
-  + age + Residence + Religion + MaritalStatus + Job 
-  + mediaNpmg + mediaRadio + mediaTv
-  + attNoTell + attNegKids + attArgue + attRefuseSex + attBurnFood
-  + heardFGC + heardGF 
-  + beneHygiene + beneAcceptance + beneMarriage + benePreventPreSex
-  + benePleasureM beneReligion + beneRedPromis + beneRedSTD + beneOther
-  + daughterPlan  + daughterFgced 
-  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
+Ans <- (combined_dat
+	%>% select(Persist, fgcstatus, CC 
+  , age , Residence , Religion , MaritalStatus , Job , Education
+  , mediaNpmg , mediaRadio , mediaTv
+  , attNoTell , attNegKids , attArgue , attRefuseSex , attBurnFood
+  , heardFGC
+  , beneHygiene , beneAcceptance , beneMarriage , benePreventPreSex
+  , benePleasureM , beneReligion , beneRedPromis , beneRedSTD , beneOther
+  , daughterPlan  , daughterFgced 
+	)
+	%>% mutate(AgeGroup = ifelse(between(age,14,19),"14-19"
+		, ifelse(between(age,20,24),"20-24"
+		, ifelse(between(age,25,29),"25-29"
+		, ifelse(between(age,30,34),"30-34"
+		, ifelse(between(age,35,39),"35-39"
+		, ifelse(between(age,40,44),"40-44"
+		, ifelse(between(age,45,49),"45-49",NA)
+		))))))
+		)
 )
 
 CCtable <- function(x){
   return(table(Ans[,x],Ans[,"CC"]))
 }
 
-predictors <- c("age","Residence","Religion","Education","Job","MaritalStatus","maxLastcondom"
-                   ,"ExtraPartnerYear", "MC", "maxLastPartner", "MCprovider2","knowledgeCondomsProtect"
[…]

### 2019-05-06 fgc_table.tex
Autocommit (fgc)

\documentclass[hidelinks,10pt,letterpaper]{article}
\usepackage[top=0.75in,footskip=0.75in,bottom=0.75in]{geometry}
\usepackage{float}
\usepackage{changepage}
\usepackage[utf8]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{amsmath,amssymb}
\usepackage{cite}
\usepackage{nameref,hyperref}
\usepackage[right]{lineno}
\usepackage{microtype}
% \DisableLigatures[f]{encoding = *, family = * }
% \raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
%% \textheight 8.75in
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother
\date{}
\usepackage{lastpage,fancyhdr,graphicx}
\pagestyle{myheadings}
\pagestyle{fancy}

% \fancyhf{}
% \setlength{\headheight}{27.023pt}
% \rfoot{\thepage/\pageref{LastPage}}
% \renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
% \fancyheadoffset[L]{2.25in}
% \fancyfootoffset[L]{2.25in}

\usepackage{setspace}

\begin{document}
% \vspace*{0.35in}
\section*{Supplementary Table: Sample Characteristics}

\setcounter{table}{0}
\renewcommand\thetable{\Alph{table}}

%% small blurb here

\begin{table}[H]

\caption{FGC table}
\scalebox{0.9}{
\tiny{
\begin{tabular}{|l|rrrr|r|}
\hline
\bf{Country} & KE & ML & NG & SL & Total \\
\hline
\input{table_output.tex}
\hline
\end{tabular}
}
}
\\
\\
\textrm{The following samples were excluded from this study: never heard of AIDS, never had sexual intercourse prior to the surveys, unaware of their circumcision status, or had NA answers to any of the variables. Condom use referred to whether a condom was used with the riskiest sexual partner of the most recent three sexual conducts. A riskiest sexual partner referred to the partner with the highest sexual risk score among the sexual partners a respondent reported to have sex with during the most recent three sexual conducts.
Media use referred to frequency samples reported on time spending on newspaper, radio and television.
HIV knowledge referred to questions of ``Reduce risk of getting HIV: always use condoms during sex," ``Reduce chance of AIDS: have one sex partner with no other partner," and ``A healthy looking person can have HIV."}
\label{fgc_table}
\end{table}

\end{document}

### 2019-05-06 table_funs.R

@@ -46,4 +46,4 @@ hline <- c("
   \\hline
 ")  
 
-spaces <- c("&&&&&&&&&&&\\\\")
+spaces <- c("&&&&&\\\\")

### 2019-05-06 tables.R

@@ -101,6 +101,7 @@ tabtotal <- (ddtab3
 
 ddtab4 <- ddtab3 %>% mutate(totalper = round(Total*100/tabtotal[[1]],1))
 
-print(ddtab4)
+print(ddtab4,n=100)
+print(summary(ddtab4))
 
 # print(ddtab4[,10:13])

### 2019-05-06 tabletex.R

@@ -7,12 +7,15 @@ Country <- (ddtab4
   %>% select(-c(Category,Category2,totalper))
 )
 
-cat("\\bf{Survey Year} & 2014 & 2014 & 2015-16 & 2011 & 2013 & 2014-15 & 2009-10 & 2011 & 2013-14 & 2015 & \\\\"
+print(latex(Country))
+
+
+cat("\\bf{Survey Year} & 2015 & 2015 & 2015 & 2015 &\\\\"
   , "\\bf{Sample Size} &" , latex(Country) ## sample size 
   , "\\bf{Category (in percentage)}", spaces
   , hline
   , "\\bf{Age Group}" , spaces
-  , latex(dfill(ddtab4,"ageGroup"))
+  , latex(dfill(ddtab4,"AgeGroup"))
   , "\\bf{Residence}" , spaces
   , latex(dfill(ddtab4,"Residence"))
   , "\\bf{Education}" , spaces
@@ -23,30 +26,15 @@ cat("\\bf{Survey Year} & 2014 & 2014 & 2015-16 & 2011 & 2013 & 2014-15 & 2009-10
   , latex(dfill(ddtab4,"MaritalStatus"))
   , "\\bf{Job}" , spaces
   , latex(dfill(ddtab4,"Job"))
-  , "\\bf{Condom Usage}" , spaces
-  , latex(dfill(ddtab4,"maxLastcondom"))
-  , "\\bf{Non-cohabiting Partners}" , spaces
-  , latex(dfill(ddtab4,"ExtraPartnerYear"))
-  , "\\bf{Circumcised}" , spaces
-  , latex(dfill(ddtab4,"MC"))
-  , "\\bf{MC Provider}" , spaces
-  , latex(dfill(ddtab4,"MCprovider2"))
-  , "\\bf{The Riskiest Sexual Partner}" , spaces
-  , latex(dfill(ddtab4,"maxLastPartner"))
-  , "\\bf{HIV Knowledge}" , spaces
-  , space , "\\bf{Condoms Protect}" , spaces
-  , latex(dfill(ddtab4,"knowledgeCondomsProtect"),space=TRUE)
-  , space , "\\bf{Less Partner Protect}" , spaces
-  , latex(dfill(ddtab4,"knowledgeLessPartnerProtect"),space=TRUE)
-  , space , "\\bf{Healthy People Get Aids}" , spaces
[…]

### 2019-05-06 fgc_table.tex
Autocommit (fgc)

@@
 \\
-\textrm{The following samples were excluded from this study: never heard of AIDS, never had sexual intercourse prior to the surveys, unaware of their circumcision status, or had NA answers to any of the variables.
-Condom use referred to whether a condom was used with the riskiest sexual partner of the most recent three sexual conducts.
-A riskiest sexual partner referred to the partner with the highest sexual risk score among the sexual partners a respondent reported to have sex with during the most recent three sexual conducts.
-Media use referred to frequency samples reported on time spending on newspaper, radio and television.
-HIV knowledge referred to questions of ``Reduce risk of getting HIV: always use condoms during sex," ``Reduce chance of AIDS: have one sex partner with no other partner," and ``A healthy looking person can have HIV."}
+\textrm{Feed me}
 \label{fgc_table}

### 2019-05-06 tabletex.R

@@ -26,6 +26,16 @@ cat("\\bf{Survey Year} & 2015 & 2015 & 2015 & 2015 &\\\\"
   , latex(dfill(ddtab4,"MaritalStatus"))
   , "\\bf{Job}" , spaces
   , latex(dfill(ddtab4,"Job"))
+  , "\\bf{Heard FGC}" , spaces
+  , latex(dfill(ddtab4,"heardFGC"))
+  , "\\bf{FGC Status}" , spaces
+  , latex(dfill(ddtab4,"fgcstatus"))
+  , "\\bf{Daughter Plan}" , spaces
+  , latex(dfill(ddtab4,"daughterPlan"))
+  , "\\bf{Daughter FGCed}" , spaces
+  , latex(dfill(ddtab4,"daughterFgced"))
+  , "\\bf{Persist}" , spaces
+  , latex(dfill(ddtab4,"Persist"))
   , "\\bf{Media}" , spaces
   , space , "\\bf{Newspaper and Magazines}" , spaces
   , latex(dfill(ddtab4,"mediaNpmg"),space=TRUE)
@@ -36,5 +46,32 @@ cat("\\bf{Survey Year} & 2015 & 2015 & 2015 & 2015 &\\\\"
   , "\\bf{Benefit}", spaces
   , space , "\\bf{Hygiene}", spaces
   , latex(dfill(ddtab4,"beneHygiene"),space=TRUE)
+  , space , "\\bf{Acceptance}", spaces
+  , latex(dfill(ddtab4,"beneAcceptance"),space=TRUE)
+  , space , "\\bf{Marriage}", spaces
+  , latex(dfill(ddtab4,"beneMarriage"),space=TRUE)
+  , space , "\\bf{Prevent Pre-Sex}", spaces
+  , latex(dfill(ddtab4,"benePreventPreSex"),space=TRUE)
+  , space , "\\bf{Religion}", spaces
+  , latex(dfill(ddtab4,"beneReligion"),space=TRUE)
+  , space , "\\bf{Reduce STD}", spaces
+  , latex(dfill(ddtab4,"beneRedSTD"),space=TRUE)
+  , space , "\\bf{Pleasure}", spaces
+  , latex(dfill(ddtab4,"benePleasureM"),space=TRUE)
+  , space , "\\bf{Reduce Promiscuous}", spaces
+  , latex(dfill(ddtab4,"beneRedPromis"),space=TRUE)
[…]

### 2019-06-05 manuscript.tex
Update manuscript.tex

@@
 Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).
-FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}.
+FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01} and Tostan (https://www.tostan.org/programs/community-empowerment-program/).
 
-The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.
-The progress is hindered due to the complicated history of the very practice \cite{Cami16}.
-The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.
+The progress is hindered due to the complicated history of the very practice \cite{BergDeni12, Cami16}.
+The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+(and BoylMcMo02)
 
-Social norm is a fundamental approach in comprehending and intervening FGC practice \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.
-Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
+Social norm is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} and analyzed \cite{DuncWand11, EffeVogt15, Hayf05,,, Youn02, }.
+For example, convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
 FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.
-When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}.
+When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}.
 \cfonly{add \cite{Bicc15}}.
@@
 Although convention theory was well deliberated and applied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges \cite{EffeVogt15} and multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13}.
+
+% norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}
 
@@
 This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).
+The main norm theory we tested in this paper was that women’s intention on genital cutting of their daughters was dependent on other women’s intention on cutting their daughters in their community.
 We developed three models in this study.
-The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
-Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of cutting daughters to understand how such positions change the main model.
+The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
+Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.
 
@@
 Only women with daughters to be considered for FGC were included in 
- main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
+ main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples.
+We included all the women with daughters who had not genital cutting because those women presented an attitude of whether to genitally cut their daughter and represented part of the community norm in the first two models.
+As a result,  there were xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
@@
 Our main interest in this project is to study how norms associate with behavioural intention.
-We focus on how women will likely cut their daughters or not based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g.
+We focus on whether women will likely genitally cut their daughters based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g.
 women’s own FGC status).
-Therefore, our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.
+Therefore, our main response variables were woman's behavioural intention to cut their daughters genital in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.
 In other words, only women with daughter for a consideration of fgc were included in the main and mix models, and all women were included in the persistence model.
@@
 We subtracted respondent (-1) from the cluster when testing the community effect \cfjd{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
+\cfcmt{Do we explain conveyance of uncertainty and data sampling?}
 
@@
 
-Our findings suggest that a daughter’s likely future of being cut or not is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others:  the norm of FGC is synergistic, based on what women think about the other women in the community will like undergo the practice than what they think about this practice.
+Our findings suggest that the likelihood of whether a mother will have their daughters genital cut is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others:  the norm of FGC is synergistic, based on what women think about the other women in the community will like undergo the practice than what they think about this practice.
 Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.
@@
 
+The findings support the idea that the practice of FGC is supported by social values and beliefs within the community \cite{BiccMari15}
+
 — Norm —
@@
 - conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
-- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}.
-“alternative convention/peer convention\cite{ShelWand11}
+- \cite{PashPonn16}:  “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." also their findings showed that beliefs of fgc benits was the strongest predictor of mother’ intention of cutting daughters.
+\cite{ShelWand11}:“alternative convention/peer convention.
+Subjective norm referred to “perceived social pressure to perform or not to perform the behavior” or “socially expected mode of conduct”  \cite{Ajze91}.
+
+- descriptive norm:  what others do. In our case, is it fgc prevalence in a community?
+
  \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
@@
 
-- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02}. 
- \cit{Hayf05}  Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status
-\cite{KandNwak09,VanMeek15} proposing various factors impacting FGC practices, such as women's education
+- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02}. 
+ \cit{Hayf05 SipsChen12}  Wealth.  \cite{Hayf05}: Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status
 
-\cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
+% age\cite{PashPonn16, SipsChen12}, \cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
+
 \cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
 \cite{Hayf05, PashPonn16} (more)
-% education:  \cite{IliyAbub12, KarmKand11}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.
+
+% education:  \cite{DalaLawo10, IliyAbub12, KandNwak09, KarmKand11, PashPonn16, VanMeek1}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.
+
 % religion:  \cite{HayfTrin11, KarmKand11}
 
+% media:  \cite{DalaLawo10}
+
+% Refer the findings to \cite{BiccMari15} on fgc dynamics/freedom/fgc prevalence trend/econcomic development etc in the 4 nations. (e.g., table 8)
 — by nations and laws in those nations—
@@
 — Suggestions —
+
+Changing social norm is a key step to changing behaviour  \cie{Bicc10}.
+Changes of social norms in public health beavhiors may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.
+An alternative to fgc (a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour.
+(using Tostan as an example) (also see \cite{Youn15}.
+Promising change are observed in changing norms \cite{EvanSnid19} (and Tostan).
+
 - empowering community, engaging community leaders and other strategies \cite{BergDeni13b}
@@
 “ (use \cite{Dagn09, MackLeJe08} for this idea)
+- a bottom-up intervention aimed at changing social expectation \cite{BiccMari15}
+- Instead of focusing on improving knowledge and changing attitudes, we need to be more cautious about implementation of social norm interventions and infuse intervention in a relational dimension and a dynamic framework \cite{CislHeis18a, CislHeis18b, McCh15}.
+Empowering local community and opinion leaders in implementing “organized diffusion” \cite{MackLeJe08}has proven cost-effective \cite{CislDenn19}.
+(and Boston?)
 
@@
 
+%  while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.
 \cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),
 
---- attitudes vs. norm (beliefs) vs. (behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
+--- attitudes vs.
+norm (beliefs) vs.
+(behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}  Attitude is “personal evaluation of a behaviour” \cite{Ajze91}
 \cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intention:  attitude, norm and perceived behavioroal control.
@@
 
-%\cfcmt{Bicchieri's norm theory \cite{Bicc06}:
+%\cfcmt{Bicchieri's norm theory \cite{Bicc06, BiccMari15}:
 behaviour:  What the responder do 
-personal normative behaviour:  What the responder believes she should do
-empirical expectation:  What the responder believes others do
-normative expectation: What the responder believes others think she should do
+personal normative behaviour:  What the responder believes she should do/Personal normative beliefs are individual’s beliefs about the value of a practice. 
+empirical expectation:  What the responder believes others do/What others do/second-order beliefs about the normative beliefs of other people (Bicchieri, 2006) 
+normative expectation: What the responder believes others think she should do/what other people believe one should do
+“individuals may actively dislike the behavior imposed by the norm, but still obey it if their social expectations point in that direction. “
 

### 2019-06-06 manuscript.tex
Update manuscript.tex

@@
 
-Social norm is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} and analyzed \cite{DuncWand11, EffeVogt15, Hayf05,,, Youn02, }.
+Social norm is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} and the FGC practice is often analyzed using social norm constructs \cite{DuncWand11, EffeVogt15, Hayf05, Youn02, } (more cite{BoylCorl010, Drol11, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm)).
 For example, convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
@@
 
-Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.
-This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).
+Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} (and Bicc etc, more).
+This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices (i.e., cutting daughters’s genitals).
 The main norm theory we tested in this paper was that women’s intention on genital cutting of their daughters was dependent on other women’s intention on cutting their daughters in their community.
@@
 
-Only women with daughters to be considered for FGC were included in 
- main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples.
-We included all the women with daughters who had not genital cutting because those women presented an attitude of whether to genitally cut their daughter and represented part of the community norm in the first two models.
+Only women with daughters to be considered for FGC were included in main model (the daughter model) and the mixed structure (future-daughter) model, while the future model included all the women in the samples; we included only women who had daughters yet to be considered FGC in the models to analyze intention of fgc behaviour.
+All woman were included in the future model.
 As a result,  there were xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
@@
 
-The findings support the idea that the practice of FGC is supported by social values and beliefs within the community \cite{BiccMari15}
+The findings support the idea that the practice of FGC is supported by social values and beliefs within the community \cite{BiccMari15}.
+FGC prevalence is a strong predictor of all models and it shows that norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.
 
@@
 Promising change are observed in changing norms \cite{EvanSnid19} (and Tostan).
+How to foresee a community conducive to certainty for girls without fgc?
 

### 2019-06-19 manuscript.tex
Update manuscript.tex

@@
 
-Social norm is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} and the FGC practice is often analyzed using social norm constructs \cite{DuncWand11, EffeVogt15, Hayf05, Youn02, } (more cite{BoylCorl010, Drol11, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm)).
+Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15}, is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13}.
+FGC practice is often analyzed using social norm constructs \cite{DuncWand11, EffeVogt15, Hayf05, Youn02, } (more cite{BoylCorl010, Drol11, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm)).
 For example, convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
@@
 
-Our main interest in this project is to study how norms associate with behavioural intention.
+Our main interest in this study is to analyze how norms associate with behavioural intention.
 We focus on whether women will likely genitally cut their daughters based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g.

### 2019-06-27 manuscript.tex
Update manuscript.tex

@@
 
+FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15} or social pressure \cite{}.
 — Suggestions —
@@
 
-- empowering community, engaging community leaders and other strategies \cite{BergDeni13b}
+Unlike foot binding which was displayed in public, the outcome of FGC can only be identified through private channels (e.g., a tight group community or personnel communications).
+The intervention of FGC via public rejection or condemnation is more questionable (or challenging, especially when if marriage is no longer a main reason for FGC).
+While the comparison of foot binding had a public norm effect, the difference between FGC and no FGC is more personal.
+A bottom-up campaign empowering local community and engaging women in change of the practice is essential \cite{BergDeni13b} and messages tailoring differences of normative beliefs in different groups should also be considered.
+The practice of FGC is likely to be revised due to types of FGC, but how to eradicate it if it evolves to just a “nick” compared to the norm of male circumcision?
+
 - MC vs.

### 2019-07-02 manuscript.tex
Update manuscript.tex

@@
 
-It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{AdnrLesc16, UNIC16}.
-Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).
-FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01} and Tostan (https://www.tostan.org/programs/community-empowerment-program/).
+It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15, with another 15 millions girls at risk by 2020  \cite{AdnrLesc16, UNIC16}.
+Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade if the trends continue \cite{KhosBane17, UNIC16}.
+FGC is also known as female genital mutilation and female circumcision.
+As adapted by Tostan \cite{Tost15}, cutting is preferred over circumcision without diminishing or excusing the negative impact of the practice because it implies a degree of self-awareness and is considered less judgmental  \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
+\cfonly{less cites}
 

### 2019-07-04 manuscript.tex
Update manuscript.tex

@@
 
-The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.
+The commonly shared position for the practice of FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.
 The progress is hindered due to the complicated history of the very practice \cite{BergDeni12, Cami16}.
-The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
-(and BoylMcMo02)
+The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, and by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+\cfonly{too many cites}.
+Understanding values and norms attached to FGC practice is essential to comprehend the persistence of FGC practice \cite{}.
+Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in comprehending,  intervening or eradicating the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} \cfonly{more cites}.
 
-Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15}, is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13}.
-FGC practice is often analyzed using social norm constructs \cite{DuncWand11, EffeVogt15, Hayf05, Youn02, } (more cite{BoylCorl010, Drol11, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm)).
-For example, convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
-FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.
-When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}.
+Social norm is often used to understand behavioural pattern of FGC \cfonly{more cite{BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17, Youn02} (to confirm)}.
+Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.
+Convention theory, a widely inferred approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
+FGC is also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.
+When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}.
 \cfonly{add \cite{Bicc15}}.
-Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}
 
-Although convention theory was well deliberated and applied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges \cite{EffeVogt15} and multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13}.
+Although convention theory was well deliberated and applied and showed a larger effect on FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges and no coordination game was observed in marital expectation \cite{EffeVogt15}.
+Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?} as well as that it can be a social bond for women \cite{Mack00, DuncWand11}.
+Multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}
 
-% norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}
-
-% prevalence of FGC in those 4 nations.
+In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitude on the practice.
+Besides social norms of FGC, women’s gender values and their social environment were also incorporated.
 
@@
 
-Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} (and Bicc etc, more).
-This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices (i.e., cutting daughters’s genitals).
-The main norm theory we tested in this paper was that women’s intention on genital cutting of their daughters was dependent on other women’s intention on cutting their daughters in their community.
+This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices.
+Our main interest in this study is to analyze how norms associate with behavioural intention.
+We focus on whether women will likely genitally cut their daughters based on their current intention and that provides a relatively more detailed result on how FGC norms interacts FGC practice than using than what had already happened (e.g.
+women’s own FGC status).
+The main norm theory tested in this paper was that women’s intention on practicing FGC on their daughters was dependent on other women’s intention on cutting their daughters within their community.
 We developed three models in this study.
-The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
-Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.
+The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in order to understand if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
+Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “daugher_ persistence” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.
 
@@
 Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 1/09/19).
+We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication \cf{checked in 1/09/19}.
 
-Only women with daughters to be considered for FGC were included in main model (the daughter model) and the mixed structure (future-daughter) model, while the future model included all the women in the samples; we included only women who had daughters yet to be considered FGC in the models to analyze intention of fgc behaviour.
-All woman were included in the future model.
-As a result,  there were xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
+Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daugher_ persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx and xxx  respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
@@
 \subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
+
 \cfonly{\cite{Rima08}}*
 
-Our main interest in this study is to analyze how norms associate with behavioural intention.
-We focus on whether women will likely genitally cut their daughters based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g.
-women’s own FGC status).
-Therefore, our main response variables were woman's behavioural intention to cut their daughters genital in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.
-In other words, only women with daughter for a consideration of fgc were included in the main and mix models, and all women were included in the persistence model.
-The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.
-The main predictors were woman's FGC status and beliefs of FGC benefits.
-Beliefs of FGC benefits was estimated based on a list of questionnaires (see supp) and quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice.
-Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use, gender awareness (see — for questions of gender awareness proxy) and residence (urban vs.
+Our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.
+The predictors selected based on literature (e.g., aforementioned above) were woman's FGC status and beliefs of FGC benefits (see supp for a list of questionnaire of FGC benefits).
+The beliefs of FGC benefits were quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice.
+We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}.
+Other socio demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs.
 rural) in addition to country.
@@
 
-In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
+In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?}.
 Cluster  was used as a proxy to represent a community level of impact \cite{AligRen06, Hayf05, Krav02}
@@
 Should we drop STD since 3 out of 4 missed this variable?}
+\cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
 
@@
 The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
-We subtracted respondent (-1) from the cluster when testing the community effect \cfjd{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
+We subtracted respondent (-1) from the cluster when testing the community effect \cfjdml{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
+
 \cfcmt{Do we explain conveyance of uncertainty and data sampling?}
@@
 \cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing? }
-\cfcmt{reference: Methods and the first paragraph of Discussion\cite{Chia14}}
+
+\cfonly{reference: Methods and the first paragraph of Discussion\cite{Chia14}}
 
@@
 Codes are be available upon request.
+
+=====stop reading===
 

### 2019-07-05 manuscript.tex
Update manuscript.tex

@@
 
-Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daugher_ persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx and xxx  respectively.
+Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daugher_ persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7253 respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
@@
 
-=====stop reading===
-
 \subsection{Results}\label{results-1}
 
-Baseline socio-demographic and sample characteristics are shown in xxx.
-The prevalence of FGC are \%, \%, \% and \% in Kenya, Mali, Nigeria and Sierra Leon accordingly, and \%, \%, \% and \%  of the samples thought FGC should continue as well.
+\cf{We need to show both isoplots and effect plots because some binary variables are not on the isoplots.}
+
+Baseline socio-demographic and sample characteristics are shown in figure x.
+The prevalence of FGC are 31.8\%, 88.6\%, 45.9\% and 91.0\%, and 15.5\%, 73.9\%, 20.6\% and 65.5\% of the samples thought FGC should be continued in Kenya, Mali, Nigeria and Sierra Leon accordingly.
 
 The results of the three models are at figure?.
-The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and FGC prevalence in a community; so as the following factors:  country, media, education, age and religion and the community levels of media, education.
-We did not find clear association of the community level of beliefs of fgc benefits and the three responses.
+The findings showed that women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters, attitudes on whether FGC should be continued); so as the following factors but in negative association:  country, media, education, age and religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret}.
+The association of gender awareness with the two responses was not clear in our findings both at a population \cf{or individual} and a community level.
+
+===== stop reading =======
 
@@
 Tables and figures to be included:
-- table of basic sociodemographic results
-- 3 figures of the results of the 3 models
 - a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)

### 2019-07-05 manuscript.tex
Comments on Main part of intro

@@
 
-It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15, with another 15 millions girls at risk by 2020  \cite{AdnrLesc16, UNIC16}.
-Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade if the trends continue \cite{KhosBane17, UNIC16}.
-FGC is also known as female genital mutilation and female circumcision.
-As adapted by Tostan \cite{Tost15}, cutting is preferred over circumcision without diminishing or excusing the negative impact of the practice because it implies a degree of self-awareness and is considered less judgmental  \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
+\jdcmt{I've been talking with Mike and Katie about writing papers that are easy to read. You should focus on paragraph structure, particularly the first s. of each \P. I will send you a link.}
+
+\jdcmt{This is a run-on sentence It is estimated,} based on a UNICEF global database \jdcmt{cite the database right here?} including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East.
+\jdcmt{Can this be a new sentence?
+are the 15 million also girls below 15?
+If so, link directly and if not, clarify} and 44 million of them are girls below age 15, with another 15 million girls at risk by 2020  \cite{AdnrLesc16, UNIC16}.
+Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC  is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.
+\jdcmt{Need to think about how much to about terminology and how to say it} FGC is also known as female genital mutilation and female circumcision.
+As adapted by Tostan \cite{Tost15}, \jdcmt{I don't understand any of this.
+Can you just say Tostan and others suggest cutting?
+Why can't this be put into the first s?} cutting is preferred over circumcision without diminishing or excusing the negative impact of the practice because it implies a degree of self-awareness and is considered less judgmental  \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
 \cfonly{less cites}
 
-The commonly shared position for the practice of FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.
-The progress is hindered due to the complicated history of the very practice \cite{BergDeni12, Cami16}.
-The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, and by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+\jdcmt{Wordy: ``about eradication'' is indirect} The commonly shared position for the practice of FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update} \jdcmt{Simplify: it looks like there's been a consensus for eradication for decades.} .
+The progress is hindered due to the complicated history of the \jdcmt{what does this mean?
+very practice} \cite{BergDeni12, Cami16}.
+The meanings of FGC are \jdcmt{don't understand: competitively defined by various groups from local religious community to international governmental institutes, and by linking the practice to cultural and religious identity in one end and to public health and human rights on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
 \cfonly{too many cites}.
-Understanding values and norms attached to FGC practice is essential to comprehend the persistence of FGC practice \cite{}.
+Understanding values and norms \jdcmt{you introduce norms soon, is it weird to use them now?} attached to FGC practice is essential to comprehend the persistence of FGC practice \cite{}.
 Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in comprehending,  intervening or eradicating the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} \cfonly{more cites}.
+\jdcmt{Not sure what is the relation in terms of document flow between the s. above and the s. below.}
 
@@
 Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.
-Convention theory, a widely inferred approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
-FGC is also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.
-When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}.
+Convention theory, a widely \jdcmt{not sure what this word means; inferred} approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, \jd{s.
+starting to run on} and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
+FGC is also viewed as social capital for inclusion within women’s social groups \cite{Shel-Wand11}.
+When the norms within the communities are strong, individuals tend to self-enforce community norms \jdcmt{this seems circular; self-enforcing is the definition of norms} \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}.
 \cfonly{add \cite{Bicc15}}.
 
-Although convention theory was well deliberated and applied and showed a larger effect on FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges and no coordination game was observed in marital expectation \cite{EffeVogt15}.
-Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?} as well as that it can be a social bond for women \cite{Mack00, DuncWand11}.
-Multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}
+Although convention theory was \jdcmt{doesn't seem to mean anything; well deliberated and applied} and showed a \jdcmt{larger (than what?
+do you just mean large?)} effect on FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges and no coordination game was observed in marital expectation \cite{EffeVogt15} \jdcmt{By anyone?
+Or just by them?
+It is hard for the reader to reconcile this statement with the previous one}.
+Studies show that there may be more than one \jdcmt{you seem to be conflating determining factors with tipping points; tipping point} other than marriageability \jdcmt{more than one total?
+or more than one other?
+this is awkward} underlying women’s fgc decisions \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?} \jdcmt{run-on and hard to parse:} as well as that it can be a social bond for women \cite{Mack00, DuncWand11}.
+Multiple theoretical frameworks were \jdcmt{what does this mean; called to be incorporated to grasp a full explanation} of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}
 
-In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitude on the practice.
-Besides social norms of FGC, women’s gender values and their social environment were also incorporated.
+In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitudes on the practice.
+In addition to \jdcmt{hard to figure out what this means in this context, do you just mean attitudes about FGC?
+social norms of FGC,} we also incorporated information about women’s gender values and their \jdcmt{Can you explain this?
+social environment.}
 
@@
 The similar results also applied to women’s view of whether FGC should be continued \cf{link}.
-\cfjd{How to use the future-mother producing daughter model?}.
+\cfjdcmt{How to use the future-mother producing daughter model?}.
 Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .

### 2019-07-05 manuscript.tex
Some more comments on Intro and Methods

@@
 
+\jdcmt{Think about a good \P\ structure here (and topic ss).}
 This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices.
@@
 The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in order to understand if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
-Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “daugher_ persistence” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.
+Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “daughter persistence” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.
+
+\jdcmt{Do we really call our three models: daughter; persistence; and daughter persistence? It does not seem conducive to reader understanding.}
 
@@
 
+\jd{What is added by ``and samples'' here?}
+
 We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS).
-Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication \cf{checked in 1/09/19}.
+We selected countries with: high FGC prevalence \cite{UNIC16}, and FGC benefit and gender awareness modules available from DHS.
+We found four countries, and used the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
+We did not analyze the newest dataset \jdcmt{What data set did we not analyze?
+Can we just say we analyzed the newest available (see edits above)?
+Also: these are pretty old.} due to the lack of FGC benefits modules before this study finished for publication \cf{checked in 1/09/19}.
 
-Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daugher_ persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7253 respectively.
+\jdcmt{Never use underscores without the url command; it messes up formatting.}
+Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daughter persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7253 respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
@@
 
-Our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.
-The predictors selected based on literature (e.g., aforementioned above) were woman's FGC status and beliefs of FGC benefits (see supp for a list of questionnaire of FGC benefits).
-The beliefs of FGC benefits were quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice.
+Our main response variables were woman's \jdcmt{I don't think this work adds anything; behavioural} reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.
+\jdcmt{You are describing just some predictors; The predictors selected} \jdcmt{I don't know what is being conveyed here, can we lose it?
+based on literature (e.g., aforementioned above)} were woman's FGC status and beliefs about FGC benefits (see supp for the benefit questionnaire).
+The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of benefits associating with fgc practice.
 We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}.
-Other socio demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs.
+Other socio-demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs.
 rural) in addition to country.

### 2019-07-08 manuscript.tex
A few more comments.

@@
 Our main response variables were woman's \jdcmt{I don't think this work adds anything; behavioural} reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.
-\jdcmt{You are describing just some predictors; The predictors selected} \jdcmt{I don't know what is being conveyed here, can we lose it?
+\jdcmt{You are describing just some predictors but it sounds like all; The predictors selected} \jdcmt{I don't know what is being conveyed here, can we lose it?
 based on literature (e.g., aforementioned above)} were woman's FGC status and beliefs about FGC benefits (see supp for the benefit questionnaire).
-The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of benefits associating with fgc practice.
-We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}.
+\jdcmt{This seems very wordy: The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify} the strength of benefits associating with fgc practice.
+We also included gender awareness (see WHERE for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}.
 Other socio-demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs.
@@
 788)}
+\jdcmt{What happened to the text about what we are actually doing with 
 \cfcmt{Regarding FGC benefits modules, there were 9 questions.
@@
 \cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
-
 \subsubsection{Statistical Model}\label{statistical-model}
@@
 The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
-We subtracted respondent (-1) from the cluster when testing the community effect \cfjdml{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
+\jdcmt{Did we do anything weird here with intercepts?
+Why do we have different intercepts with different models?} We subtracted respondent (-1) from the cluster when testing the community effect \cfjdml{Please rewrite this.
+Also, do we need to mention how we treat cluster with only one sample (if that happens).} \jdcmt{No, we don't have to worry about clusters with only one sample.}
 
 \cfcmt{Do we explain conveyance of uncertainty and data sampling?}
+\jdcmt{Can you explain this question?}
 
@@
 AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}
+\jdcmt{Not sure what any of this is about.
+Our response are ordinal, and binary is an example of ordinal.
+I don't think there needs a big problem with using ethnicity as a random effect, or with explaining it.
+I kind of feel we are going in circles because you're not happy with it -- but do you have a solution?}
 
@@
 
+\jdcmt{Why on request? I always distrust that from others. Any objection to publishing the code?}
+
 \subsection{Results}\label{results-1}
@@
 The prevalence of FGC are 31.8\%, 88.6\%, 45.9\% and 91.0\%, and 15.5\%, 73.9\%, 20.6\% and 65.5\% of the samples thought FGC should be continued in Kenya, Mali, Nigeria and Sierra Leon accordingly.
+\jdcmt{This \P is inaesthetic.
+If the figure is not clear enough, we could have a table?
+Or else, we could just give ranges here?}
 

### 2019-07-17 manuscript.tex
Update manuscript.tex

--- 2019-07-05 manuscript.tex
@@
 
-\jdcmt{I've been talking with Mike and Katie about writing papers that are easy to read. You should focus on paragraph structure, particularly the first s. of each \P. I will send you a link.}
-
-\jdcmt{This is a run-on sentence It is estimated,} based on a UNICEF global database \jdcmt{cite the database right here?} including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East.
-\jdcmt{Can this be a new sentence?
-are the 15 million also girls below 15?
-If so, link directly and if not, clarify} and 44 million of them are girls below age 15, with another 15 million girls at risk by 2020  \cite{AdnrLesc16, UNIC16}.
+It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.
+It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.
 Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.
-\jdcmt{Need to think about how much to about terminology and how to say it} FGC is also known as female genital mutilation and female circumcision.
-As adapted by Tostan \cite{Tost15}, \jdcmt{I don't understand any of this.
-Can you just say Tostan and others suggest cutting?
-Why can't this be put into the first s?} cutting is preferred over circumcision without diminishing or excusing the negative impact of the practice because it implies a degree of self-awareness and is considered less judgmental  \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
+Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
 \cfonly{less cites}
 
-\jdcmt{Wordy: ``about eradication'' is indirect} The commonly shared position for the practice of FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update} \jdcmt{Simplify: it looks like there's been a consensus for eradication for decades.} .
-The progress is hindered due to the complicated history of the \jdcmt{what does this mean?
-very practice} \cite{BergDeni12, Cami16}.
-The meanings of FGC are \jdcmt{don't understand: competitively defined by various groups from local religious community to international governmental institutes, and by linking the practice to cultural and religious identity in one end and to public health and human rights on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.
+The commonly shared position of FGC is about to abolish than to intervene the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
+Yet, the progress of intervention is hindered due to the complicated history \cite{BergDeni12, Cami16}.
+FGC is embodied with multiple meanings with cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
 \cfonly{too many cites}.
-Understanding values and norms \jdcmt{you introduce norms soon, is it weird to use them now?} attached to FGC practice is essential to comprehend the persistence of FGC practice \cite{}.
-Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in comprehending,  intervening or eradicating the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} \cfonly{more cites}.
-\jdcmt{Not sure what is the relation in terms of document flow between the s. above and the s. below.}
+Understanding values and meanings attached to FGC is essential to comprehend the persistence of FGC practice \cite{}.
+Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in fathoming the behaviour for intervention \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
 
-Social norm is often used to understand behavioural pattern of FGC \cfonly{more cite{BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17, Youn02} (to confirm)}.
 Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.
@@
 (see \cite{MackLeJe08} (p.28 which mentioned Bicchieri06)
+
+\cfonly{Jonathan:”The explanation of community belief is that it's left over
+after we include community behaviour. If the community believes in it,
+they'll probably do it, and then I'll probably do it. But if I
+_control for_ community behaviour, there's no reason to think that
+community belief is still explanatory. In fact, if I see myself as
+different from the community I'm more likely to break the norm than if
+I don’t.”
+}
 

### 2019-07-19 manuscript.tex
Update manuscript.tex

@@
 Understanding values and meanings attached to FGC is essential to comprehend the persistence of FGC practice \cite{}.
-Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in fathoming the behaviour for intervention \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
+Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is is crucial in intervention of sustainable changes \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
 
-Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.
-Convention theory, a widely \jdcmt{not sure what this word means; inferred} approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, \jd{s.
-starting to run on} and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.
-FGC is also viewed as social capital for inclusion within women’s social groups \cite{Shel-Wand11}.
-When the norms within the communities are strong, individuals tend to self-enforce community norms \jdcmt{this seems circular; self-enforcing is the definition of norms} \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}.
+Convention theory, a widely regarded approach in FGC norm research, posited first that FGC was a marriageability convention and, latter on, a social norm and others, such as religious obligation, adolescent rite of passage, and female honour and modesty as an important norm to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
+The convention theory views FGC as a social behaviour resulting from group coordination \cite{Mack00, MackLeJe08}.
+FGC was also viewed as a social capital, a value expected by women for inclusion within women’s social groups \cite{ShelWand11}.
+Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, ShelWand11}.
 \cfonly{add \cite{Bicc15}}.
+Although normative behaviour based on convention theory was well documented regarding analysis of persistence of FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges \cite{EffeVogt15, Njam04}.
+For example, there was no coordination game observed in marital expectation \cite{EffeVogt15}.
+it was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.
+Studies showed that factors other than marriageability have underlined women’s fgc decisions \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
 
-Although convention theory was \jdcmt{doesn't seem to mean anything; well deliberated and applied} and showed a \jdcmt{larger (than what?
-do you just mean large?)} effect on FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges and no coordination game was observed in marital expectation \cite{EffeVogt15} \jdcmt{By anyone?
-Or just by them?
-It is hard for the reader to reconcile this statement with the previous one}.
-Studies show that there may be more than one \jdcmt{you seem to be conflating determining factors with tipping points; tipping point} other than marriageability \jdcmt{more than one total?
-or more than one other?
-this is awkward} underlying women’s fgc decisions \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?} \jdcmt{run-on and hard to parse:} as well as that it can be a social bond for women \cite{Mack00, DuncWand11}.
-Multiple theoretical frameworks were \jdcmt{what does this mean; called to be incorporated to grasp a full explanation} of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}
-
-In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitudes on the practice.
+Multiple theoretical frameworks were \jdcmt{what does this mean; called to be incorporated to grasp a full explanation} of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}  In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitudes on the practice.
 In addition to \jdcmt{hard to figure out what this means in this context, do you just mean attitudes about FGC?
@@
 Subjective norm referred to “perceived social pressure to perform or not to perform the behavior” or “socially expected mode of conduct”  \cite{Ajze91}.
+% come back to the concept of self-enforce community norms mentioned in the introduction.  As jd agreed, this is a crucial concept linking to our findings.
 

### 2019-07-19 manuscript.tex
Update manuscript.tex

@@
 
-Multiple theoretical frameworks were \jdcmt{what does this mean; called to be incorporated to grasp a full explanation} of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}  In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitudes on the practice.
-In addition to \jdcmt{hard to figure out what this means in this context, do you just mean attitudes about FGC?
-social norms of FGC,} we also incorporated information about women’s gender values and their \jdcmt{Can you explain this?
-social environment.}
+In this study, we consider multiple social determinants of FGC practice both at an individual and a community level to analyze how FGC norm at a community level associates with that at an individual level in predicting the persistence of FGC practice \cfcmt{in the presumption that attitudes is a good proxy of social norm \cite{}}.
+\cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, ModrLiu13 , PashPonn16, ShelHern06,}}
 
@@
 
-\jdcmt{Do we really call our three models: daughter; persistence; and daughter persistence? It does not seem conducive to reader understanding.}
+\jdcmt{Do we really call our three models: daughter; persistence; and daughter persistence?
+It does not seem conducive to reader understanding.} \cfcmt{That was what we agreed.
+We don’t really like the names but couldn’t come up with a better one.
+How about daughter, fgc continuity, and structural mixed model?}
 
@@
 
-\subsubsection{Data and Samples}\label{data-and-samples}
+\subsubsection{Data}\label{data}
 
-\jd{What is added by ``and samples'' here?}
-
-We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS).
-We selected countries with: high FGC prevalence \cite{UNIC16}, and FGC benefit and gender awareness modules available from DHS.
+We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS) with FGC benefit and gender awareness modules in countries with high FGC prevalence \cite{UNIC16}.
 We found four countries, and used the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-We did not analyze the newest dataset \jdcmt{What data set did we not analyze?
-Can we just say we analyzed the newest available (see edits above)?
-Also: these are pretty old.} due to the lack of FGC benefits modules before this study finished for publication \cf{checked in 1/09/19}.
+\jdcmt{these are pretty old.} \cfcmt{checked in 1/09/19.
+Yes.
+Those datasets are pretty old but were the most recent ones with fgc benefits modules.}.
 
@@
 
-\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
+\subsubsection{Measurements}\label{measurements}
 
@@
 
-Our main response variables were woman's \jdcmt{I don't think this work adds anything; behavioural} reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.
-\jdcmt{You are describing just some predictors; The predictors selected} \jdcmt{I don't know what is being conveyed here, can we lose it?
-based on literature (e.g., aforementioned above)} were woman's FGC status and beliefs about FGC benefits (see supp for the benefit questionnaire).
+Our main response variables were woman's reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.
+The main predictors were woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire).
 The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of benefits associating with fgc practice.

### 2019-07-19 daughterfgc_full_clmm.R
con't cleaning

@@ -1,41 +1,0 @@
-library(ordinal)
-library(splines)
-
-
-modAns <- model.frame(
-  futurefgcDau ~ group_futurefgcDau
-  + fgcstatus + group_fgc
-  + CC
-  + bene 
-  + group_bene
-  + media + group_media 
-  + gender + group_gender
-  + edu + group_edu
-  + wealth + group_wealth
-  + age + maritalStat + job + urRural + religion
-  + clusterId + ethni 
-  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
-)
-
-fit_time <- system.time(mod<- clmm(
-  futurefgcDau ~ group_futurefgcDau
-  + fgcstatus + group_fgc
-  + CC
-  + bene 
-  + group_bene
-  + media + group_media 
-  + gender + group_gender 
-  + edu + group_edu
-  + ns(wealth,3) + ns(group_wealth,3)
-  + ns(age,4) 
-  + maritalStat 
-  + job
-  + urRural + religion
-  + (1|clusterId) + (1|ethni)
-  , data=modAns)
-)
-
-
-print(summary(mod))
-
-# rdsave(mod, modAns, fit_time)

### 2019-07-19 daughterfgc_full_varlvlsum.R

@@ -1,10 +1,0 @@
-library(ordinal)
-library(splines)
-library(RVAideMemoire)
-
-
-varlvlsum <- Anova.clmm(mod)
-
-print(varlvlsum)
-
-# rdsave(mod,modAns,varlvlsum)

### 2019-07-19 futurefgcDau_full_clmm.R

@@ -1,47 +1,0 @@
-library(dplyr)
-library(ordinal)
-library(splines)
-
-combined_dat <- (combined_dat
-	%>% group_by(clusterId)
-	%>% mutate(group_futurefgc = mean(futurefgc01, na.rm=TRUE))
-)
-
-modAns <- model.frame(
-  futurefgcDau ~ group_futurefgcDau
-  + futurefgc + group_futurefgc
-  + fgcstatus + group_fgc
-  + CC
-  + bene 
-  + group_bene
-  + media + group_media 
-  + gender + group_gender 
-  + edu + group_edu
-  + wealth + group_wealth
-  + age + maritalStat + job + urRural + religion
-  + clusterId + ethni
-  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
-)
-
-system.time(mod<- clmm(
-  futurefgcDau ~ group_futurefgcDau
-  + futurefgc + group_futurefgc
-  + fgcstatus + group_fgc
-  + CC
-  + bene 
-  + group_bene
-  + media + group_media 
-  + gender + group_gender 
-  + edu + group_edu
-  + ns(wealth,3) + ns(group_wealth,3)
-  + ns(age,4) 
-  + maritalStat 
-  + job
-  + urRural + religion
-  + (1|clusterId) + (1|ethni)
-  , data=modAns)
-)
-
-print(summary(mod))
-
-# rdsave(mod, modAns)

### 2019-07-19 futurefgc_full_clmm.R

@@ -1,40 +1,0 @@
-library(ordinal)
-library(splines)
-
-
-modAns <- model.frame(
-  futurefgc ~ group_futurefgc
-  + fgcstatus + group_fgc
-  + CC
-  + bene 
-  + group_bene
-  + media + group_media 
-  + gender + group_gender
-  + edu + group_edu
-  + wealth + group_wealth
-  + age + maritalStat + job + urRural + religion
-  + clusterId + ethni
-  , data=combined_dat, na.action=na.exclude, drop.unused.levels=TRUE
-)
-
-system.time(mod <- clmm(
-  futurefgc ~ group_futurefgc
-  + fgcstatus + group_fgc
-  + CC
-  + bene
-  + group_bene
-  + media + group_media 
-  + gender + group_gender
-  + edu + group_edu
-  + ns(wealth,3) + ns(group_wealth,3)
-  + ns(age,4) 
-  + maritalStat 
-  + job
-  + urRural + religion
-  + (1|clusterId) + (1|ethni)
-  , data=modAns)
-)
-
-print(summary(mod))
-
-# rdsave(mod, modAns)

### 2019-07-23 manuscript.tex
Update manuscript.tex

@@
 Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.
-Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
+Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in FAC decision\cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
 \cfonly{less cites}
@@
 In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.
-The commonly shared position of FGC is about to abolish than to intervene the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
-Yet, the progress of intervention is hindered due to the complicated history \cite{BergDeni12, Cami16}.
-FGC is embodied with multiple meanings with cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+The commonly shared position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
+Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16}.
+FGC is embodied with multiple perspectives from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
 \cfonly{too many cites}.
-Understanding values and meanings attached to FGC is essential to comprehend the persistence of FGC practice \cite{}.
-Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is is crucial in intervention of sustainable changes \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
+Understanding values attached to FGC is essential to comprehend the persistence of FGC practice \cite{Bicc10}.
+Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, presents a crucial venue in comprehending intervention of sustainable changes \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
 
-Convention theory, a widely regarded approach in FGC norm research, posited first that FGC was a marriageability convention and, latter on, a social norm and others, such as religious obligation, adolescent rite of passage, and female honour and modesty as an important norm to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
-The convention theory views FGC as a social behaviour resulting from group coordination \cite{Mack00, MackLeJe08}.
-FGC was also viewed as a social capital, a value expected by women for inclusion within women’s social groups \cite{ShelWand11}.
-Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, ShelWand11}.
-\cfonly{add \cite{Bicc15}}.
+It was found that FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.
+Social convention theory, a leading theory utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty as an important norm to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
+FGC was furthered deemed as a form of social capital, a value expected by women for inclusion within women’s social groups \cite{ShelWand11}.
+The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.
+Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.
 Although normative behaviour based on convention theory was well documented regarding analysis of persistence of FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges \cite{EffeVogt15, Njam04}.
-For example, there was no coordination game observed in marital expectation \cite{EffeVogt15}.
-it was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.
-Studies showed that factors other than marriageability have underlined women’s fgc decisions \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
+\cfonly{adding Bicchiori, The planned behaviour etc}For example, there was no coordination game observed in marital expectation \cite{EffeVogt15} and it was a peer convention for inclusion instead of for marriageability \cite{ShelWand11}.
+It was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.
+Studies showed that factors other than marriageability have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
 
@@
 - descriptive norm:  what others do. In our case, is it fgc prevalence in a community?
+- community level influence: “A daughter's adjusted hazard of FGMC was lower if she had an uncut mother who disfavored FGMC, lived in a community that was more opposed to FGMC, and lived in a more ethnically diverse community.
+Unexpectedly, a daughter's adjusted FGMC hazard was higher if she lived in a community with more extrafamilial opportunities for women.” \cie{GrosHayd19}
 
@@
 
-Changing social norm is a key step to changing behaviour  \cie{Bicc10}.
 Changes of social norms in public health beavhiors may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.

### 2019-07-25 manuscript.tex
Update manuscript.tex

@@
 
+Female genital cutting (FGC), circumcision or mutilation is mostly defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.
+The commonly shared position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
 It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.
 It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.
-Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.
+Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
 Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in FAC decision\cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
@@
 
-In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.
-The commonly shared position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
-Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16}.
-FGC is embodied with multiple perspectives from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}.
+FGC is embodied with multiple perspectives from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}.
 \cfonly{too many cites}.
-Understanding values attached to FGC is essential to comprehend the persistence of FGC practice \cite{Bicc10}.
-Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, presents a crucial venue in comprehending intervention of sustainable changes \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
+Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, CislHeis18, Mack96} for any negotiation and to reduce possible harmful intervention \cite{Cami15}.
+Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}; it can refer to an average outcome or a common practice \cite{MillPrin16}.
+Social norms is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15}, provides a crucial venue in negotiating sustainable changes of FGC practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
 
-It was found that FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.
-Social convention theory, a leading theory utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty as an important norm to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
-FGC was furthered deemed as a form of social capital, a value expected by women for inclusion within women’s social groups \cite{ShelWand11}.
+FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.
+Social convention theory, a leading theory (e.g., \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
+FGC was furthered deemed as a form of social capital, a value expected by women for inclusion within their social groups \cite{ShelWand11}.
 The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.
+Social expectation (i.e., what other people do or what other people believe one should do) was strongly correlated with FGC practice \cite{BiccMari15}.
 Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.
-Although normative behaviour based on convention theory was well documented regarding analysis of persistence of FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges \cite{EffeVogt15, Njam04}.
-\cfonly{adding Bicchiori, The planned behaviour etc}For example, there was no coordination game observed in marital expectation \cite{EffeVogt15} and it was a peer convention for inclusion instead of for marriageability \cite{ShelWand11}.
+
+======The planned behaviour \cite{}.
+For example, there was no coordination game observed in marital expectation \cite{EffeVogt15} and it was a peer convention for inclusion instead of for marriageability \cite{ShelWand11}.
 It was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.
 Studies showed that factors other than marriageability have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
+=====
 
@@
 
+Community-based intervention can be effective \cite{CislHeis18}.
 In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?}.

### 2019-09-12 manuscript.tex
Update manuscript.tex

@@
 
-Female genital cutting (FGC), circumcision or mutilation is mostly defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.
-The commonly shared position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
+Female genital cutting (FGC), circumcision or mutilation is mostly defined as violation of human rights \cite{WHO97, WHO08} \cfonly{add and update}.
+The commonly position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
 It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.
-It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.
+It was also predicted that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.
 Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
-Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in FAC decision\cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
+Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
 \cfonly{less cites}
 
-FGC is embodied with multiple perspectives from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}.
+FGC is embodied with multiple approaches from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}.
 \cfonly{too many cites}.
-Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, CislHeis18, Mack96} for any negotiation and to reduce possible harmful intervention \cite{Cami15}.
+Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, CislHeis18, Mack96} in order to negotiate, intervene and reduce possible harmful intervention \cite{Cami15} \cfonly {check cite}.
 Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}; it can refer to an average outcome or a common practice \cite{MillPrin16}.
@@
 Social convention theory, a leading theory (e.g., \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
-FGC was furthered deemed as a form of social capital, a value expected by women for inclusion within their social groups \cite{ShelWand11}.
+FGC was furthered deemed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}.
 The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.
@@
 Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.
+
+\cfonly{We believe this is the first FGC study using attitudes to model FGC intention by utilizing FGC norm (community level or FGC prevalence and intention)}
 
@@
 
+% “A daughter’s adjusted hazard of FGMC was lower if she had an uncut mother who disfavored FGMC, lived in a community that was more opposed to FGMC, and lived in a more ethnically diverse community.
+Unexpectedly, a daughter’s adjusted FGMC hazard was higher if she lived in a community with more extrafamilial opportunities for women. “ \cite{GrosHayf19}
 % education:  \cite{DalaLawo10, IliyAbub12, KandNwak09, KarmKand11, PashPonn16, VanMeek1}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.

### 2019-11-25 manuscript.tex
Update manuscript.tex

@@
 The commonly position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
-It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.
+It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15 \cfonly{adding KandEzej18?}.
 It was also predicted that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.
-Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
-Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
+Progress of intervention is impeded because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
+Following Tostan \cite{Tost15}, we used cutting instead of circumcision without deminishing or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
 \cfonly{less cites}
 
-FGC is embodied with multiple approaches from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}.
+FGC is embodied with multiple approaches from cultural and religious identity in one end and public health and human rights concerns on the other.
+\cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}.
 \cfonly{too many cites}.
-Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, CislHeis18, Mack96} in order to negotiate, intervene and reduce possible harmful intervention \cite{Cami15} \cfonly {check cite}.
-Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}; it can refer to an average outcome or a common practice \cite{MillPrin16}.
-Social norms is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15}, provides a crucial venue in negotiating sustainable changes of FGC practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
+Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, Cami15, CislHeis18, Mack96}.
+In this study, we focused on social values of FGC to understand the practice in communities.
+Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15} is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15} \cfonly{focus on FGC instead of the health behaviours in general}, and elaborating social norms of FGC provides a crucial venue in negotiating sustainable changes of the practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
 
-FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.
-Social convention theory, a leading theory (e.g., \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
-FGC was furthered deemed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}.
+FGC norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.
+Social convention theory, a leading theory probing FGC tradition (e.g., see \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) initially proposed that FGC was a marriageability convention through coordination \cite{Mack96} and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
 The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.
-Social expectation (i.e., what other people do or what other people believe one should do) was strongly correlated with FGC practice \cite{BiccMari15}.
-Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.
+As no coordination game was observed in marital expectation in community with FGC tradition \cite{EffeVogt15}, studies showed that factors other than marriageability have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
+FGC was also viewed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}.
+FGC practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)\cite{BiccMari15}.
+Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate the norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.
 
-\cfonly{We believe this is the first FGC study using attitudes to model FGC intention by utilizing FGC norm (community level or FGC prevalence and intention)}
-
-======The planned behaviour \cite{}.
-For example, there was no coordination game observed in marital expectation \cite{EffeVogt15} and it was a peer convention for inclusion instead of for marriageability \cite{ShelWand11}.
-It was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.
-Studies showed that factors other than marriageability have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
-=====
-
-In this study, we consider multiple social determinants of FGC practice both at an individual and a community level to analyze how FGC norm at a community level associates with that at an individual level in predicting the persistence of FGC practice \cfcmt{in the presumption that attitudes is a good proxy of social norm \cite{}}.
-\cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, ModrLiu13 , PashPonn16, ShelHern06,}}
+Although studies of FGC norms were abundant \cf{seems too strong.
+a better word than that?} as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.
+Such information adds depth to understanding the wax and wane of FGC practice.
+We believe this is the first FGC study using normative attitudes to model FGC intention by utilizing FGC norm (community level or FGC prevalence and intention).
 
@@
 
-\jdcmt{Think about a good \P\ structure here (and topic ss).}
-This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices.
-Our main interest in this study is to analyze how norms associate with behavioural intention.
-We focus on whether women will likely genitally cut their daughters based on their current intention and that provides a relatively more detailed result on how FGC norms interacts FGC practice than using than what had already happened (e.g.
-women’s own FGC status).
-The main norm theory tested in this paper was that women’s intention on practicing FGC on their daughters was dependent on other women’s intention on cutting their daughters within their community.
-We developed three models in this study.
-The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in order to understand if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.
-Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “daughter persistence” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.
+In this study, we focused on women’s intention of whether they will have their daughter’s genital modified in the context of group FGC norms and community FGC prevalence.
+The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!} in their community.
+We used index of attitudinal evaluation of FGC benefits to represent FGC norm.
+Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13 , PashPonn16, ShelHern06,}} \cfonly{check cites}.
 
-\jdcmt{Do we really call our three models: daughter; persistence; and daughter persistence?
-It does not seem conducive to reader understanding.} \cfcmt{That was what we agreed.
-We don’t really like the names but couldn’t come up with a better one.
-How about daughter, fgc continuity, and structural mixed model?}
+There were three models in this study.
+The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC to understand patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention.
+Additionally, we decomposed the model into two “structural” models:  structural one “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “daughter_persistence”  \cf{Should we go back to the word “mixed” model?
+It seems less jargon and easier to grasp the idea} model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters.
+We used the two structural models to further understand how such positions change the main model.
 
@@
 We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS) with FGC benefit and gender awareness modules in countries with high FGC prevalence \cite{UNIC16}.
-We found four countries, and used the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-\jdcmt{these are pretty old.} \cfcmt{checked in 1/09/19.
+We found four countries under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
+\jdcmt{these are pretty old.} \cfcmt{checked in 13/11/19.
 Yes.
-Those datasets are pretty old but were the most recent ones with fgc benefits modules.}.
+Those datasets are pretty old but were the most recent ones with fgc benefits modules: no fgc benefits in Mali 2013/18, Nigeria 2013/18} \cfcmt{We should a footnote to explain why the data was not current.}.
+\cf{Do we need the following sentence:  Since one of our main research interests was to detect relationship of normative attitudes and intentional behaviors of FGC practice, the findings should not be compromised due to the time of the data collected.}
 
-\jdcmt{Never use underscores without the url command; it messes up formatting.}
-Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daughter persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7253 respectively.
+Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daughter persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
@@
 
-Our main response variables were woman's reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.
+Our main response variables were woman's reported intention to modify their daughters’ genitals in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the future in the persistence model.
 The main predictors were woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire).
-The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of benefits associating with fgc practice.
-We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}.
-Other socio-demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs.
-rural) in addition to country.
+The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of fgc beliefs associating with fgc practice.
+We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would moderate \cf{wording?} their intention of cutting their daughters’ genitals and their position of FGC practice overall \cfonly{cites of feminist theory on fgc}.
+Other socio-demographic factors were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use, residence (urban vs.
+rural) and country.
 Media use and gender awareness were scored.
 The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).
+\cfcmt{Regarding FGC benefits modules, there were 9 questions.
+Kenya had all the 9, Mali and SL 7 missing promiscuity and STD, NG 8 missing STD).
+Should we drop STD since 3 out of 4 missed this variable?}
 
-Community-based intervention can be effective \cite{CislHeis18}.
 In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?}.
@@
 But as J said, it is too hard!
-} %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior.
-`` \cite{Hayf05}
-\cfcmt{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
+} \cfcmt{Whatever we decide, we need a reason in this section to justify our decision.
+After all, ethnicity is better to be a fixed factor but we can’t due to it breaking down the models!}
+\cfcmt{“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior” \cite{Hayf05}}
+\cfcmt{Bayesian model \cite{KandNwak09} “Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
 Consequently, the spatial analysis will be affected by some random fluctuations.
@@
 788)}
-\cfcmt{Regarding FGC benefits modules, there were 9 questions.
-Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).
-Should we drop STD since 3 out of 4 missed this variable?}
+
 \cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
@@
 
-— secondary analysis/socio demograhpic —
+— secondary analysis/socio demographic —
 
@@
 (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs.
-focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
+focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}; medicalizing FGC \cite{LeyeVanE19}
 - modelling by plotting empirical data to study threshold/tipping point.

### 2019-12-19 manuscript.tex
Update manuscript.tex

@@
 Progress of intervention is impeded because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
-Following Tostan \cite{Tost15}, we used cutting instead of circumcision without deminishing or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
+Following Tostan \cite{Tost15}, we used cutting instead of circumcision without diminishing or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
 \cfonly{less cites}
@@
 In this study, we focused on social values of FGC to understand the practice in communities.
-Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15} is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15} \cfonly{focus on FGC instead of the health behaviours in general}, and elaborating social norms of FGC provides a crucial venue in negotiating sustainable changes of the practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
+There is a considerable interest in applying social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15} to the intervention of public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15} \cfonly{focus on FGC instead of the health behaviours in general}, and elaborating social norms of FGC provides a crucial venue in negotiating sustainable changes of the practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
 
@@
 Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13 , PashPonn16, ShelHern06,}} \cfonly{check cites}.
+However, there has bee little quantitative research on the relationship between attitudes and intention of cutting daughters at both an individual and community level incorporating beliefs of FGC benefits.
 
@@
 Our main response variables were woman's reported intention to modify their daughters’ genitals in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the future in the persistence model.
-The main predictors were woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire).
-The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of fgc beliefs associating with fgc practice.
-We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would moderate \cf{wording?} their intention of cutting their daughters’ genitals and their position of FGC practice overall \cfonly{cites of feminist theory on fgc}.
-Other socio-demographic factors were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use, residence (urban vs.
-rural) and country.
-Media use and gender awareness were scored.
-The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).
+Co-variables in the models were sample’s fgc status, beliefs of fgc benefit, country, gender awareness, education, media, job, residence (rural vs.
+urban), religion, marital status, age, wealth; in order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
+In addition, daughter fgc plan at a group level was added to daughter model; persistence at a group level to persistence model; and daughter fgc plan at a group level, persistence and persistence at a group level to mixed model.
+
+Woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire) were our the main predictors.
+The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of fgc beliefs associating with FGC practice.
+We included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would moderate \cf{wording?} their intention of cutting their daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.
+Media use and gender awareness were both scored.
+Cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it) were treated as random variables.
+We treated ethnicity as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.
+
 \cfcmt{Regarding FGC benefits modules, there were 9 questions.
@@
 Should we drop STD since 3 out of 4 missed this variable?}
-
-In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?}.
-Cluster  was used as a proxy to represent a community level of impact \cite{AligRen06, Hayf05, Krav02}
-
 \jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
@@
 
+\cfonly{Attitude is “personal evaluation of a behaviour” \cite{Ajze91}}
+
 \subsubsection{Statistical Model}\label{statistical-model}
@@
 We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.
-The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
+The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of applying fgc to daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
 We subtracted respondent (-1) from the cluster when testing the community effect \cfjdml{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
+\cfjdml{Please explain why we didn’t do sampling weight.}
+\cfcmt{Do we explain conveyance of uncertainty}
 
-\cfcmt{Do we explain conveyance of uncertainty and data sampling?}
+\cfcmt{Our response ARE categorical not binary and need to explain how we quantify it into scores.; AND still need to explain why ethnicity is a random effect.}
 
-\cfcmt{Our response ARE categorical not binary; AND still need to explain why ethnicity is a random effect.
-AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}
-
-\cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing? }
+\cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing?
+}
 
@@
 
-Codes are be available upon request.
+Codes are available upon request.
 
@@
 
+Baseline sociodemographic and sample characteristics are shown in figure x.
+The prevalence of FGC were 31.8\%, 45.9\%, 88.6\% and 91.0\%, intention to have their daughters cut 12.3\%, 7.9\%, 47\% and 80.4\%, and supporting FGC practice in the future 15.5\%, 20.6\%, 73.9\% and 65.5\% in Kenya, Nigeria, Mali and Sierra Leon accordingly.
+The results showed patterns that the higher FGC prevalence is, the more likely mothers will have their daughters undergoing FGC and more likely to support FGC practice in the future.
+
+\cfml{sample size of daughters plan in sociodemographic figure?  It should be only the women with daughters for fgc.}
+
+The results of the three models are at figure xxx \cf{isoplots and effect plots}.
+The findings showed robust results.
+The main predictors, women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters and attitudes on whether FGC should be continued) in all the three models; so as the following factors but in negative associations:  age, education, media, religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret}.
+In addition, group level of intention to cut daughters was also clearly and positively associated with mothers’ intention to cut their daughter, as well as group persistence of FGC practice with the women’s attitudes on FGC practice.
+Although gender awareness was positively associated with both responses but only at an individual level not a group level.
+
+Basically, our main models indicated that mothers’ intention of having their daughters cut was mostly associated with the group intention on this matter (see Fig x daughterPlan_effects_plot.Rout.pdf and iso plots) \cf{group_daughterPlan  142.11  1  < 2.2e-16.
+How to transfer this into a more understandable sentence?}:  the stronger the intention of cutting daughters within their group, the more likely a mother’s intention to cut their daughters.
+Similarly in the persistent model (see persistence effect plots and iso plots), the higher the attitudes on carrying on FGC practice within a group, the more likely a mother’s attitude on supporting such a practice.
+Both models also showed that women’s beliefs in FGC benefits and their FGC status positively related to their likelihood of cutting their daughters, and supporting the practice.
+
+The results also showed that age had a negative nonlinear correlation with women’s intention of cutting their daughters (see daughter isoplot.
+i.e., the younger a woman was, the more likely to cut daughters) and with their attitudes on FGC continuity (i.e., the younger they were,  the more likely to support FGC practice).
+Wealth did not show correlation with cutting daughters but did in predicting FGC continuity (see persistence isoplot):  the higher the wealth level was, the less likely to support FGC, but the higher the group wealth level, the more likely to support the practice.
+(For other variables, see all the three iso plots and effect plots.)
+
+\cf{Need some discuss of the mixed model:  how it help to clarify our main models or what?}
+\cf{in daughter model, gender awareness (P<0.05) should be below group gender awareness (P>0.05) on effect plots based on the valvisum.Rout.  So is there a mistake? }
+cfcmt{Why isn’t mixed model our main model?}
+cfml{individual persistence is missing in the mixed model}
+
+Tables and figures to be included:
 \cf{We need to show both isoplots and effect plots because some binary variables are not on the isoplots.}
-
-Baseline socio-demographic and sample characteristics are shown in figure x.
-The prevalence of FGC are 31.8\%, 88.6\%, 45.9\% and 91.0\%, and 15.5\%, 73.9\%, 20.6\% and 65.5\% of the samples thought FGC should be continued in Kenya, Mali, Nigeria and Sierra Leon accordingly.
-
-The results of the three models are at figure?.
-The findings showed that women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters, attitudes on whether FGC should be continued); so as the following factors but in negative association:  country, media, education, age and religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret}.
-The association of gender awareness with the two responses was not clear in our findings both at a population \cf{or individual} and a community level.
+- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)
+- figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
+- figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
+- prevalence.Rout.pdf
+% a chart like figure 8-8D \cite{UNIC13}
 
 ===== stop reading =======
-
-\cfcmt{main predictors:  beliefs of FGC benefits, woman's FGC status and attitudes of gender equality}
-
-Tables and figures to be included:
-- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)
-% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
-% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
-% a chart like figure 8-8D \cite{UNIC13}
 
@@
 
-Our findings suggest that the likelihood of whether a mother will have their daughters genital cut is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others:  the norm of FGC is synergistic, based on what women think about the other women in the community will like undergo the practice than what they think about this practice.
-Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.
-The similar results also applied to women’s view of whether FGC should be continued \cf{link}.
-\cfjdcmt{How to use the future-mother producing daughter model?}.
-Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .
+Based on the findings, we believed that FGC is a coordinated social norm \cite{Makie etc}:  an individual behavioral intention is subjected to their community’s normative ritual.
+The norm of FGC is synergistic, based on what women think about other women’s likely position in their community regarding the practice (i.e., likelihood of others to cut their daughters) AND values they attached to this practice (i.e., beliefs of FGC benefits).
+Our findings indicated that the likelihood of whether a mother will cut their daughters was overdetermined by her community’s overall likelihood of mothers’ intention to cut their daughters and the mother’s personal beliefs of FGC benefits more so than by her fgc status and the community’s FGC prevalence (see daughrer isoplot x and effect plots x).
+The similar coordination was also applied to supporting FGC practice in the future.
+Based on the robust findings, we believe that FGC was an act of coordination \cite{} and supported by social values and beliefs within the community \cite{BiccMari15}.
+The coordinated performance could (or would be?) be a result of subjective norm as perceived social pressure to perform such behaviour or expected choice of conduct \cite{Ajze91}.
+\cfonly{FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15}} \cf{But what is this coordination based on if not marriageability?
+What can we find from the benefits PCAs?}
 
-The findings support the idea that the practice of FGC is supported by social values and beliefs within the community \cite{BiccMari15}.
-FGC prevalence is a strong predictor of all models and it shows that norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.
+Although FGC prevalence in a community was deemed as a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, our results found that community intention of cutting daughters is a greater factor cf{ show daughter effect plot}.
+The findings suggested that community preference (What kind of norm?
+subjective vs.
+objective?
+) carries more force on mothers’ intention on cutting their daughters:  What their community members will do is likely to determine what a mother will do to their daughters’ FGC status.
+In this case, what people did (descriptive norm?) was less a force than what they will do (subjective norm?).
+\cf{One confusing finding is that all the three models showed group fgc benefits are robustly and negatively associated with the responses.}.
+Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.
 
-— Norm —
+In the findings, community beliefs of FGC benefits had a negative correlation with both women’s intention of cutting their daughters and FGC continuance:  when the more and stronger FGC benefits were, the less likely a mother to cut their daughters and less likely to support the practice.
+This was against common wisdom \cite{}.
+”The explanation of community belief is that it's left over after we include community behaviour.
+If the community believes in it, they'll probably do it, and then I'll probably do it.
+But if I_control for_ community behaviour, there's no reason to think that community belief is still explanatory.
+In fact, if I see myself as different from the community I'm more likely to break the norm than if I don’t.” \cfjd{J:  This is basically your quote.
+Can you rewrite it?
+And I don’t understand the last sentence.}
 
+\cfonly{Rimale et ’15:  sum of benefits does not equal norm}
 - conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
-- \cite{PashPonn16}:  “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." also their findings showed that beliefs of fgc benits was the strongest predictor of mother’ intention of cutting daughters.
+- \cite{PashPonn16}:  “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." also their findings showed that beliefs of fgc benefits was the strongest predictor of mother’ intention of cutting daughters.
 \cite{ShelWand11}:“alternative convention/peer convention.
-Subjective norm referred to “perceived social pressure to perform or not to perform the behavior” or “socially expected mode of conduct”  \cite{Ajze91}.
-% come back to the concept of self-enforce community norms mentioned in the introduction.  As jd agreed, this is a crucial concept linking to our findings.
 
@@
 What does it mean that group level of daughter future as the biggest predictor compared to individual benefit and group fgc (prevalence)?
-Does it mean that fgc norm works implicitly and it might not be something behaviour women really agree with?
 Is it a social norm supported by social sanction (i.e., cutting daughter) for what reason?
 (see \cite{MackLeJe08} (p.28 which mentioned Bicchieri06)
-
-\cfonly{Jonathan:”The explanation of community belief is that it's left over
-after we include community behaviour. If the community believes in it,
-they'll probably do it, and then I'll probably do it. But if I
-_control for_ community behaviour, there's no reason to think that
-community belief is still explanatory. In fact, if I see myself as
-different from the community I'm more likely to break the norm than if
-I don’t.”
-}
 
@@
 
+*** Marriageability***
+
 — secondary analysis/socio demographic —
 
-- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02}. 
- \cit{Hayf05 SipsChen12}  Wealth.  \cite{Hayf05}: Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status
+Based on our findings that education (individual and community), wealth (individual and community), community gender awareness and job did not predict women’s intention on cutting their daughters, we proposed that modernization \cite{BoylMcMo02, Youn02} and gender perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were less a forceful intervention of FGC convention \cite{Hayf05} \cfonly{to confirm}.
 
 % age\cite{PashPonn16, SipsChen12}, \cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
+
+\cf{wealth and group wealth are in opposition direction, so did media and group media (as well as benefit and group benefit).Why?  see daughter isoplot}
+
+%\cite{Hayf05}: Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status
 
@@
 
-FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15} or social pressure \cite{}.
 — Suggestions —
 
-Changes of social norms in public health beavhiors may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.
+- How to adverse the health consequence:  Can FGC be abolished/contained?
+- vs. MC
+- Qualitative research to gather more elaborated answers of benefits of FGC
+
+Changes of social norms in public health behaviours may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.
 An alternative to fgc (a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour.
@@
 (and Boston?)
+
+\cite{Cami15}: “ interventions against FGC, rather than leading to the abandonment of the practice, can have unintended and potentially harmful effects on the way FGC is performed.”
 
@@
 
-%  while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.
 \cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),
 
---- attitudes vs.
-norm (beliefs) vs.
-(behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}  Attitude is “personal evaluation of a behaviour” \cite{Ajze91}
+--- attitudes vs. norm (beliefs) vs. (behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}  
 \cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intention:  attitude, norm and perceived behavioroal control.

### 2020-02-10 manuscript.tex
Update manuscript.tex

@@
 Progress of intervention is impeded because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
+For example, no clear change was concluded \cite{KandShel19}.
 Following Tostan \cite{Tost15}, we used cutting instead of circumcision without diminishing or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
@@
 \cfonly{too many cites}.
+Knowledge and attitudes in supporting FGC did not necessarily translate to support of abandoning the practice nor the intention not to cut daughters \cite{ChegAske04}.
 Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, Cami15, CislHeis18, Mack96}.
@@
 
-In this study, we focused on women’s intention of whether they will have their daughter’s genital modified in the context of group FGC norms and community FGC prevalence.
+In this study, we focused on women’s intention of whether they will have their daughter’s genital modified in the context of group FGC norms and geographic estimates of community FGC prevalence.
 The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!} in their community.
@@
 The prevalence of FGC were 31.8\%, 45.9\%, 88.6\% and 91.0\%, intention to have their daughters cut 12.3\%, 7.9\%, 47\% and 80.4\%, and supporting FGC practice in the future 15.5\%, 20.6\%, 73.9\% and 65.5\% in Kenya, Nigeria, Mali and Sierra Leon accordingly.
-The results showed patterns that the higher FGC prevalence is, the more likely mothers will have their daughters undergoing FGC and more likely to support FGC practice in the future.
+The results showed patterns that the higher FGC prevalence is, the more likely respondents will have their daughters undergoing FGC and more likely to support FGC practice in the future.
 
@@
 The main predictors, women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters and attitudes on whether FGC should be continued) in all the three models; so as the following factors but in negative associations:  age, education, media, religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret}.
-In addition, group level of intention to cut daughters was also clearly and positively associated with mothers’ intention to cut their daughter, as well as group persistence of FGC practice with the women’s attitudes on FGC practice.
+In addition, group level of intention to cut daughters was also clearly and positively associated with respondents’ intention to cut their daughter, as well as group persistence of FGC practice with the women’s attitudes on FGC practice.
 Although gender awareness was positively associated with both responses but only at an individual level not a group level.
 
-Basically, our main models indicated that mothers’ intention of having their daughters cut was mostly associated with the group intention on this matter (see Fig x daughterPlan_effects_plot.Rout.pdf and iso plots) \cf{group_daughterPlan  142.11  1  < 2.2e-16.
-How to transfer this into a more understandable sentence?}:  the stronger the intention of cutting daughters within their group, the more likely a mother’s intention to cut their daughters.
-Similarly in the persistent model (see persistence effect plots and iso plots), the higher the attitudes on carrying on FGC practice within a group, the more likely a mother’s attitude on supporting such a practice.
+Basically, After adjusting for individual- and community-level factors, our main models indicated that respondents’ intention of having their daughters cut was mostly associated with the group intention on this matter (see Fig x daughterPlan_effects_plot.Rout.pdf and iso plots) \cf{group_daughterPlan  142.11  1  < 2.2e-16.
+How to transfer this into a more understandable sentence?}:  the stronger the intention of cutting daughters within their group, the more likely a respondent’s intention to cut their daughters.
+Similarly in the persistent model (see persistence effect plots and iso plots), the higher the attitudes on carrying on FGC practice within a group, the more likely a respondent’s attitude on supporting such a practice.
 Both models also showed that women’s beliefs in FGC benefits and their FGC status positively related to their likelihood of cutting their daughters, and supporting the practice.
@@
 
-===== stop reading =======
-
 \subsection{Discussion}\label{Discussion}
@@
 
-Based on the findings, we believed that FGC is a coordinated social norm \cite{Makie etc}:  an individual behavioral intention is subjected to their community’s normative ritual.
-The norm of FGC is synergistic, based on what women think about other women’s likely position in their community regarding the practice (i.e., likelihood of others to cut their daughters) AND values they attached to this practice (i.e., beliefs of FGC benefits).
-Our findings indicated that the likelihood of whether a mother will cut their daughters was overdetermined by her community’s overall likelihood of mothers’ intention to cut their daughters and the mother’s personal beliefs of FGC benefits more so than by her fgc status and the community’s FGC prevalence (see daughrer isoplot x and effect plots x).
-The similar coordination was also applied to supporting FGC practice in the future.
-Based on the robust findings, we believe that FGC was an act of coordination \cite{} and supported by social values and beliefs within the community \cite{BiccMari15}.
+Based on the findings which rebutted a previous study \cite{EffeVogt15}, we believed that FGC is a social coordinated norm \cite{Makie etc} in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.
+The norm of FGC is synergistic, based on what women think about other women’s likely position in their community (i.e., likelihood of others to cut their daughters) and values they attached to this practice (i.e., beliefs of FGC benefits).
+Our findings suggested that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?}.
+The similar coordination also applied to supporting FGC practice in the future.
 The coordinated performance could (or would be?) be a result of subjective norm as perceived social pressure to perform such behaviour or expected choice of conduct \cite{Ajze91}.
 \cfonly{FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15}} \cf{But what is this coordination based on if not marriageability?
-What can we find from the benefits PCAs?}
+What can we find from the benefits PCAs?}.
+\cfonly{Need to add Hayf05}
 
-Although FGC prevalence in a community was deemed as a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, our results found that community intention of cutting daughters is a greater factor cf{ show daughter effect plot}.
-The findings suggested that community preference (What kind of norm?
-subjective vs.
-objective?
-) carries more force on mothers’ intention on cutting their daughters:  What their community members will do is likely to determine what a mother will do to their daughters’ FGC status.
-In this case, what people did (descriptive norm?) was less a force than what they will do (subjective norm?).
+That mothers’ beliefs in FGC benefits was a strong predictor of mothers' intentions to allow their daughters to undergo FGC was well studied \cite{PashPonn16} (more), yet our findings suggested that community’s overall intention on forgoing the practice was equally strong if not more forceful.
+When influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08} (more, Bicc11).
+It could be a social norm implicitly supported by social sanction (i.e., cutting daughter) \cite{Bicchieri06, MackLeJe08} (confirm).
+The correlation between women’s beliefs of FGC benefits and group intention of cutting daughters needs further studied to apprehend intentional behaviour and beliefs of normative practice of FGC for the intervention.
+\cf{Should the last sentence be in recommendation section?}.
+While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?
+As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cit{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.
+
+Based on our analysis of the benefit index \cf{the 4 countries’ PCA results}, marriageability was only one benefit for FGC, there were multiple factors in influencing women’s decision of cutting their daughters \cite{MackLeJe08}.
+It is likely tat marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, ShelWand11} (more).
+Reasons for FGC practice could go beyond the belief of marriage prospects and extend to peer convention \cite{ShelWand11}.
+In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.
+In Kenya, woman's decision on whether to implement FGC on their daughters were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.
+
+Although FGC prevalence was found a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot}:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status.
+In this case, what people did (descriptive norm?) was less a force than what they will do.
+In other words, - descriptive norm (i.e., FGC prevalence) was undermined by subjective norm (community intentional behaviour of .
 \cf{One confusing finding is that all the three models showed group fgc benefits are robustly and negatively associated with the responses.}.
 Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.
+FGC is conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19 (confirm), ShelWand11} (more)
 
-In the findings, community beliefs of FGC benefits had a negative correlation with both women’s intention of cutting their daughters and FGC continuance:  when the more and stronger FGC benefits were, the less likely a mother to cut their daughters and less likely to support the practice.
+Regarding community beliefs of FGC benefits, it had a negative correlation with both women’s intention of cutting their daughters and FGC continuance:  the stronger the overall FGC benefits was, the less likely a mother to cut their daughters and less likely to support the practice.
 This was against common wisdom \cite{}.
-”The explanation of community belief is that it's left over after we include community behaviour.
+One possible explanation is that “it's left over after we include community behaviour.
 If the community believes in it, they'll probably do it, and then I'll probably do it.
 But if I_control for_ community behaviour, there's no reason to think that community belief is still explanatory.
-In fact, if I see myself as different from the community I'm more likely to break the norm than if I don’t.” \cfjd{J:  This is basically your quote.
+In fact, if I see myself as different from the community I'm more likely to break the norm than if I don’t.” \cfjd{J:  This is basically your words.
 Can you rewrite it?
-And I don’t understand the last sentence.}
-
-\cfonly{Rimale et ’15:  sum of benefits does not equal norm}
-- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
-- \cite{PashPonn16}:  “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." also their findings showed that beliefs of fgc benefits was the strongest predictor of mother’ intention of cutting daughters.
-\cite{ShelWand11}:“alternative convention/peer convention.
-
-- descriptive norm:  what others do. In our case, is it fgc prevalence in a community?
-- community level influence: “A daughter's adjusted hazard of FGMC was lower if she had an uncut mother who disfavored FGMC, lived in a community that was more opposed to FGMC, and lived in a more ethnically diverse community.
-Unexpectedly, a daughter's adjusted FGMC hazard was higher if she lived in a community with more extrafamilial opportunities for women.” \cie{GrosHayd19}
-
- \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects.
-FGC allows women to gain social capitals and access to networks.
-Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
-\cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}.
-In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.}
-
-\cite{PashPonn16}: Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms
-
-- community level of effects -
-\cite{ChegAske04}(community -based approach), \cite{BrowBeec13, Hayf05, KandShel19, PatrSing15, ShelWand11}
-\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
-- tipping point/threshold -
-\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
--community level of fgc benefit:  can the no effect result partially due to heterogeneity?
-
-What does it mean that group level of daughter future as the biggest predictor compared to individual benefit and group fgc (prevalence)?
-Is it a social norm supported by social sanction (i.e., cutting daughter) for what reason?
-(see \cite{MackLeJe08} (p.28 which mentioned Bicchieri06)
-
-- Beliefs of FGC benefits -
-Our PCA results show that women’s beliefs of what benefits FGC brings is not clearly identified (see figure pca) and marriageability was not a clear one (to compare with \cite{Mack?,}.
-On interpretation is that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cfonly{Cite: EffeVogt15, MackLeJe08, ShelWand11, networking, part of social groups Duncan-Shell?}
-
-*** Marriageability***
+And I don’t understand the last sentence.}  It was noted that sum of benefits does not equal norm \cite{RimaLapi15}  \cfonly{Need to add Hayf05}
 
@@
 
-Based on our findings that education (individual and community), wealth (individual and community), community gender awareness and job did not predict women’s intention on cutting their daughters, we proposed that modernization \cite{BoylMcMo02, Youn02} and gender perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were less a forceful intervention of FGC convention \cite{Hayf05} \cfonly{to confirm}.
+Our models showed that the four countries were clearly different in intention of cutting their daughters where Sierra Lion with the highest likelihood Nigeria the least when compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.
+Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).
 
-% age\cite{PashPonn16, SipsChen12}, \cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
+We found that modernization defined by wealth, education and work \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were not obvious than the convention approach and that was similar to the previous conclusion \cite{Hayf05} \cfonly{to confirm}.
+Modernization (e.g., education and high socioeconomic status) had no clear impact on the likelihood of FGC, but education plays an important role in the mother's decision not to circumcise her daughter as in Nigeria \cite{KandNwak09}.
+Our findings also showed that education and wealth (both individual and community level) were clearly correlated with attitudes towards FGC continuation.
+While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment \cite{Sagn14}.
+
+While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had not clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.
+Individual education also found a positive correlation in discontinuation of FGC, such as in Egypt \cite{DalaLawo10, VanMeek16}.
+
+Younger women were also more likely to support and implement FGC on their daughters in our findings \cf{figures xx}, similar to
+
+It is noticed that the patterns of FGC benefits based on the PCA results \cfml\{PCA figures} indicated that benefits of FGC was not as clearly elaborated as the benefit module categorized.
+The main index was grouped as others.
+It means that the main reasons of why mothers intended to cut their daughters or what they believe was the real benefits/reason was not clearly stated.
+It could be reasons aforementioned as, for example, peer convention \cite{GrosHayd19 (confirm), ShelWand11}.
+Further field research is recommended to further clarify reasons of cutting.
+
+=========
+% education:  \cite{DalaLawo10, KandNwak09, PashPonn16, VanMeek1};
+
+Younger women were more likely to support FGC continuity and had higher intention of cutting their daughters as found in Ethiopia \cite{MashMatt09}
+
+% age\cite{PashPonn16, SipsChen12},
+
+% P<0.05 in \cite{Hayf05}:  women’s age, individual media,
 
@@
 
-%\cite{Hayf05}: Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status
-
 \cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
-\cite{Hayf05, PashPonn16} (more)
-
-% “A daughter’s adjusted hazard of FGMC was lower if she had an uncut mother who disfavored FGMC, lived in a community that was more opposed to FGMC, and lived in a more ethnically diverse community.
-Unexpectedly, a daughter’s adjusted FGMC hazard was higher if she lived in a community with more extrafamilial opportunities for women. “ \cite{GrosHayf19}
-% education:  \cite{DalaLawo10, IliyAbub12, KandNwak09, KarmKand11, PashPonn16, VanMeek1}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.
-
-% religion:  \cite{HayfTrin11, KarmKand11}
-
-% media:  \cite{DalaLawo10}
+\cite{Hayf05, PashPonn16} (more) % media:  \cite{DalaLawo10}
 
@@
 %Except for Mali, all the studied nations have enacted decrees or legislation related to FGC \cite{WHO13}
-
-In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.
-In Kenya, woman's decision on whether to cut their daughters' genitals were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.
 
@@
 
----- Nigeria: ``Modernization (education and high socioeconomic status) had minimal impact on the likelihood of FGM, but education plays an important role in the mother's decision not to circumcise her daughter.
-It follows from these findings that community factors have a large effect on FGM, with individual factors having little effect on the distribution of FGM" \cite{KandNwak09}
-
 ---- Sierra Leone: 
-\cite{Sagn14}
+\cite{Sagn14}  (used)
 
@@
 - Qualitative research to gather more elaborated answers of benefits of FGC
+- More options of FGC benefit module is suggested.
+- family dynamics are relevant to gain support to end female genital cutting”\cite{Hayf06}
+- Involve elders and traditional leaders to address the issue of those who wish not to participate in the cutting practice \cite{ChegAske04, more}
 
 Changes of social norms in public health behaviours may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.
-An alternative to fgc (a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour.
+An alternative to fgc (e.g., a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour.
 (using Tostan as an example) (also see \cite{Youn15}.
@@
 — Limitation —
-- No FGC types relating to our response varialbes
+- No FGC types relating to our response variables
 - Not controlling for daughter’s age
+- Not considering heterogeneity.
 
@@
 =======================================================================
+===== stop reading =======
 
 \cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),
-
---- attitudes vs. norm (beliefs) vs. (behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}  
-\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intention:  attitude, norm and perceived behavioroal control.
-
-\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))
 
@@
 
-% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors.
+% The finding “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors.
 This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.
@@
 (Since we did not categorize types of fgc in our study, we can't know if women of autonomy prefer to have a "nick" on their daughter to preserve cultural identity or abandon fgc completely.
-
-% \cite{WahlJohn17} showed that change does occur in newly immigrants once they were relocated to a new society where FGC was defied; how does this compared to \cite{EffeVogt15}'s heterogeneous model?
-
-% little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
-% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08}.
-(from the introduction.
-try to compare our result with theirs).
-% mother-daughter: \cite{PashPonn16}
 
@@
 
-% A Bourdieun approach:  how symbolic capital (fgc status) encounter social capital (wealth) and other forms of capital to gain community acceptance (what form of capital is this?)
+ \cf{(“social norm and the behavior it compels cannot be inferred from personal attitude, implicit or explicit” Mackie in his rebuttal letter.  But is vice versa true?}
 
-% \cite{Hayf06}:”Practical arrangements for a daughter’s circumcision are usually made by mothers (Caldwell et al.
-2000; Shell-Duncan, Obiero, and Muruli 2000; Thomas 2003).
-However, husbands and other family members, especially mothers-in-law, can exert pressure on women to make these arrangements (Shell- Duncan et al.
-2000; Yount 2002).
-If fathers, mothers, and grandparents have different opin- ions on the genital cutting, family power struc- tures will influence the relationship between individual attitudes toward circumcision and the practice of cutting.
-Thus, family dynamics are relevant to the process of gathering the critical mass of support that, according to convention theory, is necessary to end female genital cutting”
-
+Models:  “A Bayesian geo-additive mixed model based on Markov Chain Monte Carlo techniques was used to map the change in the spatial distribution of FGM/C prevalence” \cite{KandShel19}
 ====================================

### 2020-03-02 manuscript.tex
Update manuscript.tex

@@
 The norm of FGC is synergistic, based on what women think about other women’s likely position in their community (i.e., likelihood of others to cut their daughters) and values they attached to this practice (i.e., beliefs of FGC benefits).
-Our findings suggested that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?}.
+We propose that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?}.
 The similar coordination also applied to supporting FGC practice in the future.
@@
 
-That mothers’ beliefs in FGC benefits was a strong predictor of mothers' intentions to allow their daughters to undergo FGC was well studied \cite{PashPonn16} (more), yet our findings suggested that community’s overall intention on forgoing the practice was equally strong if not more forceful.
+That mothers’ beliefs in FGC benefits was a strong predictor of mothers' intentions to have their daughters to undergo FGC was well studied \cite{PashPonn16} (more), yet our findings suggested that community’s overall intention on forgoing the practice was equally strong if not more forceful.
 When influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08} (more, Bicc11).
@@
 \cf{Should the last sentence be in recommendation section?}.
-While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?
-As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cit{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.
 
 Based on our analysis of the benefit index \cf{the 4 countries’ PCA results}, marriageability was only one benefit for FGC, there were multiple factors in influencing women’s decision of cutting their daughters \cite{MackLeJe08}.
-It is likely tat marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, ShelWand11} (more).
+It is likely that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, ShelWand11} (more).
 Reasons for FGC practice could go beyond the belief of marriage prospects and extend to peer convention \cite{ShelWand11}.
@@
 
-Although FGC prevalence was found a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot}:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status.
+Although FGC prevalence was a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot}:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status.
 In this case, what people did (descriptive norm?) was less a force than what they will do.
@@
 
-Our models showed that the four countries were clearly different in intention of cutting their daughters where Sierra Lion with the highest likelihood Nigeria the least when compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.
+Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.
 Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).
+Modernization defined by wealth, education and work \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were not obvious than the convention approach and that was similar to the previous conclusion \cite{Hayf05} \cfonly{to confirm}.
 
-We found that modernization defined by wealth, education and work \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were not obvious than the convention approach and that was similar to the previous conclusion \cite{Hayf05} \cfonly{to confirm}.
 Modernization (e.g., education and high socioeconomic status) had no clear impact on the likelihood of FGC, but education plays an important role in the mother's decision not to circumcise her daughter as in Nigeria \cite{KandNwak09}.
@@
 Individual education also found a positive correlation in discontinuation of FGC, such as in Egypt \cite{DalaLawo10, VanMeek16}.
-
-Younger women were also more likely to support and implement FGC on their daughters in our findings \cf{figures xx}, similar to
+Younger women were also more likely to support and implement FGC on their daughters in our findings \cf{figures xx}, as found in Ethiopia \cite{MashMatt09}
 
@@
 
+———— stop reading —————
 =========
 % education:  \cite{DalaLawo10, KandNwak09, PashPonn16, VanMeek1};
-
-Younger women were more likely to support FGC continuity and had higher intention of cutting their daughters as found in Ethiopia \cite{MashMatt09}
 
@@
 — Limitation —
+While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?
+As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cit{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.
+
 - No FGC types relating to our response variables

### 2020-03-02 manuscript.tex
Update manuscript.tex

@@
 
-— secondary analysis/socio demographic —
+— socio demographic factors —
 
@@
 Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).
-Modernization defined by wealth, education and work \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were not obvious than the convention approach and that was similar to the previous conclusion \cite{Hayf05} \cfonly{to confirm}.
 
-Modernization (e.g., education and high socioeconomic status) had no clear impact on the likelihood of FGC, but education plays an important role in the mother's decision not to circumcise her daughter as in Nigeria \cite{KandNwak09}.
-Our findings also showed that education and wealth (both individual and community level) were clearly correlated with attitudes towards FGC continuation.
-While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment \cite{Sagn14}.
+The positive impact modernization \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, KandNwak09, Lewi04, Meye00, Njam04, YirgKass12, Youn02} on intention of cutting daughters were not obvious than the convention approach in our findings as well as previously concluded \cite{Hayf05} \cfonly{to confirm}.
+While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.
 
-While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had not clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.
-Individual education also found a positive correlation in discontinuation of FGC, such as in Egypt \cite{DalaLawo10, VanMeek16}.
-Younger women were also more likely to support and implement FGC on their daughters in our findings \cf{figures xx}, as found in Ethiopia \cite{MashMatt09}
+Regarding FGC continuity, education and wealth (both individual and community level) were clearly correlated with attitudes towards FGC continuation in our findings.
+While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment \cite{Sagn14}, and to Egpyt \cite{DalaLawo10, VanMeek16}.
+A secondary analysis of the Egypt DHS from 1995 to 2014 showed a positive correlation of individual level of education, job and wealth with their attitudes of FGC continuity \cite{VanMeek15} .
 
@@
 =========
-% education:  \cite{DalaLawo10, KandNwak09, PashPonn16, VanMeek1};
-
-% age\cite{PashPonn16, SipsChen12},
 

### 2020-09-06 manuscript.tex
Fixing ms, failing to fix autorefs

@@
 \newcommand{\cfcmt}[1]{\comment{CFS: #1}}
-\newcommand{\cfonly}[1]{\comment{CFS only: #1}}
+\newcommand{\cfonly}[1]{\comment{CFS (note): #1}}
+\newcommand{\cf}[1]{\comment{CFS (comment or note?): #1}}
 \newcommand{\jdcmt}[1]{\comment{JD: #1}}
@@
 The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC to understand patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention.
-Additionally, we decomposed the model into two “structural” models:  structural one “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “daughter_persistence”  \cf{Should we go back to the word “mixed” model?
+Additionally, we decomposed the model into two “structural” models:  structural one “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “daughter persistence”  \cf{Should we go back to the word “mixed” model?
 It seems less jargon and easier to grasp the idea} model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters.
@@
 The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of applying fgc to daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
-We subtracted respondent (-1) from the cluster when testing the community effect \cfjdml{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
-\cfjdml{Please explain why we didn’t do sampling weight.}
+We subtracted respondent (-1) from the cluster when testing the community effect \cfcmt{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
+\cfcmt{Please explain why we didn’t do sampling weight.}
 \cfcmt{Do we explain conveyance of uncertainty}
@@
 But if I_control for_ community behaviour, there's no reason to think that community belief is still explanatory.
-In fact, if I see myself as different from the community I'm more likely to break the norm than if I don’t.” \cfjd{J:  This is basically your words.
+In fact, if I see myself as different from the community I'm more likely to break the norm than if I don’t.” \cfcmt{J:  This is basically your words.
 Can you rewrite it?
@@
 
-=======================================================================
+%%% ======================================================================
 ===== stop reading =======

### 2021-07-22 manuscript.tex
merge?

@@
 
-\cfml{sample size of daughters plan in sociodemographic figure?  It should be only the women with daughters for fgc.}
+\cfcmt{M: sample size of daughters plan in sociodemographic figure?  It should be only the women with daughters for fgc.}
 
@@
 
-Basically, After adjusting for individual- and community-level factors, our main models indicated that respondents’ intention of having their daughters cut was mostly associated with the group intention on this matter (see Fig x daughterPlan_effects_plot.Rout.pdf and iso plots) \cf{group_daughterPlan  142.11  1  < 2.2e-16.
+Basically, After adjusting for individual- and community-level factors, our main models indicated that respondents’ intention of having their daughters cut was mostly associated with the group intention on this matter (see Fig x daughterPlan-effects-plot.Rout.pdf and iso plots) \cf{group-daughterPlan  142.11  1  < 2.2e-16.
 How to transfer this into a more understandable sentence?}:  the stronger the intention of cutting daughters within their group, the more likely a respondent’s intention to cut their daughters.
@@
 \cf{in daughter model, gender awareness (P<0.05) should be below group gender awareness (P>0.05) on effect plots based on the valvisum.Rout.  So is there a mistake? }
-cfcmt{Why isn’t mixed model our main model?}
-cfml{individual persistence is missing in the mixed model}
+\cfcmt{Why isn’t mixed model our main model?}
+\cfcmt{M: individual persistence is missing in the mixed model}
 
@@
 If the community believes in it, they'll probably do it, and then I'll probably do it.
-But if I_control for_ community behaviour, there's no reason to think that community belief is still explanatory.
+But if I \emph{control for} community behaviour, there's no reason to think that community belief is still explanatory.
 In fact, if I see myself as different from the community I'm more likely to break the norm than if I don’t.” \cfcmt{J:  This is basically your words.

### 2021-07-22 manuscript.tex
Cleaning debt, but still a lot left ☹

@@
 
-Although studies of FGC norms were abundant \cf{seems too strong.
+Although studies of FGC norms were abundant \cfcmt{seems too strong.
 a better word than that?} as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.
@@
 We used index of attitudinal evaluation of FGC benefits to represent FGC norm.
-Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13 , PashPonn16, ShelHern06,}} \cfonly{check cites}.
+Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.
 However, there has bee little quantitative research on the relationship between attitudes and intention of cutting daughters at both an individual and community level incorporating beliefs of FGC benefits.
@@
 
-Based on the findings which rebutted a previous study \cite{EffeVogt15}, we believed that FGC is a social coordinated norm \cite{Makie etc} in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.
+Based on the findings which rebutted a previous study \cite{EffeVogt15}, we believed that FGC is a social coordinated norm \cite{MakieETC} in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.
 The norm of FGC is synergistic, based on what women think about other women’s likely position in their community (i.e., likelihood of others to cut their daughters) and values they attached to this practice (i.e., beliefs of FGC benefits).
@@
 Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.
-FGC is conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19 (confirm), ShelWand11} (more)
+FGC is conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19CONFIRM, ShelWand11} (more)
 
@@
 
-Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.
+Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cf{figure xx and figure xxx}.
 Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).
@@
 The positive impact modernization \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, KandNwak09, Lewi04, Meye00, Njam04, YirgKass12, Youn02} on intention of cutting daughters were not obvious than the convention approach in our findings as well as previously concluded \cite{Hayf05} \cfonly{to confirm}.
-While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.
+While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite{Hayf05}.
 
@@
 
-It is noticed that the patterns of FGC benefits based on the PCA results \cfml\{PCA figures} indicated that benefits of FGC was not as clearly elaborated as the benefit module categorized.
+It is noticed that the patterns of FGC benefits based on the PCA results \cfcmt{M: PCA figures} indicated that benefits of FGC was not as clearly elaborated as the benefit module categorized.
 The main index was grouped as others.
 It means that the main reasons of why mothers intended to cut their daughters or what they believe was the real benefits/reason was not clearly stated.
-It could be reasons aforementioned as, for example, peer convention \cite{GrosHayd19 (confirm), ShelWand11}.
+It could be reasons aforementioned as, for example, peer convention \cite{GrosHayd19CONFIRM, ShelWand11}.
 Further field research is recommended to further clarify reasons of cutting.
@@
 - inviting faced women migrated to western society to participate in fgc intervention campaign.
-For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \ciet{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs.
+For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \cite{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs.
 trickle-down strategy)
@@
 While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?
-As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cit{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.
+As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cite{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.
 
 - No FGC types relating to our response variables
+
 - Not controlling for daughter’s age
+
 - Not considering heterogeneity.
@@
 % The finding “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors.
-This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.
+This is in contrast to the tipping point and informational cascade models …, wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.
 
@@
 
-% "Tradition, cleanliness, and virginity were the most common motives empowering the continuation of FGM/C , followed by men's wish, esthetic factors, marriage, and religion factors....
+% "Tradition, cleanliness, and virginity were the most common motives empowering the continuation of FGM/C, followed by men's wish, esthetic factors, marriage, and religion factors....
 A variety of socio-cultural myths, religious misbelievers, and hygienic and esthetic concerns were behind the FGM/C.

### 2023-12-11 manuscript.tex
Update manuscript.tex

@@
 
-Female genital cutting (FGC), circumcision or mutilation is mostly defined as violation of human rights \cite{WHO97, WHO08} \cfonly{add and update}.
-The commonly position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.
-It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15 \cfonly{adding KandEzej18?}.
-It was also predicted that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.
-Progress of intervention is impeded because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
-For example, no clear change was concluded \cite{KandShel19}.
+Female genital cutting (FGC), circumcision or mutilation, is a form of female's genital mutilation cite{} and mostly viewed as violation of human rights \cite{WHO97, WHO08} \cfonly{add and update}.
+The commonly international position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}\cfonly{update}.
+It is estimated, between 20xx to 20xx, that more than xxx million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, xx million are girls below age 15 \cfonly{based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} adding KandEzej18?
+and update}.
+The UNICEF global database predicted that another xx million girls and women were at risk by 20xx  \cite{AdnrLesc16, UNIC16, update}.
+Progress of intervention is impeded because of the complicated FGC history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}, and no clear change was concluded \cite{KandShel19} \cfonly{update}.
 Following Tostan \cite{Tost15}, we used cutting instead of circumcision without diminishing or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
@@
 We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS) with FGC benefit and gender awareness modules in countries with high FGC prevalence \cite{UNIC16}.
-We found four countries under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
+Four countries qualified under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
 \jdcmt{these are pretty old.} \cfcmt{checked in 13/11/19.
@@
 Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.
-FGC is conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19CONFIRM, ShelWand11} (more)
+There are conventional roots in FGC practice \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19CONFIRM, ShelWand11} (more)
 
@@
 A secondary analysis of the Egypt DHS from 1995 to 2014 showed a positive correlation of individual level of education, job and wealth with their attitudes of FGC continuity \cite{VanMeek15} .
+It is also important to engage community and religious leaders to understand the need for change and to generate a transformation within the culture \cite{KleiHelz18}.
 
@@
 
-- MC vs.
-FGC.
+- MC vs. FGC.  If MC is an ethnic identity among Jewish community and is overall accepted around the world, can FGC be granted for a similar value if it is just a "nick?"
 Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice.

### 2023-12-12 manuscript.tex
Autocommit

@@
 
-FGC norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.
-Social convention theory, a leading theory probing FGC tradition (e.g., see \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) initially proposed that FGC was a marriageability convention through coordination \cite{Mack96} and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.
+FGC norms are deeply internalized and morally embraced \cite{SchuLien13}.
+Social convention theory, a leading theory probing FGC tradition (e.g., see \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) initially proposed that FGC was a marriageability convention through coordination \cite{Mack96} and extending to social norms, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08, update}.
 The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.

### 2023-12-13 manuscript.tex
Update manuscript.tex

@@
 The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.
-As no coordination game was observed in marital expectation in community with FGC tradition \cite{EffeVogt15}, studies showed that factors other than marriageability have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
+As no coordination game was observed in marital expectation in community with FGC tradition \cite{EffeVogt15}, studies showed that factors other than marriageability, such as \cfonly{examples}, have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
 FGC was also viewed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}.
-FGC practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)\cite{BiccMari15}.
-Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate the norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.
+The practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)\cite{BiccMari15}.
+Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate such norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.
 
-Although studies of FGC norms were abundant \cfcmt{seems too strong.
-a better word than that?} as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.
-Such information adds depth to understanding the wax and wane of FGC practice.
-We believe this is the first FGC study using normative attitudes to model FGC intention by utilizing FGC norm (community level or FGC prevalence and intention).
+Although FGC norms were studied as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.
+Such information is expected to extend understandings of the persistence of FGC practice.
+We believe this is the first FGC study using modules of FGC normative attitudes to model the intention by utilizing FGC norm at a community level.
 
@@
 There were three models in this study.
-The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC to understand patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention.
-Additionally, we decomposed the model into two “structural” models:  structural one “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “daughter persistence”  \cf{Should we go back to the word “mixed” model?
-It seems less jargon and easier to grasp the idea} model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters.
+The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.
+Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuence and intention of genitally cutting daughters.
 We used the two structural models to further understand how such positions change the main model.
@@
 Four countries qualified under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-\jdcmt{these are pretty old.} \cfcmt{checked in 13/11/19.
-Yes.
-Those datasets are pretty old but were the most recent ones with fgc benefits modules: no fgc benefits in Mali 2013/18, Nigeria 2013/18} \cfcmt{We should a footnote to explain why the data was not current.}.
-\cf{Do we need the following sentence:  Since one of our main research interests was to detect relationship of normative attitudes and intentional behaviors of FGC practice, the findings should not be compromised due to the time of the data collected.}
+\cfcmt{checked and updated in Nov 6, 2023.
+The datasets are pretty old but were the most recent ones with FGC benefits modules.
+See FGC main page for updated info.}.
+Since one of our main research interests was to detect relationship of normative attitudes and intentional behaviors of circumcising daughters, the findings should not be compromised due to the time of the data collected.
 
-Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daughter persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.
+Only women with daughters to be considered for FGC were included in the the daughter model and the persistence model.
+The continuence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

### 2023-12-14 manuscript.tex
Autocommit

@@
 
-There were three models in this study.
+There were three models in this study:  the daughter model, the continuance model and the persistence model.
 The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.
-Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuence and intention of genitally cutting daughters.
+Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance and intention of genitally cutting daughters.
 We used the two structural models to further understand how such positions change the main model.
@@
 
-We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS) with FGC benefit and gender awareness modules in countries with high FGC prevalence \cite{UNIC16}.
+We analyzed the secondary data of women aged 15-49 in the Demographic and Health Surveys (DHS).
+The DHS was selected when it met the study criteria:  countries with high FGC prevalence \cite{UNIC16} with the modules of FGC benefit and gender awareness.
 Four countries qualified under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.

### 2023-12-19 manuscript.tex
Autocommit

@@
 
-In this study, we focused on women’s intention of whether they will have their daughter’s genital modified in the context of group FGC norms and geographic estimates of community FGC prevalence.
-The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!} in their community.
+The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!}.
 We used index of attitudinal evaluation of FGC benefits to represent FGC norm.
 Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.
-However, there has bee little quantitative research on the relationship between attitudes and intention of cutting daughters at both an individual and community level incorporating beliefs of FGC benefits.
+However, there were little quantitative research on the relationship between attitudes and intention of circumcising daughters at both an individual and community level while taking beliefs of FGC benefits into account.
 
-There were three models in this study:  the daughter model, the continuance model and the persistence model.
+Three models were constructed in response to the three research questions mentioned above:  the daughter model, the continuance model and the persistence model.
 The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.
@@
 
-We analyzed the secondary data of women aged 15-49 in the Demographic and Health Surveys (DHS).
-The DHS was selected when it met the study criteria:  countries with high FGC prevalence \cite{UNIC16} with the modules of FGC benefit and gender awareness.
-Four countries qualified under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.
-\cfcmt{checked and updated in Nov 6, 2023.
-The datasets are pretty old but were the most recent ones with FGC benefits modules.
-See FGC main page for updated info.}.
-Since one of our main research interests was to detect relationship of normative attitudes and intentional behaviors of circumcising daughters, the findings should not be compromised due to the time of the data collected.
+We analyzed the secondary data of women aged 15-49 from the Demographic and Health Surveys (DHS).
+The data was selected when it met the research criteria:  countries with high FGC prevalence \cite{UNIC16}, and with the modules of FGC status and benefit and gender awareness.
+Four countries qualified under this criteria with the most recent data sets: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008 \cfcmt{checked and updated in Nov 6, 2023.}   Although the datasets seemed outdated, but it should not affect the study object which was about FGC norms and behaviors.
+\cfcmt{See https://github.com/fishforwish/fgc/blob/master/README.md for updated info}.
 
-Only women with daughters to be considered for FGC were included in the the daughter model and the persistence model.
-The continuence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.
+Only women with daughters for for FGC options were included in the the daughter model and the persistence model.
+The continuance model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
@@
 
-Our main response variables were woman's reported intention to modify their daughters’ genitals in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the future in the persistence model.
-Co-variables in the models were sample’s fgc status, beliefs of fgc benefit, country, gender awareness, education, media, job, residence (rural vs.
-urban), religion, marital status, age, wealth; in order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
-In addition, daughter fgc plan at a group level was added to daughter model; persistence at a group level to persistence model; and daughter fgc plan at a group level, persistence and persistence at a group level to mixed model.
+The main response variables were woman's reported intention to modify their daughters’ genitals in the daughter model and the persistence model, and woman's attitude on FGC future in the continuance model.
+The main predictors were woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire).
+The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of fgc beliefs associating with FGC practice.
 
-Woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire) were our the main predictors.
-The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of fgc beliefs associating with FGC practice.
-We included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would moderate \cf{wording?} their intention of cutting their daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.
-Media use and gender awareness were both scored.
+Co-variables in the models were basic social demographic variables (country, gender awareness, education, media, job, residence (rural vs.
+urban), religion, marital status, age, and wealth).
+We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would associate with their intention of cutting daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.
 Cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it) were treated as random variables.
 We treated ethnicity as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.
+
+Regarding potential community impact on the practice of FGC, the models also teated education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
+
+In addition, daughter fgc plan at a group level was added to daughter model; persistence at a group level to persistence model; and daughter fgc plan at a group level, persistence and persistence at a group level to mixed model.
+Media use and gender awareness were also scored.
 

### 2023-12-21 manuscript.tex
Update manuscript.tex

@@
 The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.
-Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance and intention of genitally cutting daughters.
+Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance on intention of genitally cutting daughters.
 We used the two structural models to further understand how such positions change the main model.
@@
 
-Co-variables in the models were basic social demographic variables (country, gender awareness, education, media, job, residence (rural vs.
-urban), religion, marital status, age, and wealth).
-We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would associate with their intention of cutting daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.
-Cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it) were treated as random variables.
-We treated ethnicity as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.
+Co-variables in the models were basic social demographic factors (i.e., country, education, job, residence (rural vs.
+urban), religion, marital status, age, media use, and wealth) in addition to gender awareness.
+Gender awareness (see — for questions of gender awareness proxy) was included to test if women’s gender awareness interacted with their intention of cutting daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.
+Media use and gender awareness were scored.
+Cluster ID (i.e., villages where the samples were from) and ethnicity (see the list of ethnicity recode at table xx in appendix) \cfonly{with a footnote on how we recoded it} were treated as random variables.
+Ethnicity was applied as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.
 
-Regarding potential community impact on the practice of FGC, the models also teated education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
-
-In addition, daughter fgc plan at a group level was added to daughter model; persistence at a group level to persistence model; and daughter fgc plan at a group level, persistence and persistence at a group level to mixed model.
-Media use and gender awareness were also scored.
+Regarding potential community impact on the practice of FGC, mothers' intention on having FGC on daughters, FGC continuance, and FGC beliefs.
+The following also tested at a community level:  education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
 

### 2024-01-24 manuscript.tex
Update manuscript.tex

@@
 Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
-(or:  Cutting or Not:  Depending on what others will undergo the practice than what they think about the practice)
 \cfcmt{This title is a response to Efferson’s title}
@@
 
-Female genital cutting (FGC), circumcision or mutilation, is a form of female's genital mutilation cite{} and mostly viewed as violation of human rights \cite{WHO97, WHO08} \cfonly{add and update}.
+Female genital cutting (FGC), circumcision or mutilation is a form of female's genital mutilation \cfonly{cite}, Following Tostan \cite{Tost15} \cfonly{update to make sure Tostan still perfers the term}, we used cutting instead of circumcision in this study without excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
+\cfonly{less cites and update cites}.
+It is estimated that more than xxx million women and girls will have undergone female genital cutting (FGC), mostly in Africa and the Middle East, between 20xx to 20xx; and among them, xx million are girls below age 15 \cfonly{based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{check cites and adding KandEzej18?
+update}.
+The prevalence might be underreported due to a deeply embedded cultural practice that is mostly illegal \cite{StevKell22}.
+FGC is embodied with multiple approaches from cultural and religious identity in one end, and public health and human rights concerns on the other \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12} \cfonly{too many cites and update}.
 The commonly international position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}\cfonly{update}.
-It is estimated, between 20xx to 20xx, that more than xxx million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, xx million are girls below age 15 \cfonly{based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} adding KandEzej18?
-and update}.
-The UNICEF global database predicted that another xx million girls and women were at risk by 20xx  \cite{AdnrLesc16, UNIC16, update}.
-Progress of intervention is impeded because of the complicated FGC history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}, and no clear change was concluded \cite{KandShel19} \cfonly{update}.
-Following Tostan \cite{Tost15}, we used cutting instead of circumcision without diminishing or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
-\cfonly{less cites}
+Progress of intervention is impeded because of the complicated FGC history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
 
-FGC is embodied with multiple approaches from cultural and religious identity in one end and public health and human rights concerns on the other.
-\cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}.
-\cfonly{too many cites}.
-Knowledge and attitudes in supporting FGC did not necessarily translate to support of abandoning the practice nor the intention not to cut daughters \cite{ChegAske04}.
-Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, Cami15, CislHeis18, Mack96}.
-In this study, we focused on social values of FGC to understand the practice in communities.
-There is a considerable interest in applying social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15} to the intervention of public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15} \cfonly{focus on FGC instead of the health behaviours in general}, and elaborating social norms of FGC provides a crucial venue in negotiating sustainable changes of the practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.
+Knowledge and attitudes in supporting FGC abolishment did not necessarily translate to abandon the practice nor the intention not to modify women's genitals \cite{ChegAske04, Bicc10, Cami15, CislHeis18, Mack96} \cfonly{more cites}.
+Understanding reasons and values attached to FGC is essential for comprehending the persistence of the practice \cite{Bicc10, Cami15, CislHeis18, Mack96, Youn15} \cfonly{update}.
+There is a considerable interest in applying social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}, to the intervention of public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15} \cfonly{focus on FGC instead of the health behaviours in general, and update cites}.
+FGC norms are deeply internalized and morally embraced \cite{SchuLien13} \cfonly{update}.
+Social convention theory, a leading theory probing FGC tradition (e.g., see \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12} \cfonly{update}) initially proposed that FGC was a marriageability convention through coordination \cite{Mack96} and extended to broader social norms, such as social prestige, adolescent rite of passage, and female honour and modesty \cite{Mack00, MackLeJe08} \cfonly{more cites}.
+The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11} \cfonly{more cites}.
+As no coordination game was observed in marital expectation in community with FGC tradition \cite{EffeVogt15}\cfonly{more cites}, studies showed that factors other than marriageability, such as \cfonly{examples}, have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
+FGC was also viewed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}.
+The practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)\cite{BiccMari15} \cfonly{more cites}.
+Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate such norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}\cfonly{more cites}.
 
-FGC norms are deeply internalized and morally embraced \cite{SchuLien13}.
-Social convention theory, a leading theory probing FGC tradition (e.g., see \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) initially proposed that FGC was a marriageability convention through coordination \cite{Mack96} and extending to social norms, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08, update}.
-The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.
-As no coordination game was observed in marital expectation in community with FGC tradition \cite{EffeVogt15}, studies showed that factors other than marriageability, such as \cfonly{examples}, have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
-FGC was also viewed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}.
-The practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)\cite{BiccMari15}.
-Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate such norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.
-
+Understanding social norms of FGC provides a venue in negotiating sustainable changes of the practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less and update}.
+In this study, we anlayzed types of social values of FGC perceived in communities and the associations of social values and FGC practice.
 Although FGC norms were studied as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.
 Such information is expected to extend understandings of the persistence of FGC practice.
-We believe this is the first FGC study using modules of FGC normative attitudes to model the intention by utilizing FGC norm at a community level.
+We believe this is the first FGC study using modules of FGC normative attitudes to model the FGC intention by utilizing the norm in the context of community influence.
 
@@
 
-The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!}.
-We used index of attitudinal evaluation of FGC benefits to represent FGC norm.
-Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.
-However, there were little quantitative research on the relationship between attitudes and intention of circumcising daughters at both an individual and community level while taking beliefs of FGC benefits into account.
+There are two research questions:  what is the association of daughter's FGC future and mothers' FGC beliefs, and what is the association of FGC continuance and FGC beliefs.
+The research presumption was based on the studies aforementioned that women’s FGC intention on their daughters was dependent on other women’s attitudes on this practice \cfonly{descriptive norms?!}.
+Attitude is a personal evaluation of behaviour \cite{Ajze91}, a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11}\cfonly{cut cites}}.
+It is an important index used to evaluate fgc practices \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.
+However, there was little quantitative research on the relationship between attitudes and intention of circumcising daughters at both an individual and community level while taking beliefs of FGC benefits into account.
 
-Three models were constructed in response to the three research questions mentioned above:  the daughter model, the continuance model and the persistence model.
-The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.
-Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance on intention of genitally cutting daughters.
-We used the two structural models to further understand how such positions change the main model.
+Two main models were constructed in response to the two research questions mentioned above:  the daughter model, and the continuance model.
+In addition, we also tested a “persistence” model, to examine the association of FGC benefits and FGC continuance on mothers' intention on FGC their  daughters.
+Both of the continuance model and the persistence model were purposed to further understand how the position of the main model could be changed under the two structural models.
 
@@
 
-We analyzed the secondary data of women aged 15-49 from the Demographic and Health Surveys (DHS).
-The data was selected when it met the research criteria:  countries with high FGC prevalence \cite{UNIC16}, and with the modules of FGC status and benefit and gender awareness.
-Four countries qualified under this criteria with the most recent data sets: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008 \cfcmt{checked and updated in Nov 6, 2023.}   Although the datasets seemed outdated, but it should not affect the study object which was about FGC norms and behaviors.
+We analyzed the secondary data of women aged 15-49 from the Demographic and Health Surveys (DHS) when it met the research criteria:  countries with high FGC prevalence \cite{UNIC16}, and with the modules of FGC status, FGC benefit, and gender awareness.
+As a result, four countries of the most recent datasets were selected: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008 \cfcmt{checked and updated in Nov 6, 2023.}   Although the datasets seemed outdated, it should not affect the study object to understand FGC norms and behaviors.
 \cfcmt{See https://github.com/fishforwish/fgc/blob/master/README.md for updated info}.
 
-Only women with daughters for for FGC options were included in the the daughter model and the persistence model.
-The continuance model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.
+Only women with daughters for FGC options were included in the the daughter model and the persistence model.
+The continuance model included all the women in the datasets; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.
 \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}
@@
 
-The main response variables were woman's reported intention to modify their daughters’ genitals in the daughter model and the persistence model, and woman's attitude on FGC future in the continuance model.
-The main predictors were woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire).
-The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of fgc beliefs associating with FGC practice.
+The main responses and predictors in the models are as: FGC benefits (predictor) -->  to FGC daughters (response) in the daughter model, FGC benefits --> FGC future in the continuance model, and FGC benefits and FGC continuance --> to FGC daughters in the persistence model.
+The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of FGC beliefs associating with FGC practice.
 
-Co-variables in the models were basic social demographic factors (i.e., country, education, job, residence (rural vs.
+The co-variables were basic social demographic factors (i.e., country, education, job, residence (rural vs.
 urban), religion, marital status, age, media use, and wealth) in addition to gender awareness.
-Gender awareness (see — for questions of gender awareness proxy) was included to test if women’s gender awareness interacted with their intention of cutting daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.
-Media use and gender awareness were scored.
+Gender awareness (see — for questions of gender awareness proxy) was included to test if women’s gender awareness interacted with their intention of FGC daughters and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.
+Media use and gender awareness were also scored.
 Cluster ID (i.e., villages where the samples were from) and ethnicity (see the list of ethnicity recode at table xx in appendix) \cfonly{with a footnote on how we recoded it} were treated as random variables.
-Ethnicity was applied as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.
+Ethnicity was treated as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.
 
-Regarding potential community impact on the practice of FGC, mothers' intention on having FGC on daughters, FGC continuance, and FGC beliefs.
-The following also tested at a community level:  education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
+Regarding potential community impact on the practice of FGC, the following factors were also tested at a community level:  mothers' intention on FGC daughters, FGC continuance, and FGC benefits as well as the basic social-demographic factors:  education, wealth, media use, gender awareness and FGC prevalence \cfcmt{to confirm:  it's on a cluster level, not national.
+Correct?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
 
@@
 } \cfcmt{Whatever we decide, we need a reason in this section to justify our decision.
-After all, ethnicity is better to be a fixed factor but we can’t due to it breaking down the models!}
+After all, ethnicity is better to be a fixed factor but we can’t because it breaks down the models!}
+
 \cfcmt{“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior” \cite{Hayf05}}
@@
 
-\cfonly{Attitude is “personal evaluation of a behaviour” \cite{Ajze91}}
-
 \subsubsection{Statistical Model}\label{statistical-model}
@@
 We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.
-The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of applying fgc to daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
+The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of applying FGC to daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
 We subtracted respondent (-1) from the cluster when testing the community effect \cfcmt{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
@@
 Further field research is recommended to further clarify reasons of cutting.
+
+Norms can be rooted in what one thinks, passively or actively, others think which can be based on one's action or the communication.
 
@@
 ====================================
+
+Suggested reviewers:
+* Kerrie Stevenson (ku.ca.mthsl@nosnevets.eirrek): Faculty of Public Health and Policy, London School of Hygiene and Tropical Medicine, London, United Kingdom; Institute of Health Informatics, University College London, London, United Kingdom
+* Brenda Kelly, Oxford University Hospitals NHS Foundation Trust, The Oxford Rose Clinic, Oxford, United Kingdom

### 2024-01-25 manuscript.tex
Update manuscript.tex
referred to a format in the YouTube version: ms.jansub.tex

@@
-\documentclass[12pt,]{article}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
-\usepackage{lmodern}
-\usepackage{adjustbox}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\usepackage{longtable}
-\usepackage{url,hyperref}
-\hypersetup{unicode=true,
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-
-\usepackage{longtable,booktabs}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
   \IfFileExists{parskip.sty}{%
@@
     \setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
   \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\newcommand{\comment}[1]{\textbf{[[#1]]}}
-\newcommand{\cfcmt}[1]{\comment{CFS: #1}}
-\newcommand{\cfonly}[1]{\comment{CFS (note): #1}}
-\newcommand{\cf}[1]{\comment{CFS (comment or note?): #1}}
-\newcommand{\jdcmt}[1]{\comment{JD: #1}}
-\newcommand{\mlcmt}[1]{\comment{MLi: #1}}
-
-\bibliographystyle{plain}
-
+\author{}
 \date{}
@@
 
-\subsection{Manuscript}\label{manuscript}
+Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
 
-\subsubsection{Title}\label{title}
+Chyun-Fung Shi (1), Mike Li (2,3), Jonathan Dushoff (1,2,4)
 
-Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
-\cfcmt{This title is a response to Efferson’s title}
+1 Department of Biology, McMaster University, Hamilton, ON, Canada.
+2 Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada.
+3 PHAC, ON, Canada.
+4 Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada.
 
-\subsubsection{Authors}\label{authors}
+\hypertarget{abstract}{%
+\section{Abstract}\label{abstract}}
 
-Chyun-Fung Shi (corresponding author), Department of Biology, McMaster
-University. Michael Li, Department of Biology, McMaster University.
-Jonathan Dushoff, Department of Biology, McMaster
-University.
+\textbf{Objective:}  
+\textbf{Methods:} 
+\textbf{Results:} 
+\textbf{Conclusion:} 
+\textbf{Objective:}
 
-\subsection{journals}\label{journals}
-possible consideration:  The Lancet Global Health, Science, BMJ, Bulletin of WHO
+\hypertarget{keywords}{%
+\section{Keywords}\label{keywords}}
 
-\subsection{Abstract}\label{abstract}
+Female genital cutting, female circumcision, social norm, health behavior.
 
-\subsubsection{Context}\label{context}
+\hypertarget{background}{%
+\section{Background}\label{background}}
 
-\subsubsection{}\label{objective}
+Female genital cutting (FGC), circumcision or mutilation is a form of altering or injuring female's genitalia for non-medical reasons.
+[UNIC21], Following Tostan [Tost15], we used cutting instead of circumcision or mutilation in this study without excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC [JohnEsse10, Meye00, Shel01, Tost15].
+\cfonly{less cites and update cites].
+It is estimated that more than xxx million women and girls will have undergone female genital cutting (FGC), mostly in Africa and the Middle East, between 20xx to 20xx; and among them, xx million are girls below age 15 \cfonly{based on a UNICEF global database} [AdnrLesc16, UNIC16] \cfcmt{check cites and adding KandEzej18?
+update}.
+The prevalence might be underreported due to a deeply embedded cultural practice that is mostly illegal [StevKell22].
+FGC is embodied with multiple approaches from cultural and religious identity in one end, and public health and human rights concerns on the other [AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12] \cfonly{too many cites and update}.
+The commonly international position of FGC is about abolishment than intervention of the practice [KhosBane17, Mack96, Toub94, UNIC16, WHO97]\cfonly{update}.
+Progress of intervention is impeded because of the complicated FGC history [BergDeni12, Cami16] and of not keeping up with the population growth [KhosBane17, UNIC16].
 
-\subsubsection{Methods}\label{Methods}
+Knowledge and attitudes in supporting FGC abolishment did not necessarily translate to abandon the practice nor the intention not to modify women's genitals [ChegAske04, Bicc10, Cami15, CislHeis18, Mack96] \cfonly{more cites}.
+Understanding reasons and values attached to FGC is essential for comprehending the persistence of the practice [Bicc10, Cami15, CislHeis18, Mack96, Youn15] \cfonly{update}.
+There is a considerable interest in applying social norm, a form of values driving behavioural patterns which are self-enforcing within a group [Youn15], to the intervention of public health behaviours [Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15] \cfonly{focus on FGC instead of the health behaviours in general, and update cites}.
+FGC norms are deeply internalized and morally embraced [SchuLien13] \cfonly{update}.
+Social convention theory, a leading theory probing FGC tradition (e.g., see [BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12] \cfonly{update}) initially proposed that FGC was a marriageability convention through coordination [Mack96] and extended to broader social norms, such as social prestige, adolescent rite of passage, and female honour and modesty [Mack00, MackLeJe08] \cfonly{more cites}.
 
-\subsubsection{Main Outcome Measures}\label{main-outcome-measures}
+The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network [Mack00, MackLeJe08, ShelWand11] \cfonly{more cites}.
+As no coordination game was observed in marital expectation in community with FGC tradition [EffeVogt15]\cfonly{more cites}, studies showed that factors other than marriageability, such as \cfonly{examples}, have underlined women’s  decisions of FGC [AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?].
+FGC was also viewed as a form of social capital, a value respected by women for inclusion within their social groups [ShelWand11].
+The practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)[BiccMari15] \cfonly{more cites}.
+Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate such norms [Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92] \cfonly{add [Bicc15]]\cfonly{more cites}.
 
-\subsubsection{Results}\label{results}
-
-\subsubsection{Conclusions}\label{conclusions}
-
-\subsubsection{Funding}\label{funding}
-
-\subsubsection{Keywords}\label{keywords}
-
-female genital cutting/mutilation, multilevel model, social norms, gender, DHS
-
-\subsection{Introduction}\label{introduction}
-
-Female genital cutting (FGC), circumcision or mutilation is a form of female's genital mutilation \cfonly{cite}, Following Tostan \cite{Tost15} \cfonly{update to make sure Tostan still perfers the term}, we used cutting instead of circumcision in this study without excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}.
-\cfonly{less cites and update cites}.
-It is estimated that more than xxx million women and girls will have undergone female genital cutting (FGC), mostly in Africa and the Middle East, between 20xx to 20xx; and among them, xx million are girls below age 15 \cfonly{based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{check cites and adding KandEzej18?
-update}.
-The prevalence might be underreported due to a deeply embedded cultural practice that is mostly illegal \cite{StevKell22}.
-FGC is embodied with multiple approaches from cultural and religious identity in one end, and public health and human rights concerns on the other \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12} \cfonly{too many cites and update}.
-The commonly international position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}\cfonly{update}.
-Progress of intervention is impeded because of the complicated FGC history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.
-
-Knowledge and attitudes in supporting FGC abolishment did not necessarily translate to abandon the practice nor the intention not to modify women's genitals \cite{ChegAske04, Bicc10, Cami15, CislHeis18, Mack96} \cfonly{more cites}.
-Understanding reasons and values attached to FGC is essential for comprehending the persistence of the practice \cite{Bicc10, Cami15, CislHeis18, Mack96, Youn15} \cfonly{update}.
-There is a considerable interest in applying social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}, to the intervention of public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15} \cfonly{focus on FGC instead of the health behaviours in general, and update cites}.
-FGC norms are deeply internalized and morally embraced \cite{SchuLien13} \cfonly{update}.
-Social convention theory, a leading theory probing FGC tradition (e.g., see \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12} \cfonly{update}) initially proposed that FGC was a marriageability convention through coordination \cite{Mack96} and extended to broader social norms, such as social prestige, adolescent rite of passage, and female honour and modesty \cite{Mack00, MackLeJe08} \cfonly{more cites}.
-The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11} \cfonly{more cites}.
-As no coordination game was observed in marital expectation in community with FGC tradition \cite{EffeVogt15}\cfonly{more cites}, studies showed that factors other than marriageability, such as \cfonly{examples}, have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.
-FGC was also viewed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}.
-The practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)\cite{BiccMari15} \cfonly{more cites}.
-Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate such norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}\cfonly{more cites}.
-
-Understanding social norms of FGC provides a venue in negotiating sustainable changes of the practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less and update}.
-In this study, we anlayzed types of social values of FGC perceived in communities and the associations of social values and FGC practice.
-Although FGC norms were studied as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.
+Understanding social norms of FGC provides insights of the gaps between both camps on each end mentioned above, and a venue in negotiating sustainable changes of the practice [Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13] \cfonly{less and update}.
+In this study, we analyzed types of social norms of FGC perceived in communities and the associations of the FGC norms and the practice.
+Although there have been studies on FGC norms as aforementioned, there was limited calcification of types of individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention in response to the community norm.
 Such information is expected to extend understandings of the persistence of FGC practice.
@@
 
-\subsection{Research Questions}\label{research-questions}
+Research Questions
+=================
+\hypertarget{Research-Questions}{%
+\section{Research Questions}\label{Research-Questions}}
 
@@
 The research presumption was based on the studies aforementioned that women’s FGC intention on their daughters was dependent on other women’s attitudes on this practice \cfonly{descriptive norms?!}.
-Attitude is a personal evaluation of behaviour \cite{Ajze91}, a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11}\cfonly{cut cites}}.
-It is an important index used to evaluate fgc practices \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.
+Attitude is a personal evaluation of behaviour [Ajze91], a sensible proxy of social norm \cfonly {norm theory [Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11]\cfonly{cut cites}].
+It is an important index used to evaluate fgc practices [CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,]} \cfonly{check cites}.
 However, there was little quantitative research on the relationship between attitudes and intention of circumcising daughters at both an individual and community level while taking beliefs of FGC benefits into account.
@@
 Two main models were constructed in response to the two research questions mentioned above:  the daughter model, and the continuance model.
-In addition, we also tested a “persistence” model, to examine the association of FGC benefits and FGC continuance on mothers' intention on FGC their  daughters.
-Both of the continuance model and the persistence model were purposed to further understand how the position of the main model could be changed under the two structural models.
+In addition, we also tested a “persistence” model, to examine the association of mothers' intention on FGC their daughters and their view of FGC continuance FGC benefits predicted by mother's FGC status and their FGC beliefs .
+The persistence model was purposed to further understand how the position of the main model could be changed under mother's attitude on FGC continuance.
 
-\subsection{Methods}\label{methods}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
-\subsubsection{Data}\label{data}
+\hypertarget{data-selection}{%
+\subsection{Data selection}\label{data-selection}}
 
-We analyzed the secondary data of women aged 15-49 from the Demographic and Health Surveys (DHS) when it met the research criteria:  countries with high FGC prevalence \cite{UNIC16}, and with the modules of FGC status, FGC benefit, and gender awareness.
+We analyzed the secondary data of women aged 15-49 from the Demographic and Health Surveys (DHS) when it met the research criteria:  countries with high FGC prevalence [UNIC16], and with the modules of FGC status, FGC benefit, and gender awareness.
 As a result, four countries of the most recent datasets were selected: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008 \cfcmt{checked and updated in Nov 6, 2023.}   Although the datasets seemed outdated, it should not affect the study object to understand FGC norms and behaviors.
@@
 
-\subsubsection{Measurements}\label{measurements}
+\hypertarget{Measurements}{%
+\subsection{Measurements}\label{Measurements}}
 
-\cfonly{\cite{Rima08}}*
+\cfonly{[Rima08]]}*
 
 The main responses and predictors in the models are as: FGC benefits (predictor) -->  to FGC daughters (response) in the daughter model, FGC benefits --> FGC future in the continuance model, and FGC benefits and FGC continuance --> to FGC daughters in the persistence model.
-The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of FGC beliefs associating with FGC practice.
+The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm] to identify the strength of FGC beliefs associating with FGC practice.
 
@@
 urban), religion, marital status, age, media use, and wealth) in addition to gender awareness.
-Gender awareness (see — for questions of gender awareness proxy) was included to test if women’s gender awareness interacted with their intention of FGC daughters and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.
+Gender awareness (see — for questions of gender awareness proxy) was included to test if women’s gender awareness interacted with their intention of FGC daughters and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02] check and cut].
 Media use and gender awareness were also scored.
-Cluster ID (i.e., villages where the samples were from) and ethnicity (see the list of ethnicity recode at table xx in appendix) \cfonly{with a footnote on how we recoded it} were treated as random variables.
-Ethnicity was treated as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.
+Cluster ID (i.e., villages where the samples were from) and ethnicity (see the list of ethnicity recode at table xx in appendix) \cfonly{with a footnote on how we recoded it] were treated as random variables.
+Ethnicity was treated as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity [Hayf05].
 
 Regarding potential community impact on the practice of FGC, the following factors were also tested at a community level:  mothers' intention on FGC daughters, FGC continuance, and FGC benefits as well as the basic social-demographic factors:  education, wealth, media use, gender awareness and FGC prevalence \cfcmt{to confirm:  it's on a cluster level, not national.
-Correct?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
+Correct?] with cluster as a proxy to represent a community level of impact [AligRen06, BoylSvec19, Hayf05, Krav02].
 
@@
 Kenya had all the 9, Mali and SL 7 missing promiscuity and STD, NG 8 missing STD).
-Should we drop STD since 3 out of 4 missed this variable?}
-\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
+Should we drop STD since 3 out of 4 missed this variable?]
+\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.] \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.
 But as J said, it is too hard!
-} \cfcmt{Whatever we decide, we need a reason in this section to justify our decision.
-After all, ethnicity is better to be a fixed factor but we can’t because it breaks down the models!}
+] \cfcmt{Whatever we decide, we need a reason in this section to justify our decision.
+After all, ethnicity is better to be a fixed factor but we can’t because it breaks down the models!]
 
-\cfcmt{“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior” \cite{Hayf05}}
-\cfcmt{Bayesian model \cite{KandNwak09} “Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
+\cfcmt{“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior” [Hayf05]]
+\cfcmt{Bayesian model [KandNwak09] “Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level.
 Consequently, the spatial analysis will be affected by some random fluctuations.
@@
 However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p.
-788)}
+788)]
 
-\cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).
+\cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see [Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02])}
 
-\subsubsection{Statistical Model}\label{statistical-model}
+\hypertarget{Statistical-Model}{%
+\subsection{Statistical Model}\label{Statistical-Model}}
 
-We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.
+We used cumulative link mixed models (CLMMs) in the statistics package R [Rstats,Rpackage_ordinal] to analyze the models.
 The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of applying FGC to daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.
@@
 \cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing?
+
 }
 
-\cfonly{reference: Methods and the first paragraph of Discussion\cite{Chia14}}
+\cfonly{reference: Methods and the first paragraph of Discussion[Chia14]}
 
-\subsubsection{Scripts}\label{scripts}
+\hypertarget{Scripts}{%
+\subsection{Scripts}\label{Scripts}}
 
@@
 
-\subsection{Results}\label{results-1}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 
-\cfcmt{M: sample size of daughters plan in sociodemographic figure?  It should be only the women with daughters for fgc.}
+\cfcmt{M: sample size of daughters plan in sociodemographic figure?  It should be only the women with daughters for fgc.]
 
-The results of the three models are at figure xxx \cf{isoplots and effect plots}.
+The results of the three models are at figure xxx \cf{isoplots and effect plots].
 The findings showed robust results.
-The main predictors, women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters and attitudes on whether FGC should be continued) in all the three models; so as the following factors but in negative associations:  age, education, media, religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret}.
+The main predictors, women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters and attitudes on whether FGC should be continued) in all the three models; so as the following factors but in negative associations:  age, education, media, religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret].
 In addition, group level of intention to cut daughters was also clearly and positively associated with respondents’ intention to cut their daughter, as well as group persistence of FGC practice with the women’s attitudes on FGC practice.
@@
 Basically, After adjusting for individual- and community-level factors, our main models indicated that respondents’ intention of having their daughters cut was mostly associated with the group intention on this matter (see Fig x daughterPlan-effects-plot.Rout.pdf and iso plots) \cf{group-daughterPlan  142.11  1  < 2.2e-16.
-How to transfer this into a more understandable sentence?}:  the stronger the intention of cutting daughters within their group, the more likely a respondent’s intention to cut their daughters.
+How to transfer this into a more understandable sentence?]:  the stronger the intention of cutting daughters within their group, the more likely a respondent’s intention to cut their daughters.
 Similarly in the persistent model (see persistence effect plots and iso plots), the higher the attitudes on carrying on FGC practice within a group, the more likely a respondent’s attitude on supporting such a practice.
@@
 
-\cf{Need some discuss of the mixed model:  how it help to clarify our main models or what?}
-\cf{in daughter model, gender awareness (P<0.05) should be below group gender awareness (P>0.05) on effect plots based on the valvisum.Rout.  So is there a mistake? }
-\cfcmt{Why isn’t mixed model our main model?}
-\cfcmt{M: individual persistence is missing in the mixed model}
+\cf{Need some discuss of the mixed model:  how it help to clarify our main models or what?]
+\cf{in daughter model, gender awareness (P<0.05) should be below group gender awareness (P>0.05) on effect plots based on the valvisum.Rout.  So is there a mistake? ]
+\cfcmt{Why isn’t mixed model our main model?]
+\cfcmt{M: individual persistence is missing in the mixed model]
 
 Tables and figures to be included:
-\cf{We need to show both isoplots and effect plots because some binary variables are not on the isoplots.}
-- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)
+\cf{We need to show both isoplots and effect plots because some binary variables are not on the isoplots.]
+- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/], Fig 1)
 - figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
@@
 - prevalence.Rout.pdf
-% a chart like figure 8-8D \cite{UNIC13}
+% a chart like figure 8-8D [UNIC13]
 
-\subsection{Discussion}\label{Discussion}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 
-Based on the findings which rebutted a previous study \cite{EffeVogt15}, we believed that FGC is a social coordinated norm \cite{MakieETC} in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.
+Based on the findings which rebutted a previous study [EffeVogt15], we believed that FGC is a social coordinated norm [MakieETC] in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.
 The norm of FGC is synergistic, based on what women think about other women’s likely position in their community (i.e., likelihood of others to cut their daughters) and values they attached to this practice (i.e., beliefs of FGC benefits).
-We propose that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?}.
+We propose that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?].
 The similar coordination also applied to supporting FGC practice in the future.
-The coordinated performance could (or would be?) be a result of subjective norm as perceived social pressure to perform such behaviour or expected choice of conduct \cite{Ajze91}.
-\cfonly{FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15}} \cf{But what is this coordination based on if not marriageability?
-What can we find from the benefits PCAs?}.
-\cfonly{Need to add Hayf05}
+The coordinated performance could (or would be?) be a result of subjective norm as perceived social pressure to perform such behaviour or expected choice of conduct [Ajze91].
+\cfonly{FGC is less a coordination rite than singling group identity and symbolism [ShelWand11, Youn15]] \cf{But what is this coordination based on if not marriageability?
+What can we find from the benefits PCAs?].
+\cfonly{Need to add Hayf05]
 
-That mothers’ beliefs in FGC benefits was a strong predictor of mothers' intentions to have their daughters to undergo FGC was well studied \cite{PashPonn16} (more), yet our findings suggested that community’s overall intention on forgoing the practice was equally strong if not more forceful.
-When influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08} (more, Bicc11).
-It could be a social norm implicitly supported by social sanction (i.e., cutting daughter) \cite{Bicchieri06, MackLeJe08} (confirm).
+That mothers’ beliefs in FGC benefits was a strong predictor of mothers' intentions to have their daughters to undergo FGC was well studied [PashPonn16] (more), yet our findings suggested that community’s overall intention on forgoing the practice was equally strong if not more forceful.
+When influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours [Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08] (more, Bicc11).
+It could be a social norm implicitly supported by social sanction (i.e., cutting daughter) [Bicchieri06, MackLeJe08] (confirm).
 The correlation between women’s beliefs of FGC benefits and group intention of cutting daughters needs further studied to apprehend intentional behaviour and beliefs of normative practice of FGC for the intervention.
-\cf{Should the last sentence be in recommendation section?}.
+\cf{Should the last sentence be in recommendation section?].
 
-Based on our analysis of the benefit index \cf{the 4 countries’ PCA results}, marriageability was only one benefit for FGC, there were multiple factors in influencing women’s decision of cutting their daughters \cite{MackLeJe08}.
-It is likely that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, ShelWand11} (more).
-Reasons for FGC practice could go beyond the belief of marriage prospects and extend to peer convention \cite{ShelWand11}.
-In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.
-In Kenya, woman's decision on whether to implement FGC on their daughters were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.
+Based on our analysis of the benefit index \cf{the 4 countries’ PCA results], marriageability was only one benefit for FGC, there were multiple factors in influencing women’s decision of cutting their daughters [MackLeJe08].
+It is likely that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around [EffeVogt15, ShelWand11] (more).
+Reasons for FGC practice could go beyond the belief of marriage prospects and extend to peer convention [ShelWand11].
+In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion [YirgKass12].
+In Kenya, woman's decision on whether to implement FGC on their daughters were likely to relate to collective identity within ethnic groups against broader social changes [Achi14, Hayf05]; similarly findings observed in Nigeria [FreyJohn07, KandMwek09].
 
-Although FGC prevalence was a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot}:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status.
+Although FGC prevalence was a main factor predicting daughter’s FGC status [BoylSvec19] \cf{more cites], we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot]:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status.
 In this case, what people did (descriptive norm?) was less a force than what they will do.
 In other words, - descriptive norm (i.e., FGC prevalence) was undermined by subjective norm (community intentional behaviour of .
-\cf{One confusing finding is that all the three models showed group fgc benefits are robustly and negatively associated with the responses.}.
-Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.
-There are conventional roots in FGC practice \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19CONFIRM, ShelWand11} (more)
+\cf{One confusing finding is that all the three models showed group fgc benefits are robustly and negatively associated with the responses.].
+Norms sustained through communications and evolve through social interactions [FishAjze10, RimaLapi15].
+There are conventional roots in FGC practice [FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11] which may evolve into various forms of conventional norms, such as peer convention [GrosHayd19CONFIRM, ShelWand11] (more)
 
 Regarding community beliefs of FGC benefits, it had a negative correlation with both women’s intention of cutting their daughters and FGC continuance:  the stronger the overall FGC benefits was, the less likely a mother to cut their daughters and less likely to support the practice.
-This was against common wisdom \cite{}.
+This was against common wisdom [].
 One possible explanation is that “it's left over after we include community behaviour.
 If the community believes in it, they'll probably do it, and then I'll probably do it.
-But if I \emph{control for} community behaviour, there's no reason to think that community belief is still explanatory.
+But if I \emph{control for] community behaviour, there's no reason to think that community belief is still explanatory.
 In fact, if I see myself as different from the community I'm more likely to break the norm than if I don’t.” \cfcmt{J:  This is basically your words.
 Can you rewrite it?
-And I don’t understand the last sentence.}  It was noted that sum of benefits does not equal norm \cite{RimaLapi15}  \cfonly{Need to add Hayf05}
+And I don’t understand the last sentence.]  It was noted that sum of benefits does not equal norm [RimaLapi15]  \cfonly{Need to add Hayf05]
 
@@
 
-Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cf{figure xx and figure xxx}.
+Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cf{figure xx and figure xxx].
 Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).
 
-The positive impact modernization \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, KandNwak09, Lewi04, Meye00, Njam04, YirgKass12, Youn02} on intention of cutting daughters were not obvious than the convention approach in our findings as well as previously concluded \cite{Hayf05} \cfonly{to confirm}.
-While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite{Hayf05}.
+The positive impact modernization [BoylMcMo02, Youn02] and gender/feminist perspectives [BoylSvec19, DalaLawo10, Dell04, FrieMahm13, KandNwak09, Lewi04, Meye00, Njam04, YirgKass12, Youn02] on intention of cutting daughters were not obvious than the convention approach in our findings as well as previously concluded [Hayf05] \cfonly{to confirm].
+While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) [GrosHayf19], our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya [Hayf05].
 
 Regarding FGC continuity, education and wealth (both individual and community level) were clearly correlated with attitudes towards FGC continuation in our findings.
-While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment \cite{Sagn14}, and to Egpyt \cite{DalaLawo10, VanMeek16}.
-A secondary analysis of the Egypt DHS from 1995 to 2014 showed a positive correlation of individual level of education, job and wealth with their attitudes of FGC continuity \cite{VanMeek15} .
-It is also important to engage community and religious leaders to understand the need for change and to generate a transformation within the culture \cite{KleiHelz18}.
+While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment [Sagn14], and to Egpyt [DalaLawo10, VanMeek16].
+A secondary analysis of the Egypt DHS from 1995 to 2014 showed a positive correlation of individual level of education, job and wealth with their attitudes of FGC continuity [VanMeek15] .
+It is also important to engage community and religious leaders to understand the need for change and to generate a transformation within the culture [KleiHelz18].
 
-It is noticed that the patterns of FGC benefits based on the PCA results \cfcmt{M: PCA figures} indicated that benefits of FGC was not as clearly elaborated as the benefit module categorized.
+It is noticed that the patterns of FGC benefits based on the PCA results \cfcmt{M: PCA figures] indicated that benefits of FGC was not as clearly elaborated as the benefit module categorized.
 The main index was grouped as others.
 It means that the main reasons of why mothers intended to cut their daughters or what they believe was the real benefits/reason was not clearly stated.
-It could be reasons aforementioned as, for example, peer convention \cite{GrosHayd19CONFIRM, ShelWand11}.
+It could be reasons aforementioned as, for example, peer convention [GrosHayd19CONFIRM, ShelWand11].
 Further field research is recommended to further clarify reasons of cutting.
@@
 
+\hypertarget{conclusion}{%
+\section{Conclusion:}\label{conclusion}}
+
 ———— stop reading —————
@@
 
-% P<0.05 in \cite{Hayf05}:  women’s age, individual media,
+% P<0.05 in [Hayf05]:  women’s age, individual media,
 
-\cf{wealth and group wealth are in opposition direction, so did media and group media (as well as benefit and group benefit).Why?  see daughter isoplot}
+\cf{wealth and group wealth are in opposition direction, so did media and group media (as well as benefit and group benefit).Why?  see daughter isoplot]
 
-\cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
-\cite{Hayf05, PashPonn16} (more) % media:  \cite{DalaLawo10}
+[DalaKalm18](in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
+[Hayf05, PashPonn16] (more) % media:  [DalaLawo10]
 
-% Refer the findings to \cite{BiccMari15} on fgc dynamics/freedom/fgc prevalence trend/econcomic development etc in the 4 nations. (e.g., table 8)
+% Refer the findings to [BiccMari15] on fgc dynamics/freedom/fgc prevalence trend/econcomic development etc in the 4 nations. (e.g., table 8)
 — by nations and laws in those nations—
 
-%Except for Mali, all the studied nations have enacted decrees or legislation related to FGC \cite{WHO13}
+%Except for Mali, all the studied nations have enacted decrees or legislation related to FGC [WHO13]
 
----- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
- vs. \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
+---- Kenya: legal background:  Kenya [GKEN01]; [UNIC13]; 
+ vs. [Chia14, Hayf05], and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]]
 ---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali.
@@
 FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone.
-We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}
+We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea [YodaWang13]
 
 ---- Sierra Leone: 
-\cite{Sagn14}  (used)
+[Sagn14]  (used)
 
@@
 - More options of FGC benefit module is suggested.
-- family dynamics are relevant to gain support to end female genital cutting”\cite{Hayf06}
-- Involve elders and traditional leaders to address the issue of those who wish not to participate in the cutting practice \cite{ChegAske04, more}
+- family dynamics are relevant to gain support to end female genital cutting”[Hayf06]
+- Involve elders and traditional leaders to address the issue of those who wish not to participate in the cutting practice [ChegAske04, more]
 
-Changes of social norms in public health behaviours may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.
+Changes of social norms in public health behaviours may require a few steps:  motivation, deliberation and action [CislHeis18a].
 An alternative to fgc (e.g., a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour.
-(using Tostan as an example) (also see \cite{Youn15}.
-Promising change are observed in changing norms \cite{EvanSnid19} (and Tostan).
+(using Tostan as an example) (also see [Youn15].
+Promising change are observed in changing norms [EvanSnid19] (and Tostan).
 How to foresee a community conducive to certainty for girls without fgc?
@@
 While the comparison of foot binding had a public norm effect, the difference between FGC and no FGC is more personal.
-A bottom-up campaign empowering local community and engaging women in change of the practice is essential \cite{BergDeni13b} and messages tailoring differences of normative beliefs in different groups should also be considered.
+A bottom-up campaign empowering local community and engaging women in change of the practice is essential [BergDeni13b] and messages tailoring differences of normative beliefs in different groups should also be considered.
 The practice of FGC is likely to be revised due to types of FGC, but how to eradicate it if it evolves to just a “nick” compared to the norm of male circumcision?
@@
 - MC vs. FGC.  If MC is an ethnic identity among Jewish community and is overall accepted around the world, can FGC be granted for a similar value if it is just a "nick?"
-Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice.
+Considering the acceptance of Alternative rights of passage [GaluKama15] without criminalize the practice.
 (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs.
-focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}; medicalizing FGC \cite{LeyeVanE19}
+focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) [ShelHern13, Will18]; medicalizing FGC [LeyeVanE19]
 - modelling by plotting empirical data to study threshold/tipping point.
@@
 - inviting faced women migrated to western society to participate in fgc intervention campaign.
-For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \cite{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs.
+For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" [WahlJohn17], and initiating “participatory campaign and education”  (an idea from [MackLeJe08]’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs.
 trickle-down strategy)
-- \cite{MackLeJe08}”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html).
+- [MackLeJe08]”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html).
 Both human rights deliberation and coordinated community abandonment are necessary for change.
 National programmes in Egypt and Sudan are promoting positive human rights messages and discussions at national, regional, and local levels, and are experimenting with a variety of coordinated abandonment through community dialogue efforts at the local level.
-“ (use \cite{Dagn09, MackLeJe08} for this idea)
-- a bottom-up intervention aimed at changing social expectation \cite{BiccMari15}
-- Instead of focusing on improving knowledge and changing attitudes, we need to be more cautious about implementation of social norm interventions and infuse intervention in a relational dimension and a dynamic framework \cite{CislHeis18a, CislHeis18b, McCh15}.
-Empowering local community and opinion leaders in implementing “organized diffusion” \cite{MackLeJe08}has proven cost-effective \cite{CislDenn19}.
+“ (use [Dagn09, MackLeJe08] for this idea)
+- a bottom-up intervention aimed at changing social expectation [BiccMari15]
+- Instead of focusing on improving knowledge and changing attitudes, we need to be more cautious about implementation of social norm interventions and infuse intervention in a relational dimension and a dynamic framework [CislHeis18a, CislHeis18b, McCh15].
+Empowering local community and opinion leaders in implementing “organized diffusion” [MackLeJe08]has proven cost-effective [CislDenn19].
 (and Boston?)
 
-\cite{Cami15}: “ interventions against FGC, rather than leading to the abandonment of the practice, can have unintended and potentially harmful effects on the way FGC is performed.”
+[Cami15]: “ interventions against FGC, rather than leading to the abandonment of the practice, can have unintended and potentially harmful effects on the way FGC is performed.”
 
-— Limitation —
+-- Limitation --
 While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?
-As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cite{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.
+As proposed that social norm and the behavior it compels cannot be inferred from personal attitude [Mack18] (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.
 
@@
 
-\subsection{Funding}\label{Funding}
+\hypertarget{declarations}{%
+\section{Declarations}\label{declarations}}
 
-CF was funded by a grant from the James S. McDonnell foundation. JD holds a New Investigator award from the Canadian Institutes of Health Research.
+\hypertarget{availability-of-data-and-materials}{%
+\subsection{Availability of data and
+materials}\label{availability-of-data-and-materials}}
 
-\subsection{Conflicts of interest}\label{Conflicts-of-Interest}
+The datasets analysed during the current study will be publicly
+available on
+\href{} when the paper is published.
 
-The James S.
-McDonnell foundation and the Canadian Institutes of Health Research had no role in study design; collection, analysis, and interpretation of data; the writing of the manuscript; or in the decision to submit the manuscript for publication.
-The views expressed herein do not necessarily represent the views of the founding bodies.
+\hypertarget{competing-interests}{%
+\subsection{Competing interests}\label{competing-interests}}
 
-\subsection{Authors' contributions}\label{Authors'-contributions}
+The authors report no competing interests.
 
-\subsubsection{Disclaimer}\label{disclaimer}
+\hypertarget{funding}{%
+\subsection{Funding}\label{funding}}
 
-The findings and conclusions of this article are those of the authors
-and do not necessarily represent the views of the funding agency.
+\hypertarget{authors-contributions}{%
+\subsection{Authors' contributions}\label{authors-contributions}}
 
-\subsubsection{Acknowledgement}\label{Acknowledgement}
-Ben Bolker,  Marta Wayne
+Authors contributed to this work as follows: conceptualizing the
+research questions: CS; designing the study: CS, JD, ML; acquiring the
+data: MS; analyzing and interpreting the data: JD, MS, CS.; drafting the article: CS, JD, ML. Revising and approving
+the version to be published: CS, JD, ML
 
-\subsubsection{Appendix}\label{appendix-1}
+\hypertarget{acknowledgements}{%
+\subsection{Acknowledgements}\label{acknowledgements}}
 
-\bibliography{refs}
+We thank Beth Haller, Ben Bolker, and the
+\href{https://mac-theobio.github.io/}{Theoretical Biology lab} at
+McMaster University for valuable discussions and comments.
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+
+\end{CSLReferences}
 
@@
 
-%%% ======================================================================
 ===== stop reading =======
 
-\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),
+[Drot11, Grue05, JoneEhir04] (both on cultural perspective, and maybe norm),
 
 OVERALL:
-\cite{UNIC13}:  “Many girls who are cut are daughters of women who oppose the practice”
+[UNIC13]:  “Many girls who are cut are daughters of women who oppose the practice”
 
 % The finding “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors.
-This is in contrast to the tipping point and informational cascade models …, wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.
+This is in contrast to the tipping point and informational cascade models …, wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  [BellNova15]; and to compare our results to [BellNova15] because they agnostic about the three theories.
 
-\comment{cf: how to cite \cite{AkhmWord13,EffeVogt15} and compare these two?}
+\comment{cf: how to cite [AkhmWord13,EffeVogt15] and compare these two?]
 % There are "discrepancies between attitudes and practices, especially significant under an analysis by sex as, despite manifesting less support, the percentage of female HCPs declaring to have performed medicalization is almost twice the males' average.
-These findings suggest that female HCPs could be facing higher demand to medicalize the practice, and that, even when brought to the medical setting, FGM/C is regarded as a women's issue to be performed by women to women." \cite{KaplSing16}
+These findings suggest that female HCPs could be facing higher demand to medicalize the practice, and that, even when brought to the medical setting, FGM/C is regarded as a women's issue to be performed by women to women." [KaplSing16]
 
-% "autonomy within culture" is socially situated and entails neither endorsement of FGC nor resignation to its persistence." \cite{Meye00}:  How can we apply this feminism perspective to our findings?
+% "autonomy within culture" is socially situated and entails neither endorsement of FGC nor resignation to its persistence." [Meye00]:  How can we apply this feminism perspective to our findings?
 (Since we did not categorize types of fgc in our study, we can't know if women of autonomy prefer to have a "nick" on their daughter to preserve cultural identity or abandon fgc completely.
@@
 
-%Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics \cite{BrowBeec13}.
- \cite{Shel-Wand11}:  supporting Mackie's convetion theory ``expections regarding fgc are interdependent...."
+%Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics [BrowBeec13].
+ [Shel-Wand11]:  supporting Mackie's convetion theory ``expections regarding fgc are interdependent...."
 
-% suggestions:  to invite elder woman to participate in reducing FGC \cite{ShelMore18}
+% suggestions:  to invite elder woman to participate in reducing FGC [ShelMore18]
 
-% contagious diffusion \cite{Mack96}
+% contagious diffusion [Mack96]
 
@@
 Based on this new evidence and reinterpretation of social convention theory, we suggest that interventions aimed at eliminating FGC should target women's social networks, which are intergenerational, and include both men and women.
-Our findings support Mackie's assertion that expectations regarding FGC are interdependent; change must therefore be coordinated among interconnected members of social networks." \cite{ShelWand11}
+Our findings support Mackie's assertion that expectations regarding FGC are interdependent; change must therefore be coordinated among interconnected members of social networks." [ShelWand11]
 
-FGC is still in practice or a preference among women after migrated to a western environment from their original communities where FGC was a common practice, in the hope (wording?) of preserving their ethnic and gender identity despite its conflict against the  norms and laws of the newly settled society \cite{}; however, a baseline study in Sweden showed that a majority of female immigrants, including those newly arrived, opposed all forms of FGC with increased opposition over time after migration, and suggested that an attitude change had occurred \cite{WahlJohn17}; that suggested a likely influence of convention theory.
+FGC is still in practice or a preference among women after migrated to a western environment from their original communities where FGC was a common practice, in the hope (wording?) of preserving their ethnic and gender identity despite its conflict against the  norms and laws of the newly settled society []; however, a baseline study in Sweden showed that a majority of female immigrants, including those newly arrived, opposed all forms of FGC with increased opposition over time after migration, and suggested that an attitude change had occurred [WahlJohn17]; that suggested a likely influence of convention theory.
 
-% Spatial Bayesian model \cite{KandNwak09}
-% idea of purity of women reflects on the status and honor of their families \cite{Ortn87}.  Female purity is oriented to an ideal and unattainable higher class. \cite{Ortn87}
-% a possibility of a multicultural egalitarian society \cite{Wade11}
-% success in community education program to abandon FGC \cite{DiopAske09}
+% Spatial Bayesian model [KandNwak09]
+% idea of purity of women reflects on the status and honor of their families [Ortn87].  Female purity is oriented to an ideal and unattainable higher class. [Ortn87]
+% a possibility of a multicultural egalitarian society [Wade11]
+% success in community education program to abandon FGC [DiopAske09]
 %\cfcmt{convention theory mainly work on norms or also on behaviour change?
 There seems a gap between norm and behaviour in FGC, can diffusion theory brigade the gap?
-As suggested, community-based education program has fallen shot tin changing FGC behaviours \cite{Shel08}}
+As suggested, community-based education program has fallen shot tin changing FGC behaviours [Shel08]]
 % "I do not deny that individuals have evolved the capability to learn and apply social norms even to situations that are completely new, but there is much evidence that we are conditional followers of norms.
 In fact, as the experiments reported in Bicchieri and Xiao (2009) and Bicchieri and Chavez (2010) show, manipulating information produces major changes in behavior, and the existence of a social norm is no guarantee that it will be followed.
-The real challenge we face is to explain how normative expectations emerge or, in other words, how the beliefs that support social norms take shape." \cite{Bicc10}.
+The real challenge we face is to explain how normative expectations emerge or, in other words, how the beliefs that support social norms take shape." [Bicc10].
 
 “we find that some older women express an openness to reassessing norms and practices as they seek solutions to maintaining the physical well-being, moral integrity and cultural identity of girls in their families.
-Moreover, given the authority of older women over younger women, they also have power to negotiate change.\cite{ShelMore18}
+Moreover, given the authority of older women over younger women, they also have power to negotiate change.[ShelMore18]
 
-% "granted, recognized, and implemented by the state must not de-emphasize or delegitimize approaches recognizing the cultural significance of FGC and the potentially multiple and cascading social effects of ending the practice." \cite{(Shel08}, p.
+% "granted, recognized, and implemented by the state must not de-emphasize or delegitimize approaches recognizing the cultural significance of FGC and the potentially multiple and cascading social effects of ending the practice." [(Shel08], p.
 229)
 
-% A society may discontinue FGC practice or maintain the practice in a different form (e.g., a less harmful type of FGC) (that is cultural change in Wade's concept \cite{Wade11})
+% A society may discontinue FGC practice or maintain the practice in a different form (e.g., a less harmful type of FGC) (that is cultural change in Wade's concept [Wade11])
 
 %  "Residual spatial effects of FGM have enabled us to see the inherent spatial patterns of the prevalence of FGM because the variability or noise has been removed.
-A more precise spatial pattern of the prevalence of FGM emerged with the estimated residual state effects compared with the crude prevalence without the control of geographic location effects." \cite{KandNwak09, p.
-791}
+A more precise spatial pattern of the prevalence of FGM emerged with the estimated residual state effects compared with the crude prevalence without the control of geographic location effects." [KandNwak09, p.
+791]
 
-% From modifying the practice to discarding it through a process of conversations and understanding  \cite{Mutu02, Shel08}
-% findings in \cite{BoylMcMo02}
+% From modifying the practice to discarding it through a process of conversations and understanding  [Mutu02, Shel08]
+% findings in [BoylMcMo02]
 %* "These finding are particularly informative because most modernization analyses only consider attitude change.
@@
 % "This study suggests that the adoption of a `modern' lifestyle is not an inevitable result of acquiring the tools that give a person mastery over nature.
-Rather, the transmission of particular ideologies through global institutionalized arrangements appears to be the critical factor in abandoning practices like FGC." \cite{(BoylMcMo02}, p.
+Rather, the transmission of particular ideologies through global institutionalized arrangements appears to be the critical factor in abandoning practices like FGC." [(BoylMcMo02], p.
 26)  What does this mean???
 
-% National and cultural boundaries are not coextensive, when religious and community-based norms are considered \cite{BoylCorl10} (similar cultural approach \cite{SchuLien13}
+% National and cultural boundaries are not coextensive, when religious and community-based norms are considered [BoylCorl10] (similar cultural approach [SchuLien13]
 
-% The legitimacy of international laws banning the practice of FGC"rests on its ability to demonstrate that global and local cultures are highly interpenetrated—that global culture absorbs a full range of local values." \cite{(BoylCorl10}, p 209)
+% The legitimacy of international laws banning the practice of FGC"rests on its ability to demonstrate that global and local cultures are highly interpenetrated—that global culture absorbs a full range of local values." [(BoylCorl10], p 209)
 
@@
 %"This review demonstrates the strong social pressure to which women are subjected as regards the practice of female genital mutilation.
-However, many other factors can contribute to eroding beliefs and arguments in favour of this practice, such as the globalization, culture and social environment of countries in the West." \cite{ReigGonz14}
+However, many other factors can contribute to eroding beliefs and arguments in favour of this practice, such as the globalization, culture and social environment of countries in the West." [ReigGonz14]
 
-systematic review of effectiveness of fgc factors associating the practice \cite{WaigDoos18}
+systematic review of effectiveness of fgc factors associating the practice [WaigDoos18]
 
-Gender/feminist perspective:  \cite{Meye00} Meyers questions the idea of social norm and autonomy "It seems to me that we would need far more consensus than we presently have (or are likely to get) about human nature and social justice before we could conclude that women who opt for compliance with female genital cutting norms never do so autonomously.
+Gender/feminist perspective:  [Meye00] Meyers questions the idea of social norm and autonomy "It seems to me that we would need far more consensus than we presently have (or are likely to get) about human nature and social justice before we could conclude that women who opt for compliance with female genital cutting norms never do so autonomously.
 We would have to be persuaded, in other words, that all women's interests are such that this decision could not accord with any woman's authentic values and desires under any circumstances."
 
-Egypt:  "Literate, better educated and employed women are more likely to oppose FGM" \cite{VanMeek15}
-Sinegal: \cite{KandComb15}
-West Africa:  \cite{SipsChen12} (law and current practices)
+Egypt:  "Literate, better educated and employed women are more likely to oppose FGM" [VanMeek15]
+Sinegal: [KandComb15]
+West Africa:  [SipsChen12] (law and current practices)
 Theory:
@@
 % convention or modernization theory?`` campaigns against FGC using educational, health, legal, and human rights–based approaches are at times ineffective and counterproductive when they frame the practice as a ``tradition" rooted in a ``primitive" and unchanging culture.
-We suggest that development interventions that do not address local contexts of FGC, including the complex politics and history of interventions designed to eradicate it, can in fact reify and reinscribe the practice as central to Maasai cultural identity." \cite{WintKoom09}
+We suggest that development interventions that do not address local contexts of FGC, including the complex politics and history of interventions designed to eradicate it, can in fact reify and reinscribe the practice as central to Maasai cultural identity." [WintKoom09]
 
-% \cite{Koom14}: `` practices of female excision are so diverse that they may defy generalizable remedies"  ``Rather than relying on common campaign models, transferable advocacy tools, or `best practices,' scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics."  Instead of straightforward campaigns against traditional culture, "culturalconstestaion" characterized by politicized negotiation and, at times, resistance, was proposed.
-\cite{Koom14}.
+% [Koom14]: `` practices of female excision are so diverse that they may defy generalizable remedies"  ``Rather than relying on common campaign models, transferable advocacy tools, or `best practices,' scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics."  Instead of straightforward campaigns against traditional culture, "culturalconstestaion" characterized by politicized negotiation and, at times, resistance, was proposed.
+[Koom14].
 
-A multicultural egalitarian approach respecting both cultural identity and basic legal human rights was addressed \cite{BoylCarb10, Wade11}.
+A multicultural egalitarian approach respecting both cultural identity and basic legal human rights was addressed [BoylCarb10, Wade11].
 
@@
 A variety of socio-cultural myths, religious misbelievers, and hygienic and esthetic concerns were behind the FGM/C.
-Overall, a large proportion of the participants supported the continuation of FGM/C in spite of adverse effect and sexual dysfunction associated with FGM/C." \cite{MohaHass14}
+Overall, a large proportion of the participants supported the continuation of FGM/C in spite of adverse effect and sexual dysfunction associated with FGM/C." [MohaHass14]
 
-% read \cite{MohaHass14, MuteMill16, PashPonn16, VaroFras14}
+% read [MohaHass14, MuteMill16, PashPonn16, VaroFras14]
 
-"support HCPs in the integration of FGM/C preventive interventions within the public health system, to address arguments favoring medicalization, and to use data to design appropriate strategies." \cite{KaplRiba16}
+"support HCPs in the integration of FGM/C preventive interventions within the public health system, to address arguments favoring medicalization, and to use data to design appropriate strategies." [KaplRiba16]
 
@@
 Living in an urban area decreased the likelihood of favoring genital cutting, but it had no effect on behavior.
-`` \cite{BoylMcMo02}
+`` [BoylMcMo02]
 
-%\cfcmt{Bicchieri's norm theory \cite{Bicc06, BiccMari15}:
+%\cfcmt{Bicchieri's norm theory [Bicc06, BiccMari15]:
 behaviour:  What the responder do 
@@
 
-\cite{UNFPA14, UNIC16}
+[UNFPA14, UNIC16]
 
 % cultural sensitivity:  It suggests that "legislative efforts to protect women's health may remain ineffective with
-out structured efforts between health systems, governments or legal institutions and the cultural society." \cite{Iyio12} and 
-% through laws \cite{AloGbad11}
-%\cite{MackLeJe08}: “transformative human rights”  it seems to assume that western human rights will work accompanied with social and moral norm in abandoning fgc (p.
+out structured efforts between health systems, governments or legal institutions and the cultural society." [Iyio12] and 
+% through laws [AloGbad11]
+%[MackLeJe08]: “transformative human rights”  it seems to assume that western human rights will work accompanied with social and moral norm in abandoning fgc (p.
 2).
@@
 % Education programs aimed to empower women through a broad range of educational and health-promoting activities by improvements in knowledge about and critical attitudes toward FGC had impact on behaviors and attitudes.
-\cite{DiopAske09}.
-Legal measures must combine with social measures to effectively eradicate FGC and communities practising FGC must be involved in the planning and implementation of  intervention of FGC elimination \cite{AkoAwke09}
+[DiopAske09].
+Legal measures must combine with social measures to effectively eradicate FGC and communities practising FGC must be involved in the planning and implementation of  intervention of FGC elimination [AkoAwke09]
 
-% \cite{BrowBeec13}:  their questions of the 4 current approaches (sexuality, human rights, etc) and their suggestions
+% [BrowBeec13]:  their questions of the 4 current approaches (sexuality, human rights, etc) and their suggestions
 
-% attitudes change may be followed by behaviour change, but more slowly \cite{BoylMcMo02}
+% attitudes change may be followed by behaviour change, but more slowly [BoylMcMo02]
 
-%\cite{JohaDiop13}:  Some of the most common approaches (1) health risk approaches, (2) conversion of excisers, (3) training of health professionals as change agents, (4) alternative rituals, (5) community-led approaches, (6) public statements, and (7) legal measures.
+%[JohaDiop13]:  Some of the most common approaches (1) health risk approaches, (2) conversion of excisers, (3) training of health professionals as change agents, (4) alternative rituals, (5) community-led approaches, (6) public statements, and (7) legal measures.
 
-% Did our findings see something like group/community identity, womanhood \cite{Koom14}?
-% \cite{Koom14}: `` an Aang Serian activist who had addressed a village meeting saying, `The world is changing and the Maasai must change with it or risk dying out.' They argued that these appeals to cultural survival were much more persuasive and meaningful to them than the `foreign' language of rights."
+% Did our findings see something like group/community identity, womanhood [Koom14]?
+% [Koom14]: `` an Aang Serian activist who had addressed a village meeting saying, `The world is changing and the Maasai must change with it or risk dying out.' They argued that these appeals to cultural survival were much more persuasive and meaningful to them than the `foreign' language of rights."
 
-Analyzing why MC is a much accepted behaviour might help us to re-think the meanings of FGC (see \cite{DarbSvob07}) and, if, to certain extent, to accept a form of FGC practice (e.g, a "nick" \cite{Wade11}).
+Analyzing why MC is a much accepted behaviour might help us to re-think the meanings of FGC (see [DarbSvob07]) and, if, to certain extent, to accept a form of FGC practice (e.g, a "nick" [Wade11]).
 
-% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{Can heterogeneity explain the differences of beliefs in FGC benefits at individual level vs.
-at a community level?}
+% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population [EffeVogt15] \cfcmt{Can heterogeneity explain the differences of beliefs in FGC benefits at individual level vs.
+at a community level?]
 
-% \cfcmt{TOSTAN uses a strategy based on convention theory's critical mass to eradicate FGC (see (Wils13}}
+% \cfcmt{TOSTAN uses a strategy based on convention theory's critical mass to eradicate FGC (see (Wils13]]
  * Festinger (1950?):  Social pressure in informal groups
 
-% a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see \cite{BoylCorl10}, table 1)
+% a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see [BoylCorl10], table 1)
 
-\cite{CentBeck18}:  social convention and tipping point
+[CentBeck18]:  social convention and tipping point
 
@@
 
-Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShel18} vs.
+Suggestions: pricking (type IV[WHO08])[WahlJohn17a, WahlJohn17b] and medical FGC [KimaShel18] vs.
 no-tolerance, fgc vs.
-mc \cite{WahlEsse18}?
+mc [WahlEsse18]?
 We suggest to position ourselves in a context where male circumcision (MC) is practices and accepted; to consider the differences of a prick of FGC and MC; to comprehend the outcomes of abolishing FGC vs.
 changing FGC practices.
-\cite{WahlEsse18}:  from sameness to differences, a global multicultural approach especially during the international migration across the globe.
+[WahlEsse18]:  from sameness to differences, a global multicultural approach especially during the international migration across the globe.
 
- \cf{(“social norm and the behavior it compels cannot be inferred from personal attitude, implicit or explicit” Mackie in his rebuttal letter.  But is vice versa true?}
+ \cf{(“social norm and the behavior it compels cannot be inferred from personal attitude, implicit or explicit” Mackie in his rebuttal letter.  But is vice versa true?]
 
-Models:  “A Bayesian geo-additive mixed model based on Markov Chain Monte Carlo techniques was used to map the change in the spatial distribution of FGM/C prevalence” \cite{KandShel19}
+Models:  “A Bayesian geo-additive mixed model based on Markov Chain Monte Carlo techniques was used to map the change in the spatial distribution of FGM/C prevalence” [KandShel19]
 ====================================
